---
title: "CGM_all_patients"
author: "Christoph Völtzke"
date: "2022"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Needed packages
```{r}
library(lubridate) # manipulate dates
library(tidyverse) # data processing
library(ggplot2) # plotting
library(broom) # data processing
library(iglu) # CGM indices
```


## Loading the data sets
```{r}
# All patients with CGM data
cgm_574 <- read.table("Patients_all_sources/574/cgm_574.txt",sep ="", dec=",", header=T)
cgm_597 <- read.table("Patients_all_sources/597/cgm_597.txt",sep ="", dec=",", header=T)
cgm_598 <- read.table("Patients_all_sources/598/cgm_598.txt",sep ="", dec=",", header=T)
cgm_601 <- read.table("Patients_all_sources/601/cgm_601.txt",sep ="", dec=",", header=T)
cgm_608 <- read.table("Patients_all_sources/608/cgm_608.txt",sep ="", dec=",", header=T)
cgm_605 <- read.table("Patients_all_sources/605/cgm_605.txt",sep ="", dec=",", header=T)
cgm_606 <- read.table("Patients_all_sources/606/cgm_606.txt",sep ="", dec=",", header=T)
cgm_607 <- read.table("Patients_all_sources/607/cgm_607.txt",sep ="", dec=",", header=T)
cgm_609 <- read.table("Patients_all_sources/609/cgm_609.txt",sep ="", dec=",", header=T)
cgm_611 <- read.table("Patients_all_sources/611/cgm_611.txt",sep ="", dec=",", header=T)
cgm_612 <- read.table("Patients_all_sources/612/cgm_612.txt",sep ="", dec=",", header=T)
cgm_615 <- read.table("Patients_all_sources/615/cgm_615.txt",sep ="", dec=",", header=T)
cgm_616 <- read.table("Patients_all_sources/616/cgm_616.txt",sep ="", dec=",", header=T)
cgm_617 <- read.table("Patients_all_sources/617/cgm_617.txt",sep ="", dec=",", header=T)
cgm_618 <- read.table("Patients_all_sources/618/cgm_618.txt",sep ="", dec=",", header=T)
cgm_619 <- read.table("Patients_all_sources/619/cgm_619.txt",sep ="", dec=",", header=T)
cgm_621 <- read.table("Patients_all_sources/621/cgm_621.txt",sep ="", dec=",", header=T)
cgm_623 <- read.table("Patients_all_sources/623/cgm_623.txt",sep ="", dec=",", header=T)
cgm_624 <- read.table("Patients_all_sources/624/cgm_624.txt",sep ="", dec=",", header=T)
cgm_628 <- read.table("Patients_all_sources/628/cgm_628.txt",sep ="", dec=",", header=T)
cgm_629 <- read.table("Patients_all_sources/629/cgm_629.txt",sep ="", dec=",", header=T)
cgm_630 <- read.table("Patients_all_sources/630/cgm_630.txt",sep ="", dec=",", header=T)
cgm_632 <- read.table("Patients_all_sources/632/632/cgm_632.txt",sep ="", dec=",", header=T)
cgm_633 <- read.table("Patients_all_sources/633/cgm_633.txt",sep ="", dec=",", header=T)
cgm_634 <- read.table("Patients_all_sources/634/cgm_634.txt",sep ="", dec=",", header=T)
cgm_635 <- read.table("Patients_all_sources/635/cgm_635.txt",sep ="", dec=",", header=T)
cgm_636 <- read.table("Patients_all_sources/636/cgm_636.txt",sep ="", dec=",", header=T)
cgm_637 <- read.table("Patients_all_sources/637/cgm_637.txt",sep ="", dec=",", header=T)
cgm_638 <- read.table("Patients_all_sources/638/cgm_638.txt",sep ="", dec=",", header=T)
cgm_639 <- read.table("Patients_all_sources/639/cgm_639.txt",sep ="", dec=",", header=T)
cgm_640 <- read.table("Patients_all_sources/640/cgm_640.txt",sep ="", dec=",", header=T)
cgm_641 <- read.table("Patients_all_sources/641/cgm_641.txt",sep ="", dec=",", header=T)
cgm_642 <- read.table("Patients_all_sources/642/cgm_642.txt",sep ="", dec=",", header=T)
cgm_643 <- read.table("Patients_all_sources/643/cgm_643.txt",sep ="", dec=",", header=T)
cgm_644 <- read.table("Patients_all_sources/644/cgm_644.txt",sep ="", dec=",", header=T)
cgm_645 <- read.table("Patients_all_sources/645/cgm_645.txt",sep ="", dec=",", header=T)
cgm_646 <- read.table("Patients_all_sources/646/cgm_646.txt",sep ="", dec=",", header=T)
cgm_647 <- read.table("Patients_all_sources/647/cgm_647.txt",sep ="", dec=",", header=T)
cgm_648 <- read.table("Patients_all_sources/648/cgm_648.txt",sep ="", dec=",", header=T)
cgm_649 <- read.table("Patients_all_sources/649/cgm_649.txt",sep ="", dec=",", header=T)
cgm_650 <- read.table("Patients_all_sources/650/cgm_650.txt",sep ="", dec=",", header=T)
cgm_651 <- read.table("Patients_all_sources/651/cgm_651.txt",sep ="", dec=",", header=T)
cgm_654 <- read.table("Patients_all_sources/654/654/cgm_654.txt",sep ="", dec=",", header=T)
cgm_656 <- read.table("Patients_all_sources/656/656/cgm_656.txt",sep ="", dec=",", header=T)
cgm_658 <- read.table("Patients_all_sources/658/cgm_658.txt",sep ="", dec=",", header=T)
cgm_660 <- read.table("Patients_all_sources/660/cgm_660.txt",sep ="", dec=",", header=T)
cgm_661 <- read.table("Patients_all_sources/661/cgm_661.txt",sep ="", dec=",", header=T)
cgm_662 <- read.table("Patients_all_sources/662/cgm_662.txt",sep ="", dec=",", header=T)
cgm_663 <- read.table("Patients_all_sources/663/cgm_663.txt",sep ="", dec=",", header=T)
cgm_664 <- read.table("Patients_all_sources/664/cgm_664.txt",sep ="", dec=",", header=T)
cgm_665 <- read.table("Patients_all_sources/665/cgm_665.txt",sep ="", dec=",", header=T)
cgm_666 <- read.table("Patients_all_sources/666/cgm_666.txt",sep ="", dec=",", header=T)
cgm_667 <- read.table("Patients_all_sources/667/cgm_667.txt",sep ="", dec=",", header=T)
cgm_669 <- read.table("Patients_all_sources/669/cgm_669.txt",sep ="", dec=",", header=T)
cgm_671 <- read.table("Patients_all_sources/671/cgm_671.txt",sep ="", dec=",", header=T)
cgm_672 <- read.table("Patients_all_sources/672/cgm_672.txt",sep ="", dec=",", header=T)
cgm_674 <- read.table("Patients_all_sources/674/cgm_674.txt",sep ="", dec=",", header=T)
cgm_676 <- read.table("Patients_all_sources/676/cgm_676.txt",sep ="", dec=",", header=T)
cgm_677 <- read.table("Patients_all_sources/677/cgm_677.txt",sep ="", dec=",", header=T)
cgm_678 <- read.table("Patients_all_sources/678/cgm_678.txt",sep ="", dec=",", header=T,row.names=NULL)
cgm_678 <- cgm_678[,-1]
cgm_680 <- read.table("Patients_all_sources/680/cgm_680.txt",sep ="", dec=",", header=T)
cgm_681 <- read.table("Patients_all_sources/681/cgm_681.txt",sep ="", dec=",", header=T)
cgm_682 <- read.table("Patients_all_sources/682/cgm_682.txt",sep ="", dec=",", header=T)
cgm_683 <- read.table("Patients_all_sources/683/cgm_683.txt",sep ="", dec=",", header=T)
cgm_684 <- read.table("Patients_all_sources/684/cgm_684.txt",sep ="", dec=",", header=T)
cgm_686 <- read.table("Patients_all_sources/686/cgm_686.txt",sep ="", dec=",", header=T)
cgm_687 <- read.table("Patients_all_sources/687/cgm_687.txt",sep ="", dec=",", header=T)
cgm_688 <- read.table("Patients_all_sources/688/cgm_688.txt",sep ="", dec=",", header=T)
cgm_690 <- read.table("Patients_all_sources/690/cgm_690.txt",sep ="", dec=",", header=T)
cgm_691 <- read.table("Patients_all_sources/691/cgm_691.txt",sep ="", dec=",", header=T)
cgm_692 <- read.table("Patients_all_sources/692/cgm_692.txt",sep ="", dec=",", header=T)
cgm_694 <- read.table("Patients_all_sources/694/cgm_694.txt",sep ="", dec=",", header=T)
cgm_695 <- read.table("Patients_all_sources/695/cgm_695.txt",sep ="", dec=",", header=T)
cgm_696 <- read.table("Patients_all_sources/696/cgm_696.txt",sep ="", dec=",", header=T)
cgm_697 <- read.table("Patients_all_sources/697/cgm_697.txt",sep ="", dec=",", header=T)
cgm_698 <- read.table("Patients_all_sources/698/cgm_698.txt",sep ="", dec=",", header=T)
cgm_699 <- read.table("Patients_all_sources/699/cgm_699.txt",sep ="", dec=",", header=T)
cgm_702 <- read.table("Patients_all_sources/702/cgm_702.txt",sep ="", dec=",", header=T)
cgm_703 <- read.table("Patients_all_sources/703/cgm_703.txt",sep ="", dec=",", header=T)
cgm_708 <- read.table("Patients_all_sources/708/cgm_708.txt",sep ="", dec=",", header=T)
cgm_709 <- read.table("Patients_all_sources/709/cgm_709.txt",sep ="", dec=",", header=T)
cgm_712 <- read.table("Patients_all_sources/712/cgm_712.txt",sep ="", dec=",", header=T)
rownames(cgm_712) <- NULL
cgm_713 <- read.table("Patients_all_sources/713/cgm_713.txt",sep ="", dec=",", header=T)
rownames(cgm_713) <- NULL
cgm_716 <- read.table("Patients_all_sources/716/cgm_716.txt",sep ="", dec=",", header=T)
rownames(cgm_716) <- NULL
cgm_719 <- read.table("Patients_all_sources/719/cgm_719.txt",sep ="", dec=",", header=T)
rownames(cgm_719) <- NULL
cgm_729 <- read.table("Patients_all_sources/729/cgm_729.txt",sep ="", dec=",", header=T,row.names=NULL)
cgm_729 <- cgm_729 %>%
  rename("ID" = "row.names")
cgm_745 <- read.table("Patients_all_sources/745/cgm_745.txt",sep ="", dec=",", header=T,row.names=NULL)
cgm_745 <- cgm_745[,-1]
cgm_746 <- read.table("Patients_all_sources/746/cgm_746.txt",sep ="", dec=",", header=T, row.names=NULL)
cgm_746 <- cgm_746[,-1]
cgm_748 <- read.table("Patients_all_sources/748/cgm_748.txt",sep ="", dec=",", header=T, row.names=NULL)
cgm_748 <- cgm_748[,-1]
cgm_749 <- read.table("Patients_all_sources/749/cgm_749.txt",sep ="", dec=",", header=T, row.names=NULL)
cgm_749 <- cgm_749[,-1]
cgm_750 <- read.table("Patients_all_sources/750/cgm_750.txt",sep ="", dec=",", header=T, row.names=NULL)
cgm_750 <- cgm_750[,-1]
cgm_751 <- read.table("Patients_all_sources/751/cgm_751.txt",sep ="", dec=",", header=T, row.names=NULL)
cgm_751 <- cgm_751[,-1]
cgm_752 <- read.table("Patients_all_sources/752/cgm_752.txt",sep ="", dec=",", header=T,row.names=NULL)
cgm_752 <- cgm_752 %>%
  rename("ID" = "row.names")
cgm_753 <- read.table("Patients_all_sources/753/cgm_753.txt",sep ="", dec=",", header=T,row.names=NULL)
cgm_753 <- cgm_753[,-1]
cgm_754 <- read.table("Patients_all_sources/754/cgm_754.txt",sep ="", dec=",", header=T,row.names=NULL)
cgm_754 <- cgm_754[,-1]
cgm_755 <- read.table("Patients_all_sources/755/cgm_755.txt",sep ="", dec=",", header=T,row.names=NULL) # new
cgm_755 <- cgm_755[,-1]
cgm_756 <- read.table("Patients_all_sources/756/cgm_756.txt",sep ="", dec=",", header=T,row.names=NULL)
cgm_756 <- cgm_756[,-1]
cgm_757 <- read.table("Patients_all_sources/757/cgm_757.txt",sep ="", dec=",", header=T,row.names=NULL)
cgm_757 <- cgm_757[,-1]
cgm_759 <- read.table("Patients_all_sources/759/cgm_759.txt",sep ="", dec=",", header=T,row.names=NULL)
cgm_759 <- cgm_759[,-1]
cgm_760 <- read.table("Patients_all_sources/760/cgm_760.txt",sep ="", dec=",", header=T,row.names=NULL)
cgm_760 <- cgm_760[,-1]
cgm_761 <- read.table("Patients_all_sources/761/cgm_761.txt",sep ="", dec=",", header=T,row.names=NULL)
cgm_761 <- cgm_761[,-1]
cgm_762 <- read.table("Patients_all_sources/762/cgm_762.txt",sep ="", dec=",", header=T,row.names=NULL)
cgm_762 <- cgm_762[,-1]
cgm_1001 <- read.table("Patients_all_sources/1001/cgm_1001.txt",sep ="", dec=",", header=T)
```

```{r}
# adding the patient number to identify each patient
# this is needed as there are some differences in the data. So the first part needs to be done separately 
cgm_574$patient <- 574
cgm_597$patient <- 597
cgm_598$patient <- 598
cgm_601$patient <- 601
cgm_605$patient <- 605
cgm_606$patient <- 606
cgm_607$patient <- 607
cgm_608$patient <- 608
cgm_609$patient <- 609
cgm_611$patient <- 611
cgm_612$patient <- 612
cgm_615$patient <- 615
cgm_616$patient <- 616
cgm_617$patient <- 617
cgm_618$patient <- 618
cgm_619$patient <- 619
cgm_621$patient <- 621
cgm_623$patient <- 623
cgm_624$patient <- 624
cgm_628$patient <- 628
cgm_629$patient <- 629
cgm_630$patient <- 630
cgm_632$patient <- 632
cgm_633$patient <- 633
cgm_634$patient <- 634
cgm_635$patient <- 635
cgm_636$patient <- 636
cgm_637$patient <- 637
cgm_638$patient <- 638
cgm_639$patient <- 639
cgm_640$patient <- 640
cgm_641$patient <- 641
cgm_642$patient <- 642
cgm_643$patient <- 643
cgm_644$patient <- 644
cgm_645$patient <- 645
cgm_646$patient <- 646
cgm_647$patient <- 647
cgm_648$patient <- 648
cgm_649$patient <- 649
cgm_650$patient <- 650
cgm_651$patient <- 651
cgm_654$patient <- 654
cgm_656$patient <- 656
cgm_658$patient <- 658
cgm_660$patient <- 660
cgm_661$patient <- 661
cgm_662$patient <- 662
cgm_663$patient <- 663
cgm_664$patient <- 664
cgm_665$patient <- 665
cgm_666$patient <- 666
cgm_667$patient <- 667
cgm_669$patient <- 669
cgm_671$patient <- 671
cgm_672$patient <- 672
cgm_674$patient <- 674
cgm_676$patient <- 676
cgm_677$patient <- 677
cgm_678$patient <- 678
cgm_680$patient <- 680
cgm_681$patient <- 681
cgm_682$patient <- 682
cgm_683$patient <- 683
cgm_684$patient <- 684
cgm_686$patient <- 686
cgm_687$patient <- 687
cgm_688$patient <- 688
cgm_690$patient <- 690
cgm_691$patient <- 691
cgm_692$patient <- 692
cgm_694$patient <- 694
cgm_695$patient <- 695
cgm_696$patient <- 696
cgm_697$patient <- 697
cgm_698$patient <- 698
cgm_699$patient <- 699
cgm_702$patient <- 702
cgm_703$patient <- 703
cgm_708$patient <- 708
cgm_709$patient <- 709
cgm_712$patient <- 712
cgm_713$patient <- 713
cgm_716$patient <- 716
cgm_719$patient <- 719
cgm_729$patient <- 729
cgm_745$patient <- 745
cgm_746$patient <- 746
cgm_748$patient <- 748
cgm_749$patient <- 749
cgm_750$patient <- 750
cgm_751$patient <- 751
cgm_752$patient <- 752
cgm_753$patient <- 753
cgm_754$patient <- 754
cgm_755$patient <- 755
cgm_756$patient <- 756
cgm_757$patient <- 757
cgm_759$patient <- 759
cgm_760$patient <- 760
cgm_761$patient <- 761
cgm_762$patient <- 762
cgm_1001$patient <- 1001
```

# Feature Engineering

## Basic preprocessing
- Creation of time and date features
- Definition of thresholds based on ADA for Hypoglycemia events
- Definition of Episodes based on Night and Day time definition

### First data set
```{r}
# this step must be performed 2 times as there are some structural differences between the loaded data
cgm_all_extra <- list()
cgm_all_extra <- list(cgm_745,cgm_746,cgm_748,cgm_749,cgm_750,cgm_751,cgm_752,cgm_753,cgm_754,cgm_755,cgm_756,cgm_757,cgm_759,cgm_760,cgm_761)

for(i in 1:length(cgm_all_extra)){
cgm_all_extra[[i]] <- cgm_all_extra[[i]] %>%
  mutate(date = dmy(ID),  # this date format is differently
         time = hm(Tijd),
         time_num = as.numeric(time),
         year = year(date),
         month = month(date),
         mday = mday(date),
         wday = wday(date, label =TRUE),
         weekend = as.factor(case_when(wday == "Sa" |wday == "So" ~ "Weekend",
                                       wday == "Mo" |wday == "Di" | wday == "Mi" |wday == "Do" |wday == "Fr" ~ "Week")),
         hour = hour(time),
         minute = minute(time),
         full_date = make_datetime(year,month,mday,hour,minute),
         full_date_num = as.numeric(full_date)) %>%
  mutate(Status = as.factor(case_when(Historie_glucose>10 ~ "Hyperglycaemia",
                            Historie_glucose>=3.9 & Historie_glucose<=10 ~ "Regular",
                            Historie_glucose< 3.9 ~ "Hypoglycaemia"))) %>%
  mutate(Nocturnal_dicho = as.factor(case_when(as.numeric(time) >= 21600 ~ "Day",
                                         as.numeric(time) > 10800 & as.numeric(time) < 21600 ~ "Night_late",
                                         as.numeric(time) <= 10800 ~ "Night_early"))) %>%
  mutate(Nocturnal = as.factor(ifelse(as.numeric(time) > 21600 , "Day", "Night"))) %>%
  mutate(Noc_variability = as.factor(case_when(Nocturnal == "Night" & Status =="Hyperglycaemia" ~ "Nocturnal Hyperglycaemia",
                                        Nocturnal == "Night" & Status =="Hypoglycaemia" ~ "Nocturnal Hypoglycaemia",
                                        Status == "Regular"| Status == "Hypoglycaemia" | Nocturnal == "Day" & Status =="Hyperglycaemia" ~ "Regular"))) %>%
  mutate(Night_class_hypo = ifelse( Nocturnal == "Night" & Status =="Hypoglycaemia",1,0),
         Night_class_hyper = ifelse( Nocturnal == "Night" & Status =="Hyperglycaemia",1,0)) %>%
  mutate(Intervals_before_bedtime = as.factor(case_when(as.numeric(time) < 21600 ~ "Night_time",
                                                        as.numeric(time) > 82800 ~ "hour_0_1_before",
                                                        as.numeric(time) > 79200 & as.numeric(time) <= 82800 ~ "hours_1_2_before",
                                                        as.numeric(time) > 75600 & as.numeric(time) <= 79200 ~ "hours_2_3_before",
                                                        as.numeric(time) > 72000 & as.numeric(time) <= 75600 ~ "hours_3_4_before",
                                                        as.numeric(time) > 68400 & as.numeric(time) <= 72000 ~ "hours_4_5_before",
                                                        as.numeric(time) > 64800 & as.numeric(time) <= 68400 ~ "hours_5_6_before",
                                                        as.numeric(time) >= 21600 & as.numeric(time) <= 64800 ~ "hours_7_plus")))

}
```

### Second data set
```{r}
# Second time - with exactly the same approach
cgm_all <- list()
cgm_all <- list(cgm_574,cgm_597,cgm_598,cgm_605,cgm_606,cgm_607,cgm_609,cgm_611,cgm_612,cgm_615,cgm_616,cgm_617,cgm_618,cgm_619,cgm_621,cgm_623,cgm_624,cgm_628,cgm_629,cgm_630,cgm_632,cgm_633,cgm_634,cgm_635,cgm_636,cgm_637,cgm_638,cgm_639,cgm_640,cgm_641,cgm_642,cgm_643,cgm_644,cgm_645,cgm_646,cgm_647,cgm_648,cgm_649,cgm_650,cgm_656,cgm_658,cgm_660,cgm_661,cgm_663,cgm_664,cgm_666,cgm_669,cgm_671,cgm_674,cgm_677,cgm_1001,cgm_601,cgm_608,cgm_662,cgm_667,cgm_672,cgm_676,cgm_680,cgm_683,cgm_684,cgm_687,cgm_690,cgm_691,cgm_692,cgm_695,cgm_699,cgm_702,cgm_703,cgm_708,cgm_709,cgm_712,cgm_713,cgm_716,cgm_719,
                cgm_612,cgm_651,cgm_654,cgm_729,cgm_665)

for(i in 1:length(cgm_all)){
cgm_all[[i]] <- cgm_all[[i]] %>%
  mutate(date = ymd(ID),
         time = hm(Tijd),
         time_num = as.numeric(time),
         year = year(date),
         month = month(date),
         mday = mday(date),
         wday = wday(date, label =TRUE),
         weekend = as.factor(case_when(wday == "Sa" |wday == "So" ~ "Weekend",
                                       wday == "Mo" |wday == "Di" | wday == "Mi" |wday == "Do" |wday == "Fr" ~ "Week")),
         hour = hour(time),
         minute = minute(time),
         full_date = make_datetime(year,month,mday,hour,minute),
         full_date_num = as.numeric(full_date)) %>%
  mutate(Status = as.factor(case_when(Historie_glucose>10 ~ "Hyperglycaemia",
                            Historie_glucose>=3.9 & Historie_glucose<=10 ~ "Regular",
                            Historie_glucose< 3.9 ~ "Hypoglycaemia"))) %>%
  mutate(Nocturnal_dicho = as.factor(case_when(as.numeric(time) >= 21600 ~ "Day",
                                         as.numeric(time) > 10800 & as.numeric(time) < 21600 ~ "Night_late",
                                         as.numeric(time) <= 10800 ~ "Night_early"))) %>%
  mutate(Nocturnal = as.factor(ifelse(as.numeric(time) > 21600 , "Day", "Night"))) %>%
  mutate(Noc_variability = as.factor(case_when(Nocturnal == "Night" & Status =="Hyperglycaemia" ~ "Nocturnal Hyperglycaemia",
                                        Nocturnal == "Night" & Status =="Hypoglycaemia" ~ "Nocturnal Hypoglycaemia",
                                        Status == "Regular"| Status == "Hypoglycaemia" | Nocturnal == "Day" & Status =="Hyperglycaemia" ~ "Regular"))) %>%
  mutate(Night_class_hypo = ifelse( Nocturnal == "Night" & Status =="Hypoglycaemia",1,0),
         Night_class_hyper = ifelse( Nocturnal == "Night" & Status =="Hyperglycaemia",1,0)) %>%
  mutate(Intervals_before_bedtime = as.factor(case_when(as.numeric(time) < 21600 ~ "Night_time",
                                                        as.numeric(time) > 82800 ~ "hour_0_1_before",
                                                        as.numeric(time) > 79200 & as.numeric(time) <= 82800 ~ "hours_1_2_before",
                                                        as.numeric(time) > 75600 & as.numeric(time) <= 79200 ~ "hours_2_3_before",
                                                        as.numeric(time) > 72000 & as.numeric(time) <= 75600 ~ "hours_3_4_before",
                                                        as.numeric(time) > 68400 & as.numeric(time) <= 72000 ~ "hours_4_5_before",
                                                        as.numeric(time) > 64800 & as.numeric(time) <= 68400 ~ "hours_5_6_before",
                                                        as.numeric(time) >= 21600 & as.numeric(time) <= 64800 ~ "hours_7_plus")))

}
```

### Merging of all data sets
```{r}
# combine the two lists into a single list
cgm_all <- list(cgm_all[[1]],cgm_all[[2]],cgm_all[[3]],cgm_all[[4]],cgm_all[[5]],cgm_all[[6]],cgm_all[[7]],cgm_all[[8]],cgm_all[[9]],cgm_all[[10]],cgm_all[[11]],cgm_all[[12]],cgm_all[[13]],cgm_all[[14]],cgm_all[[15]],cgm_all[[16]],cgm_all[[17]],cgm_all[[18]],cgm_all[[19]],cgm_all[[20]],cgm_all[[21]],cgm_all[[22]],cgm_all[[23]],cgm_all[[24]],cgm_all[[25]],cgm_all[[26]],cgm_all[[27]],cgm_all[[28]],cgm_all[[29]],cgm_all[[30]],cgm_all[[31]],cgm_all[[32]],cgm_all[[33]],cgm_all[[34]],cgm_all[[35]],cgm_all[[36]], cgm_all[[37]],cgm_all[[38]],cgm_all[[39]],cgm_all[[40]],cgm_all[[41]],cgm_all[[42]],cgm_all[[43]],cgm_all[[44]],cgm_all[[45]],cgm_all[[46]],cgm_all[[47]],cgm_all[[48]],cgm_all[[49]],cgm_all[[50]],cgm_all[[51]],cgm_all[[52]],cgm_all[[53]],cgm_all[[54]],cgm_all[[55]],cgm_all[[56]],cgm_all[[57]],cgm_all[[58]],cgm_all[[59]],cgm_all[[60]],cgm_all[[61]],cgm_all[[62]],cgm_all[[63]],cgm_all[[64]],cgm_all[[65]], cgm_all[[66]],cgm_all[[67]],cgm_all[[68]],cgm_all[[69]],cgm_all[[70]],cgm_all[[71]],cgm_all[[72]],cgm_all[[73]],cgm_all[[74]],cgm_all[[75]],cgm_all[[76]],cgm_all[[77]],cgm_all[[78]],cgm_all[[79]],
 cgm_all_extra[[1]],cgm_all_extra[[2]],cgm_all_extra[[3]],cgm_all_extra[[4]],cgm_all_extra[[5]],cgm_all_extra[[6]],cgm_all_extra[[7]],cgm_all_extra[[8]],cgm_all_extra[[9]],cgm_all_extra[[10]],cgm_all_extra[[11]],cgm_all_extra[[12]],cgm_all_extra[[13]],cgm_all_extra[[14]],cgm_all_extra[[15]])
```

## Advanced pre processing
- Creation of periods - One period per patient in a single row
- Bringing all in the same format regarding start of a new period
- Exclusion criterion of at least two observations per assigned time interval per period

### Interval creation
```{r}
# there are different filtering options for the different intervals before the night time as I need to have the same starting format for each new observation
for(i in 1:length(cgm_all)){
  if(cgm_all[[i]]$Intervals_before_bedtime[1] == "hour_0_1_before" | cgm_all[[i]]$Intervals_before_bedtime[1] == "hours_1_2_before" | cgm_all[[i]]$Intervals_before_bedtime[1] == "hours_2_3_before" | cgm_all[[i]]$Intervals_before_bedtime[1] == "hours_3_4_before" | cgm_all[[i]]$Intervals_before_bedtime[1] == "hours_4_5_before" | cgm_all[[i]]$Intervals_before_bedtime[1] == "hours_5_6_before"){
    cgm_all[[i]] <- cgm_all[[i]] %>% 
      filter(!(date == date[1]))
    
    intervals <- as.numeric(seq(ymd_hms(cgm_all[[i]]$full_date[1]), by = "24 hours", length.out = length(unique(cgm_all[[i]]$date))))
    intervals <- intervals + 21600
    
    cgm_all[[i]] <- cgm_all[[i]] %>%
       mutate(periods = case_when(full_date_num <= intervals[1] ~ 0,
                                  full_date_num >= intervals[1] & full_date_num < intervals[2] ~ 1,
                                  full_date_num >= intervals[2] & full_date_num < intervals[3] ~ 2,
                                  full_date_num >= intervals[3] & full_date_num < intervals[4] ~ 3,
                                  full_date_num >= intervals[4] & full_date_num < intervals[5] ~ 4,
                                  full_date_num >= intervals[5] & full_date_num < intervals[6] ~ 5,
                                  full_date_num >= intervals[6] & full_date_num < intervals[7] ~ 6,
                                  full_date_num >= intervals[7] & full_date_num < intervals[8] ~ 7,
                                  full_date_num >= intervals[8] & full_date_num < intervals[9] ~ 8,
                                  full_date_num >= intervals[9] & full_date_num < intervals[10] ~ 9,
                                  full_date_num >= intervals[10] & full_date_num < intervals[11] ~ 10,
                                  full_date_num >= intervals[11] & full_date_num < intervals[12] ~ 11,
                                  full_date_num >= intervals[12] & full_date_num < intervals[13] ~ 12,
                                  full_date_num >= intervals[13] & full_date_num < intervals[14] ~ 13)) %>%
    filter(periods > 0)
    
  }
  
  if(cgm_all[[i]]$Intervals_before_bedtime[1] == "hours_7_plus" ){
    cgm_all[[i]] <- cgm_all[[i]] %>%
      filter(!(date == date[1] & time_num <= 60200))
    
    intervals <- as.numeric(seq(ymd_hms(cgm_all[[i]]$full_date[1]), by = "24 hours", length.out = length(unique(cgm_all[[i]]$date))))
    intervals <- intervals + 47700
    
    cgm_all[[i]] <- cgm_all[[i]] %>%
       mutate(periods = case_when(full_date_num <= intervals[1] ~ 1,
                                  full_date_num >= intervals[1] & full_date_num < intervals[2] ~ 2,
                                  full_date_num >= intervals[2] & full_date_num < intervals[3] ~ 3,
                                  full_date_num >= intervals[3] & full_date_num < intervals[4] ~ 4,
                                  full_date_num >= intervals[4] & full_date_num < intervals[5] ~ 5,
                                  full_date_num >= intervals[5] & full_date_num < intervals[6] ~ 6,
                                  full_date_num >= intervals[6] & full_date_num < intervals[7] ~ 7,
                                  full_date_num >= intervals[7] & full_date_num < intervals[8] ~ 8,
                                  full_date_num >= intervals[8] & full_date_num < intervals[9] ~ 9,
                                  full_date_num >= intervals[9] & full_date_num < intervals[10] ~ 10,
                                  full_date_num >= intervals[10] & full_date_num < intervals[11] ~ 11,
                                  full_date_num >= intervals[11] & full_date_num < intervals[12] ~ 12,
                                  full_date_num >= intervals[12] & full_date_num < intervals[13] ~ 13,
                                  full_date_num >= intervals[13] & full_date_num < intervals[14] ~ 14))
  }
  
  if(cgm_all[[i]]$Intervals_before_bedtime[1] == "Night_time"){
    cgm_all[[i]] <- cgm_all[[i]] %>%
      filter(full_date_num >= (full_date_num[1] + 60200))
    
    intervals <- as.numeric(seq(ymd_hms(cgm_all[[i]]$full_date[1]), by = "24 hours", length.out = length(unique(cgm_all[[i]]$date))))
    intervals <- intervals + 47700
    
    cgm_all[[i]] <- cgm_all[[i]] %>%
       mutate(periods = case_when(full_date_num <= intervals[1] ~ 1,
                                  full_date_num >= intervals[1] & full_date_num < intervals[2] ~ 2,
                                  full_date_num >= intervals[2] & full_date_num < intervals[3] ~ 3,
                                  full_date_num >= intervals[3] & full_date_num < intervals[4] ~ 4,
                                  full_date_num >= intervals[4] & full_date_num < intervals[5] ~ 5,
                                  full_date_num >= intervals[5] & full_date_num < intervals[6] ~ 6,
                                  full_date_num >= intervals[6] & full_date_num < intervals[7] ~ 7,
                                  full_date_num >= intervals[7] & full_date_num < intervals[8] ~ 8,
                                  full_date_num >= intervals[8] & full_date_num < intervals[9] ~ 9,
                                  full_date_num >= intervals[9] & full_date_num < intervals[10] ~ 10,
                                  full_date_num >= intervals[10] & full_date_num < intervals[11] ~ 11,
                                  full_date_num >= intervals[11] & full_date_num < intervals[12] ~ 12,
                                  full_date_num >= intervals[12] & full_date_num < intervals[13] ~ 13,
                                  full_date_num >= intervals[13] & full_date_num < intervals[14] ~ 14))
  }
}
```

### Exclusion criterion
```{r}
# delete periods with less than 1 observation per interval to have an estimate for each category
cgm_all_count <- list()
for(i in 1:length(cgm_all)){
  cgm_all_count[[i]] <- cgm_all[[i]] %>%
    group_by(periods, patient) %>%
    count(Intervals_before_bedtime, .drop = FALSE) %>%
      mutate(Low_class = ifelse(n <2,1,0),
             Sum_class = sum(Low_class)) %>%
  filter(Intervals_before_bedtime == "Night_time") %>%
  select(periods,patient,Sum_class)
  
  cgm_all[[i]] <-  merge(x=cgm_all[[i]],y=cgm_all_count[[i]], 
             by=c("periods","patient")) 
  
  cgm_all[[i]] <- cgm_all[[i]] %>% 
    filter(!(Sum_class >= 1))
}
```

# Features and outcome extraction 

## Indices calculation with Iglu

- New data set to avoid problems with original dataset
- Exclusion of Nights to only calculate indices based on day time - otherwise we would use information we wouldn't have for the normal prediction (Last before bed - LBB)
```{r}
# all days per person with valid features
iglu_data <- rbind(cgm_all[[1]],cgm_all[[2]],cgm_all[[3]],cgm_all[[4]],cgm_all[[5]],cgm_all[[6]],cgm_all[[7]],cgm_all[[8]],cgm_all[[9]],cgm_all[[10]],cgm_all[[11]],cgm_all[[12]],cgm_all[[13]],cgm_all[[14]],cgm_all[[15]],cgm_all[[16]],cgm_all[[17]],cgm_all[[18]],cgm_all[[19]],cgm_all[[20]],cgm_all[[21]],cgm_all[[22]],cgm_all[[23]],cgm_all[[24]],cgm_all[[25]],cgm_all[[26]],cgm_all[[27]],cgm_all[[28]],cgm_all[[29]],cgm_all[[30]],cgm_all[[31]],cgm_all[[32]],cgm_all[[33]],cgm_all[[34]],cgm_all[[35]],cgm_all[[36]], cgm_all[[37]],cgm_all[[38]],cgm_all[[39]],cgm_all[[40]],cgm_all[[41]],cgm_all[[42]],cgm_all[[43]],cgm_all[[44]],cgm_all[[45]],cgm_all[[46]],cgm_all[[47]],cgm_all[[48]],cgm_all[[49]],cgm_all[[50]],cgm_all[[51]],cgm_all[[52]],cgm_all[[53]],cgm_all[[54]],cgm_all[[55]],cgm_all[[56]],cgm_all[[57]],cgm_all[[58]],cgm_all[[59]],cgm_all[[60]],cgm_all[[61]],cgm_all[[62]],cgm_all[[63]],cgm_all[[64]],cgm_all[[65]],cgm_all[[66]],cgm_all[[67]],cgm_all[[68]],cgm_all[[69]],cgm_all[[70]],cgm_all[[71]],cgm_all[[72]],cgm_all[[73]],cgm_all[[74]],cgm_all[[75]],cgm_all[[76]],cgm_all[[77]],cgm_all[[78]],cgm_all[[79]],cgm_all[[80]],cgm_all[[81]],cgm_all[[82]],cgm_all[[83]],cgm_all[[84]],cgm_all[[85]],cgm_all[[86]],cgm_all[[87]],cgm_all[[88]],cgm_all[[89]],cgm_all[[90]],cgm_all[[91]],cgm_all[[92]],cgm_all[[93]],cgm_all[[94]])
```

```{r}
iglu_data$Historie_glucose[iglu_data$Nocturnal == "Night"] <- NA # to have before bed indices and not the information of the night, other studies just included it what of course increased the accuracy

iglu_processed <- iglu_data %>%
  group_split(periods)

iglu_periods <- list()
for(i in 1:length(iglu_processed)){
iglu_periods[[i]]  <- iglu_processed[[i]]  %>%
rename(id = patient, "gl_mmol/l" = Historie_glucose, time_old = time, time = full_date) %>%
  select(id,time,"gl_mmol/l")
}

for(i in 1:length(iglu_periods)){
iglu_periods[[i]]  <- process_data(iglu_periods[[i]], id = "id", timestamp = "time", glu = "gl_mmol/l")
}
```
## Indices
```{r}
hbgi <- list()
for(i in 1:length(iglu_periods)){
hbgi[[i]] <- hbgi(iglu_periods[[i]])
}

lbgi <- list()
for(i in 1:length(iglu_periods)){
lbgi[[i]] <- lbgi(iglu_periods[[i]])
}

grade <- list()
for(i in 1:length(iglu_periods)){
grade[[i]] <- grade(iglu_periods[[i]])
}

gmi <- list()
for(i in 1:length(iglu_periods)){
gmi[[i]] <- gmi(iglu_periods[[i]])
}

hyper_index <- list()
for(i in 1:length(iglu_periods)){
hyper_index[[i]] <- hyper_index(iglu_periods[[i]])
}

hypo_index <- list()
for(i in 1:length(iglu_periods)){
hypo_index[[i]] <- hypo_index(iglu_periods[[i]])
}

in_range_percent <- list()
for(i in 1:length(iglu_periods)){
in_range_percent[[i]] <- in_range_percent(iglu_periods[[i]])
}
```

```{r}
indic_per_1 <- list(in_range_percent[[1]],hypo_index[[1]],hyper_index[[1]],gmi[[1]],grade[[1]],lbgi[[1]],hbgi[[1]])
indic_per_1 <- indic_per_1 %>%
  reduce(full_join, by="id") %>%
  mutate(periods = 1)

indic_per_2 <- list(in_range_percent[[2]],hypo_index[[2]],hyper_index[[2]],gmi[[2]],grade[[2]],lbgi[[2]],hbgi[[2]])
indic_per_2 <- indic_per_2 %>%
  reduce(full_join, by="id") %>%
  mutate(periods = 2)

indic_per_3 <- list(in_range_percent[[3]],hypo_index[[3]],hyper_index[[3]],gmi[[3]],grade[[3]],lbgi[[3]],hbgi[[3]])
indic_per_3 <- indic_per_3 %>%
  reduce(full_join, by="id") %>%
  mutate(periods = 3)

indic_per_4 <- list(in_range_percent[[4]],hypo_index[[4]],hyper_index[[4]],gmi[[4]],grade[[4]],lbgi[[4]],hbgi[[4]])
indic_per_4 <- indic_per_4 %>%
  reduce(full_join, by="id") %>%
  mutate(periods = 4)

indic_per_5 <- list(in_range_percent[[5]],hypo_index[[5]],hyper_index[[5]],gmi[[5]],grade[[5]],lbgi[[5]],hbgi[[5]])
indic_per_5 <- indic_per_5 %>%
  reduce(full_join, by="id") %>%
  mutate(periods = 5)

indic_per_6 <- list(in_range_percent[[6]],hypo_index[[6]],hyper_index[[6]],gmi[[6]],grade[[6]],lbgi[[6]],hbgi[[6]])
indic_per_6 <- indic_per_6 %>%
  reduce(full_join, by="id") %>%
  mutate(periods = 6)

indic_per_7 <- list(in_range_percent[[7]],hypo_index[[7]],hyper_index[[7]],gmi[[7]],grade[[7]],lbgi[[7]],hbgi[[7]])
indic_per_7 <- indic_per_7 %>%
  reduce(full_join, by="id") %>%
  mutate(periods = 7)

indic_per_8 <- list(in_range_percent[[8]],hypo_index[[8]],hyper_index[[8]],gmi[[8]],grade[[8]],lbgi[[8]],hbgi[[8]])
indic_per_8 <- indic_per_8 %>%
  reduce(full_join, by="id") %>%
  mutate(periods = 8)

indic_per_9 <- list(in_range_percent[[9]],hypo_index[[9]],hyper_index[[9]],gmi[[9]],grade[[9]],lbgi[[9]],hbgi[[9]])
indic_per_9 <- indic_per_9 %>%
  reduce(full_join, by="id") %>%
  mutate(periods = 9)

indic_per_10 <- list(in_range_percent[[10]],hypo_index[[10]],hyper_index[[10]],gmi[[10]],grade[[10]],lbgi[[10]],hbgi[[10]])
indic_per_10 <- indic_per_10 %>%
  reduce(full_join, by="id") %>%
  mutate(periods = 10)

indic_per_11 <- list(in_range_percent[[11]],hypo_index[[11]],hyper_index[[11]],gmi[[11]],grade[[11]],lbgi[[11]],hbgi[[11]])
indic_per_11 <- indic_per_11 %>%
  reduce(full_join, by="id") %>%
  mutate(periods = 11)

indic_per_12 <- list(in_range_percent[[12]],hypo_index[[12]],hyper_index[[12]],gmi[[12]],grade[[12]],lbgi[[12]],hbgi[[12]])
indic_per_12 <- indic_per_12 %>%
  reduce(full_join, by="id") %>%
  mutate(periods = 12)

indic_per_13 <- list(in_range_percent[[13]],hypo_index[[13]],hyper_index[[13]],gmi[[13]],grade[[13]],lbgi[[13]],hbgi[[13]])
indic_per_13 <- indic_per_13 %>%
  reduce(full_join, by="id") %>%
  mutate(periods = 13)

indic_per_14 <- list(in_range_percent[[14]],hypo_index[[14]],hyper_index[[14]],gmi[[14]],grade[[14]],lbgi[[14]],hbgi[[14]])
indic_per_14 <- indic_per_14 %>%
  reduce(full_join, by="id") %>%
  mutate(periods = 14)

indic_per_15 <- list(in_range_percent[[15]],hypo_index[[15]],hyper_index[[15]],gmi[[15]],grade[[15]],lbgi[[15]],hbgi[[15]])
indic_per_15 <- indic_per_15 %>%
  reduce(full_join, by="id") %>%
  mutate(periods = 15)

indic_per <- rbind(indic_per_1,indic_per_2,indic_per_3,indic_per_4,indic_per_5,indic_per_6,indic_per_7,indic_per_8,indic_per_9,indic_per_10,indic_per_11,indic_per_12,indic_per_13,indic_per_14,indic_per_15)
indic_per <- indic_per %>%
  rename(patient = id)
```

## Features per time interval
```{r}
# This is needed to have this information in the data frame with the Historical glucose values
# basic features are created based on other studies as well as definitions of the outcome variables
for(i in 1:length(cgm_all)){
  cgm_all[[i]] <- cgm_all[[i]] %>%
    group_by(periods,Intervals_before_bedtime) %>%
    mutate(mean_glucose_ti = mean(Historie_glucose, na.rm = TRUE),
           median_glucose_ti = median(Historie_glucose, na.rm = TRUE),
           sd_glucose_ti = sd(Historie_glucose, na.rm = TRUE),
           mad_glucose_ti = mad(Historie_glucose, na.rm = TRUE),
           min_glucose_ti = min(Historie_glucose, na.rm = TRUE),
           max_glucose_ti = max(Historie_glucose, na.rm = TRUE),
           Night_class_hypo_ti = as.factor(ifelse(sum(Night_class_hypo) >= 1, 1,0)),
           Night_class_hyper_ti = as.factor(ifelse(sum(Night_class_hyper) >= 1, 1,0))) %>%
    ungroup()
}

for(i in 1:length(cgm_all)){
  cgm_all[[i]] <- cgm_all[[i]] %>%
  group_by(periods) %>%
     mutate(Night_class_hyper_30 = ifelse(sum(Night_class_hyper == 1 & Nocturnal == "Night") >= sum(Night_class_hyper == 0 & Nocturnal == "Night")*0.3, 1,0)) %>%
    ungroup()
}
```

# Working with a single data set
```{r}
# all days per person with valid features
all_patients_cgm <- rbind(cgm_all[[1]],cgm_all[[2]],cgm_all[[3]],cgm_all[[4]],cgm_all[[5]],cgm_all[[6]],cgm_all[[7]],cgm_all[[8]],cgm_all[[9]],cgm_all[[10]],cgm_all[[11]],cgm_all[[12]],cgm_all[[13]],cgm_all[[14]],cgm_all[[15]],cgm_all[[16]],cgm_all[[17]],cgm_all[[18]],cgm_all[[19]],cgm_all[[20]],cgm_all[[21]],cgm_all[[22]],cgm_all[[23]],cgm_all[[24]],cgm_all[[25]],cgm_all[[26]],cgm_all[[27]],cgm_all[[28]],cgm_all[[29]],cgm_all[[30]],cgm_all[[31]],cgm_all[[32]],cgm_all[[33]],cgm_all[[34]],cgm_all[[35]],cgm_all[[36]], cgm_all[[37]],cgm_all[[38]],cgm_all[[39]],cgm_all[[40]],cgm_all[[41]],cgm_all[[42]],cgm_all[[43]],cgm_all[[44]],cgm_all[[45]],cgm_all[[46]],cgm_all[[47]],cgm_all[[48]],cgm_all[[49]],cgm_all[[50]],cgm_all[[51]],cgm_all[[52]],cgm_all[[53]],cgm_all[[54]],cgm_all[[55]],cgm_all[[56]],cgm_all[[57]],cgm_all[[58]],cgm_all[[59]],cgm_all[[60]],cgm_all[[61]],cgm_all[[62]],cgm_all[[63]],cgm_all[[64]],cgm_all[[65]],cgm_all[[66]],cgm_all[[67]],cgm_all[[68]],cgm_all[[69]],cgm_all[[70]],cgm_all[[71]],cgm_all[[72]],cgm_all[[73]],cgm_all[[74]],cgm_all[[75]],cgm_all[[76]],cgm_all[[77]],cgm_all[[78]],cgm_all[[79]],cgm_all[[80]],cgm_all[[81]],cgm_all[[82]],cgm_all[[83]],cgm_all[[84]],cgm_all[[85]],cgm_all[[86]],cgm_all[[87]],cgm_all[[88]],cgm_all[[89]],cgm_all[[90]],cgm_all[[91]],cgm_all[[92]],cgm_all[[93]],cgm_all[[94]])
  
all_patients_cgm <- all_patients_cgm %>%
  select(patient,full_date,date,time_num,periods,wday,weekend,Nocturnal,Nocturnal_dicho,Intervals_before_bedtime,Historie_glucose,Status,Noc_variability,mean_glucose_ti,median_glucose_ti,sd_glucose_ti,mad_glucose_ti,min_glucose_ti,max_glucose_ti,Night_class_hypo_ti,Night_class_hyper_ti,Night_class_hypo,Night_class_hyper,Night_class_hyper_30)

all_patients_cgm <- all_patients_cgm %>%
 distinct(patient, full_date, .keep_all = T)
```

## Feature extraction - CGM point estimates

## Feature extraction - Slopes
```{r, warning=FALSE}
  by_noc_per <- all_patients_cgm %>%
    group_by(Nocturnal, periods,patient)
  
  slope_day <- do(by_noc_per,
   tidy(lm(Historie_glucose ~ time_num, data = .)$coef[2]))
  
  slope_day <- slope_day %>%
    filter(Nocturnal == "Day") %>%
    rename(slope_day = x) %>%
    ungroup() %>%
    select(periods,patient,slope_day)
```

```{r, warning=FALSE}
by_int_per <- all_patients_cgm %>% 
  group_by(Intervals_before_bedtime, periods,patient)

slope_interval <- do(by_int_per,
   tidy(lm(Historie_glucose ~ time_num, data = .)$coef[2]))

slope_interval <- slope_interval %>%
  filter(Intervals_before_bedtime== "hour_0_1_before" | Intervals_before_bedtime == "hours_1_2_before") %>%
  rename(slope_day = x) %>%
  ungroup() %>%
  select(periods,Intervals_before_bedtime,patient,slope_day) %>%
  pivot_wider(names_from = Intervals_before_bedtime, 
              values_from = c(slope_day), 
              names_glue = "{Intervals_before_bedtime}_{.value}") %>%
  na.omit()
```

### Extraction per Time interval
```{r}
# Feature extraction to have the features for each observation separately
cgm_per_day <- all_patients_cgm %>%
  group_by(patient,Intervals_before_bedtime,periods) %>%
  summarise(mean_glucose_ti = mean(Historie_glucose, na.rm = TRUE),
         sd_glucose_ti = sd(Historie_glucose, na.rm = TRUE),
         min_glucose_ti = min(Historie_glucose, na.rm = TRUE),
         max_glucose_ti = max(Historie_glucose, na.rm = TRUE)
         ) %>%
  ungroup()
```

### Extraction per Day time 
```{r}
# Feature extraction to have the features for each observation separately
cgm_per_day_noc <- all_patients_cgm %>%
  group_by(patient,Nocturnal_dicho,periods) %>%
  summarise(mean_glucose = mean(Historie_glucose, na.rm = TRUE),
         sd_glucose = sd(Historie_glucose, na.rm = TRUE),
         min_glucose = min(Historie_glucose, na.rm = TRUE),
         max_glucose = max(Historie_glucose, na.rm = TRUE)) %>%
  ungroup()
```

```{r}
# adding the number of hypo and hyper events in different time intervals
cgm_all_patients_noc_extra <- all_patients_cgm %>%
  group_by(patient,periods,Nocturnal_dicho) %>%
    summarise(Hyper_events = sum(Status == "Hyperglycaemia"),
         Hypo_events = sum(Status == "Hypoglycaemia"),
         Night_class_hypo_out = as.factor(ifelse(sum(Night_class_hypo) >= 1, 1,0)),
         Night_class_hyper_out = as.factor(ifelse(sum(Night_class_hyper) >= 1, 1,0)),
         Night_class_hyper_30 = ifelse(sum(Night_class_hyper == 1) >= sum(Night_class_hyper == 0)*0.3, 1,0)) %>%
  na.omit()
```

### Pivoting the data sets 
```{r}
# Features for full day and for early and late night
 cgm_all_patients_noc <- cgm_per_day_noc %>%
  dplyr::select(patient,periods,Nocturnal_dicho,mean_glucose,sd_glucose,min_glucose,max_glucose) %>%
    pivot_wider(names_from = Nocturnal_dicho, 
              values_from = c(mean_glucose,sd_glucose,min_glucose,max_glucose), 
              names_glue = "{Nocturnal_dicho}_{.value}") %>%
  na.omit()
```

```{r}
cgm_all_patients_noc_extra <- cgm_all_patients_noc_extra %>%
  dplyr::select(patient,periods,Nocturnal_dicho,Hyper_events,Hypo_events,Night_class_hypo_out,Night_class_hyper_out,Night_class_hyper_30) %>%
    pivot_wider(names_from = Nocturnal_dicho, 
              values_from = c(Hyper_events,Hypo_events,Night_class_hypo_out,Night_class_hyper_out,Night_class_hyper_30), 
              names_glue = "{Nocturnal_dicho}_{.value}") %>%
  na.omit()

cgm_all_patients_noc <- merge(cgm_all_patients_noc, cgm_all_patients_noc_extra, by=c("periods", "patient"))
```

```{r}
# features for every time interval including full night
 cgm_all_patients <- cgm_per_day %>%
  dplyr::select(patient,periods,Intervals_before_bedtime,mean_glucose_ti,sd_glucose_ti,min_glucose_ti,max_glucose_ti) %>%
    pivot_wider(names_from = Intervals_before_bedtime, 
              values_from = c(mean_glucose_ti,sd_glucose_ti,min_glucose_ti,max_glucose_ti), 
              names_glue = "{Intervals_before_bedtime}_{.value}") %>%
  na.omit()

cgm_all_patients <- merge(cgm_all_patients, cgm_all_patients_noc, by=c("periods", "patient"))
```

### Merging the data frames
```{r}
# Outcome variables defined
merge_all_patients <- all_patients_cgm %>%
  group_by(periods, patient) %>%
    summarise(Night_class_hypo_out = as.factor(ifelse(sum(Night_class_hypo) >= 1, 1,0)),
              Night_class_hyper_out = as.factor(ifelse(sum(Night_class_hyper) >= 1, 1,0)),
              Night_class_hyper_30 = ifelse(sum(Night_class_hyper == 1 & Nocturnal == "Night") >= sum(Night_class_hyper == 0 & Nocturnal == "Night")*0.3, 1,0)) %>%
  na.omit()

cgm_all_patients <- merge(cgm_all_patients, merge_all_patients, by=c("periods", "patient"))
```

### Merging Indices and Slope data sets
```{r}
# adding the indices calculated from iglu package
cgm_all_patients <- merge(cgm_all_patients, indic_per, by=c("periods", "patient"))
```

```{r}
slopes <- merge(slope_interval, slope_day, by=c("periods", "patient"))
cgm_all_patients <- merge(cgm_all_patients, slopes, by=c("periods", "patient"))
```

### Temporal location features
```{r}
# adding time based information
week_inf <- all_patients_cgm %>%
  distinct(patient, periods, .keep_all = T) %>%
  select(patient,periods,wday,weekend)

```
### Check distribution of days over patients

cgm_all_patients <- merge(cgm_all_patients, week_inf, by=c("periods", "patient"))
```{r}
#check this with 1 obs per interval
number_of_days_pp <- cgm_all_patients %>%
  group_by(patient) %>%
  summarise(n= n())
sort(number_of_days_pp$n)
nrow(number_of_days_pp)
```

```{r}
# based on this information filter out patients with less than 5 days full observations
all_patients_cgm <- all_patients_cgm %>%
  filter(!(patient == 619 | patient == 623 | patient == 654 | patient == 661 | patient == 612 | patient == 713 | patient == 755))

cgm_all_patients <- cgm_all_patients %>%
  filter(!(patient == 619 | patient == 623 | patient == 654 | patient == 661 | patient == 612 | patient == 713 | patient == 755))
```

### Save data sets
```{r}
# this data frame consists the general information about the hypoglycamic state based on the used definitions
#write.csv(all_patients_cgm,"Data_processed/all_patients_cgm.csv", row.names = FALSE)
#write.csv(cgm_all_patients,"Data_processed/cgm_all_patients.csv", row.names = FALSE)

#View(all_patients_cgm)
#View(cgm_all_patients)
```
