---
title: "Food Diaries all patients"
author: "Christoph Völtzke"
date: "2022"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Packages
```{r}
library(lubridate) # process dates
library(tidyverse) # process data
library(ggplot2) # to plot
library(readxl) # load raw data
library(readr) # load raw data
```

# Information
- In this document the food entry data is processed and features are extracted.
- Data is in very different formats and needs to first be compiled in a generalized framework.
- Raw data from each patient needs to be processed in a way that all relevant features can get extracted.
- Several features are extracted and data is saved.


# Data loading
Different formats are needed as the data is stored in different ways
```{r}
X574_voeding <- read_excel("Patients_all_sources/574/574-voeding.xlsx", 
    col_types = c("date", "text", "text", 
        "text", "text", "text", "text", "text", 
        "text", "text", "text", "text", "text", 
        "text", "text", "text", "text", "text", 
        "text", "text", "text", "text", "text", 
        "text", "text", "text", "text", "text", 
        "text", "text", "text", "text"))
X574_voeding <- X574_voeding[!is.na(X574_voeding$...1), ]
X574_voeding <- X574_voeding[,-2]
X574_voeding$...33 <- 0
X574_voeding$...34 <- 0
X574_voeding$...35<- 0
X597_voeding <- read_excel("Patients_all_sources/597/Copy of 597-voeding.xlsx")
X597_voeding <- X597_voeding[!is.na(X597_voeding$...1), ]
X598_voeding <- read_excel("Patients_all_sources/598/Copy of 598-voeding.xlsx")
X598_voeding <- X598_voeding[!is.na(X598_voeding$...1), ] 
X601_voeding <- read_excel("Patients_all_sources/601/Copy of 601-voeding.xlsx")
X601_voeding <- X601_voeding[!is.na(X601_voeding$...1), ] 
X605_voeding <- read_excel("Patients_all_sources/605/Copy of 605-voeding.xlsx")
X605_voeding <- X605_voeding[!is.na(X605_voeding$...1), ]
X606 <- read_delim("Patients_all_sources/606/606.csv", 
    delim = ";", escape_double = FALSE, trim_ws = TRUE)
X607 <- read_delim("Patients_all_sources/607/607.csv", 
    delim = "\t", escape_double = FALSE, 
    trim_ws = TRUE)
X608_voeding <- read_excel("Patients_all_sources/608/Copy of 608-voeding.xlsx")
X608_voeding <- X608_voeding[!is.na(X608_voeding$...1), ]
X609_voeding <- read_excel("Patients_all_sources/609/Copy of 609-voeding.xlsx")
X609_voeding <- X609_voeding[!is.na(X609_voeding$...1), ]
X611_voeding <- read_excel("Patients_all_sources/611/Copy of 611-voeding.xlsx")
X611_voeding <- X611_voeding[!is.na(X611_voeding$...1), ]
X612 <- read_delim("Patients_all_sources/612/612-voeding.csv", 
    delim = "\t", escape_double = FALSE, 
    trim_ws = TRUE)
X615 <- read_delim("Patients_all_sources/615/615.csv", 
    delim = ";", escape_double = FALSE, trim_ws = TRUE)
X616 <- read_delim("Patients_all_sources/616/616.csv", 
    delim = ";", escape_double = FALSE, trim_ws = TRUE)
X617 <- read_delim("Patients_all_sources/617/617.csv", 
    delim = ";", escape_double = FALSE, trim_ws = TRUE)
X618 <- read_delim("Patients_all_sources/618/618.csv", 
    delim = ";", escape_double = FALSE, trim_ws = TRUE)
X621 <- read_delim("Patients_all_sources/621/621.csv", 
    delim = ";", escape_double = FALSE, trim_ws = TRUE)
X623 <- read_delim("Patients_all_sources/623/623.csv", 
    delim = ";", escape_double = FALSE, trim_ws = TRUE)
X624 <- read_delim("Patients_all_sources/624/624.csv", 
    delim = ";", escape_double = FALSE, trim_ws = TRUE)
X628_voeding <- read_excel("Patients_all_sources/628/Copy of 628-voeding.xlsx", 
    col_types = c("date", "text", "text", 
        "text", "text", "text", "text", "text", 
        "text", "text", "text", "text", "text", 
        "text", "text", "text", "text", "text", 
        "text", "text", "text", "text", "text", 
        "text", "text", "text", "text", "text", 
        "text", "text", "text", "text"))
X628_voeding <- X628_voeding[!is.na(X628_voeding$...1), ]
X629 <- read_delim("Patients_all_sources/629/629.csv", 
    delim = ";", escape_double = FALSE, trim_ws = TRUE)
X630 <- read_delim("Patients_all_sources/630/630.csv", 
    delim = ";", escape_double = FALSE, trim_ws = TRUE)
X632 <- read_delim("Patients_all_sources/632/632-analyse.csv", 
    delim = ";", escape_double = FALSE, trim_ws = TRUE)
X633_voeding <- read_excel("Patients_all_sources/633/633-voeding.xlsx", 
    col_types = c("date", "text", "text", 
        "text", "text", "text", "text", "text", 
        "text", "text", "text", "text", "text", 
        "text", "text", "text", "text", "text", 
        "text", "text", "text", "text", "text", 
        "text", "text", "text", "text", "text", 
        "text", "text", "text", "text", "text", 
        "text", "text"))
X633_voeding <- X633_voeding[!is.na(X633_voeding$...1), ]
X633_voeding <- X633_voeding[,-2]
X634_voeding <- read_excel("Patients_all_sources/634/Copy of 634-voeding.xlsx")
X634_voeding <- X634_voeding[!is.na(X634_voeding$...1), ]
X635 <- read_delim("Patients_all_sources/635/635.csv", 
    delim = ";", escape_double = FALSE, trim_ws = TRUE)
X636_voeding <- read_excel("Patients_all_sources/636/636-voeding.xlsx", 
    col_types = c("date", "text", "text", 
        "text", "text", "text", "text", "text", 
        "text", "text", "text", "text", "text", 
        "text", "text", "text", "text", "text", 
        "text", "text", "text", "text", "text", 
        "text", "text", "text", "text", "text", 
        "text", "text", "text", "text", "text", 
        "text", "text"))
X636_voeding <- X636_voeding[!is.na(X636_voeding$...1), ]
X636_voeding <- X636_voeding[,-2]
X637 <- read_delim("Patients_all_sources/637/637.csv", 
    delim = ";", escape_double = FALSE, trim_ws = TRUE)
X638 <- read_delim("Patients_all_sources/638/638.csv", 
    delim = ";", escape_double = FALSE, trim_ws = TRUE)
X639_voeding <- read_excel("Patients_all_sources/639/639-voeding.xlsx", 
    col_types = c("date", "text", "text", 
        "text", "text", "text", "text", "text", 
        "text", "text", "text", "text", "text", 
        "text", "text", "text", "text", "text", 
        "text", "text", "text", "text", "text", 
        "text", "text", "text", "text", "text", 
        "text", "text", "text", "text", "text", 
        "text", "text"))
X639_voeding <- X639_voeding[!is.na(X639_voeding$...1), ]
X639_voeding <- X639_voeding[,-2]
X640 <- read_delim("Patients_all_sources/640/640.csv", 
    delim = ";", escape_double = FALSE, trim_ws = TRUE)
X641 <- read_delim("Patients_all_sources/641/641.csv", 
    delim = ";", escape_double = FALSE, trim_ws = TRUE)
X642_voeding <- read_excel("Patients_all_sources/642/Copy of 642-voeding.xlsx")
X642_voeding <- X642_voeding[!is.na(X642_voeding$...1), ]
X643 <- read_delim("Patients_all_sources/643/643.csv", 
    delim = ";", escape_double = FALSE, trim_ws = TRUE)
X644 <- read_delim("Patients_all_sources/644/644.csv", 
    delim = ";", escape_double = FALSE, trim_ws = TRUE)
X645 <- read_delim("Patients_all_sources/645/645-voeding.csv", 
    delim = "\t", escape_double = FALSE, 
    trim_ws = TRUE)
X646 <- read_delim("Patients_all_sources/646/646.csv", 
    delim = ";", escape_double = FALSE, trim_ws = TRUE)
X647 <- read_delim("Patients_all_sources/647/647.csv", 
    delim = ";", escape_double = FALSE, trim_ws = TRUE)
X648_voeding <- read_excel("Patients_all_sources/648/Copy of 648-voeding.xlsx")
X648_voeding <- X648_voeding[!is.na(X648_voeding$...1), ]
X649_voeding <- read_excel("Patients_all_sources/649/649-voeding.xlsx", 
    col_types = c("date", "text", "text", 
        "text", "text", "text", "text", "text", 
        "text", "text", "text", "text", "text", 
        "text", "text", "text", "text", "text", 
        "text", "text", "text", "text", "text", 
        "text", "text", "text", "text", "text", 
        "text", "text", "text", "text", "text", 
        "text", "text"))
X649_voeding <- X649_voeding[!is.na(X649_voeding$...1), ]
X649_voeding <- X649_voeding[,-2]
X650 <- read_delim("Patients_all_sources/650/650.csv", 
    delim = ";", escape_double = FALSE, trim_ws = TRUE)
X651 <- read_delim("Patients_all_sources/651/651-voeding.csv", 
    delim = "\t", escape_double = FALSE, 
    trim_ws = TRUE)
X654 <- read_delim("Patients_all_sources/654/654.csv", 
    delim = ";", escape_double = FALSE, trim_ws = TRUE)
X656 <- read_delim("Patients_all_sources/656/656.csv", 
    delim = ";", escape_double = FALSE, trim_ws = TRUE)
X658_voeding <- read_excel("Patients_all_sources/658/658-voeding.xlsx", 
    col_types = c("date", "text", "text", 
        "text", "text", "text", "text", "text", 
        "text", "text", "text", "text", "text", 
        "text", "text", "text", "text", "text", 
        "text", "text", "text", "text", "text", 
        "text", "text", "text", "text", "text", 
        "text", "text", "text", "text", "text", 
        "text", "text"))
X658_voeding <- X658_voeding[!is.na(X658_voeding$...1), ]
X658_voeding <- X658_voeding[,-2]
X660 <- read_delim("Patients_all_sources/660/660.csv", 
    delim = ";", escape_double = FALSE, trim_ws = TRUE)
X662 <- read_delim("Patients_all_sources/662/662.csv", 
    delim = ";", escape_double = FALSE, trim_ws = TRUE)
X664_voeding <- read_excel("Patients_all_sources/664/664-voeding.xlsx", 
    col_types = c("date", "text", "text", 
        "text", "text", "text", "text", "text", 
        "text", "text", "text", "text", "text", 
        "text", "text", "text", "text", "text", 
        "text", "text", "text", "text", "text", 
        "text", "text", "text", "text", "text", 
        "text", "text", "text", "text", "text", 
        "text", "text"))
X664_voeding <- X664_voeding[!is.na(X664_voeding$...1), ]
X664_voeding <- X664_voeding[,-2]
X665 <- read_delim("Patients_all_sources/665/665.csv", 
    delim = ";", escape_double = FALSE, trim_ws = TRUE)
X666_voeding <- read_excel("Patients_all_sources/666/666-voeding.xlsx", 
    col_types = c("date", "text", "text", 
        "text", "text", "text", "text", "text", 
        "text", "text", "text", "text", "text", 
        "text", "text", "text", "text", "text", 
        "text", "text", "text", "text", "text", 
        "text", "text", "text", "text", "text", 
        "text", "text", "text", "text", "text", 
        "text", "text"))
X666_voeding <- X666_voeding[!is.na(X666_voeding$...1), ]
X666_voeding <- X666_voeding[,-2]
X667 <- read_delim("Patients_all_sources/667/667.csv", 
    delim = ";", escape_double = FALSE, trim_ws = TRUE)
X669_voeding <- read_excel("Patients_all_sources/669/669-voeding.xlsx", 
    col_types = c("date", "text", "text", 
        "text", "text", "text", "text", "text", 
        "text", "text", "text", "text", "text", 
        "text", "text", "text", "text", "text", 
        "text", "text", "text", "text", "text", 
        "text", "text", "text", "text", "text", 
        "text", "text", "text", "text", "text", 
        "text", "text"))
X669_voeding <- X669_voeding[!is.na(X669_voeding$...1), ]
X669_voeding <- X669_voeding[,-2]
X671_voeding <- read_excel("Patients_all_sources/671/671-voeding.xlsx", 
    col_types = c("date", "text", "text", 
        "text", "text", "text", "text", "text", 
        "text", "text", "text", "text", "text", 
        "text", "text", "text", "text", "text", 
        "text", "text", "text", "text", "text", 
        "text", "text", "text", "text", "text", 
        "text", "text", "text", "text", "text", 
        "text", "text"))
X671_voeding <- X671_voeding[!is.na(X671_voeding$...1), ]
X671_voeding <- X671_voeding[,-2]
X672 <- read_delim("Patients_all_sources/672/672.csv", 
    delim = ";", escape_double = FALSE, trim_ws = TRUE)
X674_voeding <- read_excel("Patients_all_sources/674/674-voeding.xlsx", 
    col_types = c("date", "text", "text", 
        "text", "text", "text", "text", "text", 
        "text", "text", "text", "text", "text", 
        "text", "text", "text", "text", "text", 
        "text", "text", "text", "text", "text", 
        "text", "text", "text", "text", "text", 
        "text", "text", "text", "text", "text", 
        "text", "text"))
X674_voeding <- X674_voeding[!is.na(X674_voeding$...1), ]
X674_voeding <- X674_voeding[,-2]
X676 <- read_delim("Patients_all_sources/676/676.csv", 
    delim = ";", escape_double = FALSE, trim_ws = TRUE)
X677_voeding <- read_excel("Patients_all_sources/677/677-voeding.xlsx", 
    col_types = c("date", "text", "text", 
        "text", "text", "text", "text", "text", 
        "text", "text", "text", "text", "text", 
        "text", "text", "text", "text", "text", 
        "text", "text", "text", "text", "text", 
        "text", "text", "text", "text", "text", 
        "text", "text", "text", "text", "text", 
        "text", "text"))
X677_voeding <- X677_voeding[!is.na(X677_voeding$...1), ]
X677_voeding <- X677_voeding[,-2]
X678_voeding <- read_excel("Patients_all_sources/678/678-voeding.xlsx", 
    col_types = c("date", "text", "text", 
        "text", "text", "text", "text", "text", 
        "text", "text", "text", "text", "text", 
        "text", "text", "text", "text", "text", 
        "text", "text", "text", "text", "text", 
        "text", "text", "text", "text", "text", 
        "text", "text", "text", "text", "text", 
        "text", "text"))
X678_voeding <- X678_voeding[!is.na(X678_voeding$...1), ]
X678_voeding <- X678_voeding[,-2]
X680 <- read_delim("Patients_all_sources/680/680.csv", 
    delim = ";", escape_double = FALSE, trim_ws = TRUE)
X681_voeding <- read_excel("Patients_all_sources/681/681-voeding.xlsx", 
    col_types = c("date", "text", "text", 
        "text", "text", "text", "text", "text", 
        "text", "text", "text", "text", "text", 
        "text", "text", "text", "text", "text", 
        "text", "text", "text", "text", "text", 
        "text", "text", "text", "text", "text", 
        "text", "text", "text", "text", "text", 
        "text", "text"))
X681_voeding <- X681_voeding[!is.na(X681_voeding$...1), ]
X681_voeding <- X681_voeding[,-2]
X682_voeding <- read_excel("Patients_all_sources/682/682-voeding.xlsx", 
    col_types = c("date", "text", "text", 
        "text", "text", "text", "text", "text", 
        "text", "text", "text", "text", "text", 
        "text", "text", "text", "text", "text", 
        "text", "text", "text", "text", "text", 
        "text", "text", "text", "text", "text", 
        "text", "text", "text", "text", "text", 
        "text", "text"))
X682_voeding <- X682_voeding[!is.na(X682_voeding$...1), ]
X682_voeding <- X682_voeding[,-2]
X686_voeding <- read_excel("Patients_all_sources/686/686-voeding.xlsx", 
    col_types = c("date", "text", "text", 
        "text", "text", "text", "text", "text", 
        "text", "text", "text", "text", "text", 
        "text", "text", "text", "text", "text", 
        "text", "text", "text", "text", "text", 
        "text", "text", "text", "text", "text", 
        "text", "text", "text", "text", "text", 
        "text", "text"))
X686_voeding <- X686_voeding[!is.na(X686_voeding$...1), ]
X686_voeding <- X686_voeding[,-2]
X683 <- read_delim("Patients_all_sources/683/683.csv", 
    delim = ";", escape_double = FALSE, trim_ws = TRUE)
X684 <- read_delim("Patients_all_sources/684/684.csv", 
    delim = ";", escape_double = FALSE, trim_ws = TRUE)
X687 <- read_delim("Patients_all_sources/687/687.csv", 
    delim = ";", escape_double = FALSE, trim_ws = TRUE)
X688_voeding <- read_excel("Patients_all_sources/688/688-voeding.xlsx", 
    col_types = c("date", "text", "text", 
        "text", "text", "text", "text", "text", 
        "text", "text", "text", "text", "text", 
        "text", "text", "text", "text", "text", 
        "text", "text", "text", "text", "text", 
        "text", "text", "text", "text", "text", 
        "text", "text", "text", "text", "text", 
        "text", "text"))
X688_voeding <- X688_voeding[!is.na(X688_voeding$...1), ]
X688_voeding <- X688_voeding[,-2]
X690 <- read_delim("Patients_all_sources/690/690.csv", 
    delim = ";", escape_double = FALSE, trim_ws = TRUE)
X691 <- read_delim("Patients_all_sources/691/691.csv", 
    delim = ";", escape_double = FALSE, trim_ws = TRUE)
X692 <- read_delim("Patients_all_sources/692/692.csv", 
    delim = ";", escape_double = FALSE, trim_ws = TRUE)
X694_voeding <- read_excel("Patients_all_sources/694/694-voeding.xlsx", 
    col_types = c("date", "text", "text", 
        "text", "text", "text", "text", "text", 
        "text", "text", "text", "text", "text", 
        "text", "text", "text", "text", "text", 
        "text", "text", "text", "text", "text", 
        "text", "text", "text", "text", "text", 
        "text", "text", "text", "text", "text", 
        "text", "text"))
X694_voeding <- X694_voeding[!is.na(X694_voeding$...1), ]
X694_voeding <- X694_voeding[,-2]
X695 <- read_delim("Patients_all_sources/695/695.csv", 
    delim = ";", escape_double = FALSE, trim_ws = TRUE)
X696_voeding <- read_excel("Patients_all_sources/696/696-voeding.xlsx", 
    col_types = c("date", "text", "text", 
        "text", "text", "text", "text", "text", 
        "text", "text", "text", "text", "text", 
        "text", "text", "text", "text", "text", 
        "text", "text", "text", "text", "text", 
        "text", "text", "text", "text", "text", 
        "text", "text", "text", "text", "text", 
        "text", "text"))
X696_voeding <- X696_voeding[!is.na(X696_voeding$...1), ]
X696_voeding <- X696_voeding[,-2]
X697_voeding <- read_excel("Patients_all_sources/697/697-voeding.xlsx", 
    col_types = c("date", "text", "text", 
        "text", "text", "text", "text", "text", 
        "text", "text", "text", "text", "text", 
        "text", "text", "text", "text", "text", 
        "text", "text", "text", "text", "text", 
        "text", "text", "text", "text", "text", 
        "text", "text", "text", "text", "text", 
        "text", "text"))
X697_voeding <- X697_voeding[!is.na(X697_voeding$...1), ]
X697_voeding <- X697_voeding[,-2]
X698_voeding <- read_excel("Patients_all_sources/698/698-voeding.xlsx", 
    col_types = c("date", "text", "text", 
        "text", "text", "text", "text", "text", 
        "text", "text", "text", "text", "text", 
        "text", "text", "text", "text", "text", 
        "text", "text", "text", "text", "text", 
        "text", "text", "text", "text", "text", 
        "text", "text", "text", "text", "text", 
        "text", "text"))
X698_voeding <- X698_voeding[!is.na(X698_voeding$...1), ]
X698_voeding <- X698_voeding[,-2]
X699 <- read_delim("Patients_all_sources/699/699.csv", 
    delim = ";", escape_double = FALSE, trim_ws = TRUE)
X702 <- read_delim("Patients_all_sources/702/702.csv", 
    delim = ";", escape_double = FALSE, trim_ws = TRUE)
X703 <- read_delim("Patients_all_sources/703/703.csv", 
    delim = ";", escape_double = FALSE, trim_ws = TRUE)
X708 <- read_delim("Patients_all_sources/708/708.csv", 
    delim = ";", escape_double = FALSE, trim_ws = TRUE)
X709 <- read_delim("Patients_all_sources/709/709.csv", 
    delim = ";", escape_double = FALSE, trim_ws = TRUE)
X712 <- read_delim("Patients_all_sources/712/712.csv", 
    delim = ";", escape_double = FALSE, trim_ws = TRUE)
X713 <- read_delim("Patients_all_sources/713/713.csv", 
    delim = ";", escape_double = FALSE, trim_ws = TRUE)
X716 <- read_delim("Patients_all_sources/716/716.csv", 
    delim = ";", escape_double = FALSE, trim_ws = TRUE)
X719 <- read_delim("Patients_all_sources/719/719.csv", 
    delim = ";", escape_double = FALSE, trim_ws = TRUE)
X729 <- read_delim("Patients_all_sources/729/729.csv", 
    delim = ";", escape_double = FALSE, trim_ws = TRUE)
X745_voeding <- read_excel("Patients_all_sources/745/745-voeding.xlsx", 
    col_types = c("date", "text", "text", 
        "text", "text", "text", "text", "text", 
        "text", "text", "text", "text", "text", 
        "text", "text", "text", "text", "text", 
        "text", "text", "text", "text", "text", 
        "text", "text", "text", "text", "text", 
        "text", "text", "text", "text", "text", 
        "text", "text"))
X745_voeding <- X745_voeding[!is.na(X745_voeding$...1), ]
X745_voeding <- X745_voeding[,-2]
X746_voeding <- read_excel("Patients_all_sources/746/746-voeding.xlsx", 
    col_types = c("date", "text", "text", 
        "text", "text", "text", "text", "text", 
        "text", "text", "text", "text", "text", 
        "text", "text", "text", "text", "text", 
        "text", "text", "text", "text", "text", 
        "text", "text", "text", "text", "text", 
        "text", "text", "text", "text", "text", 
        "text", "text"))
X746_voeding <- X746_voeding[!is.na(X746_voeding$...1), ]
X746_voeding <- X746_voeding[,-2]
X748_voeding <- read_excel("Patients_all_sources/748/748-voeding.xlsx", 
    col_types = c("date", "text", "text", 
        "text", "text", "text", "text", "text", 
        "text", "text", "text", "text", "text", 
        "text", "text", "text", "text", "text", 
        "text", "text", "text", "text", "text", 
        "text", "text", "text", "text", "text", 
        "text", "text", "text", "text", "text", 
        "text", "text"))
X748_voeding <- X748_voeding[!is.na(X748_voeding$...1), ]
X748_voeding <- X748_voeding[,-2]
X749_voeding <- read_excel("Patients_all_sources/749/749-voeding.xlsx", 
    col_types = c("date", "text", "text", 
        "text", "text", "text", "text", "text", 
        "text", "text", "text", "text", "text", 
        "text", "text", "text", "text", "text", 
        "text", "text", "text", "text", "text", 
        "text", "text", "text", "text", "text", 
        "text", "text", "text", "text", "text", 
        "text", "text"))
X749_voeding <- X749_voeding[!is.na(X749_voeding$...1), ]
X749_voeding <- X749_voeding[,-2]
X750_voeding <- read_excel("Patients_all_sources/750/750-voeding.xlsx", 
    col_types = c("date", "text", "text", 
        "text", "text", "text", "text", "text", 
        "text", "text", "text", "text", "text", 
        "text", "text", "text", "text", "text", 
        "text", "text", "text", "text", "text", 
        "text", "text", "text", "text", "text", 
        "text", "text", "text", "text", "text", 
        "text", "text"))
X750_voeding <- X750_voeding[!is.na(X750_voeding$...1), ]
X750_voeding <- X750_voeding[,-2]
X751_voeding <- read_excel("Patients_all_sources/751/751-voeding.xlsx", 
    col_types = c("date", "text", "text", 
        "text", "text", "text", "text", "text", 
        "text", "text", "text", "text", "text", 
        "text", "text", "text", "text", "text", 
        "text", "text", "text", "text", "text", 
        "text", "text", "text", "text", "text", 
        "text", "text", "text", "text", "text", 
        "text", "text"))
X751_voeding <- X751_voeding[!is.na(X751_voeding$...1), ]
X751_voeding <- X751_voeding[,-2]
X752_voeding <- read_excel("Patients_all_sources/752/752-voeding.xlsx", 
    col_types = c("date", "text", "text", 
        "text", "text", "text", "text", "text", 
        "text", "text", "text", "text", "text", 
        "text", "text", "text", "text", "text", 
        "text", "text", "text", "text", "text", 
        "text", "text", "text", "text", "text", 
        "text", "text", "text", "text", "text", 
        "text", "text"))
X752_voeding <- X752_voeding[!is.na(X752_voeding$...1), ]
X752_voeding <- X752_voeding[,-2]
X753_voeding <- read_excel("Patients_all_sources/753/753-voeding.xlsx", 
    col_types = c("date", "text", "text", 
        "text", "text", "text", "text", "text", 
        "text", "text", "text", "text", "text", 
        "text", "text", "text", "text", "text", 
        "text", "text", "text", "text", "text", 
        "text", "text", "text", "text", "text", 
        "text", "text", "text", "text", "text", 
        "text", "text"))
X753_voeding <- X753_voeding[!is.na(X753_voeding$...1), ]
X753_voeding <- X753_voeding[,-2]
X754_voeding <- read_excel("Patients_all_sources/754/754-voeding.xlsx", 
    col_types = c("date", "text", "text", 
        "text", "text", "text", "text", "text", 
        "text", "text", "text", "text", "text", 
        "text", "text", "text", "text", "text", 
        "text", "text", "text", "text", "text", 
        "text", "text", "text", "text", "text", 
        "text", "text", "text", "text", "text", 
        "text", "text"))
X754_voeding <- X754_voeding[!is.na(X754_voeding$...1), ]
X754_voeding <- X754_voeding[,-2]
X755_voeding <- read_excel("Patients_all_sources/755/755-voeding.xlsx", 
    col_types = c("date", "text", "text", 
        "text", "text", "text", "text", "text", 
        "text", "text", "text", "text", "text", 
        "text", "text", "text", "text", "text", 
        "text", "text", "text", "text", "text", 
        "text", "text", "text", "text", "text", 
        "text", "text", "text", "text", "text", 
        "text", "text"))
X757_voeding <- read_excel("Patients_all_sources/757/757-voeding.xlsx", 
    col_types = c("date", "text", "text", 
        "text", "text", "text", "text", "text", 
        "text", "text", "text", "text", "text", 
        "text", "text", "text", "text", "text", 
        "text", "text", "text", "text", "text", 
        "text", "text", "text", "text", "text", 
        "text", "text", "text", "text", "text", 
        "text", "text"))
X757_voeding <- X757_voeding[!is.na(X757_voeding$...1), ]
X757_voeding <- X757_voeding[,-2]
X759_voeding <- read_excel("Patients_all_sources/759/759-voeding.xlsx", 
    col_types = c("date", "text", "text", 
        "text", "text", "text", "text", "text", 
        "text", "text", "text", "text", "text", 
        "text", "text", "text", "text", "text", 
        "text", "text", "text", "text", "text", 
        "text", "text", "text", "text", "text", 
        "text", "text", "text", "text", "text", 
        "text", "text"))
X759_voeding <- X759_voeding[!is.na(X759_voeding$...1), ]
X759_voeding <- X759_voeding[,-2]
X760_voeding <- read_excel("Patients_all_sources/760/760-voeding.xlsx", 
    col_types = c("date", "text", "text", 
        "text", "text", "text", "text", "text", 
        "text", "text", "text", "text", "text", 
        "text", "text", "text", "text", "text", 
        "text", "text", "text", "text", "text", 
        "text", "text", "text", "text", "text", 
        "text", "text", "text", "text", "text", 
        "text", "text"))
X760_voeding <- X760_voeding[!is.na(X760_voeding$...1), ]
X760_voeding <- X760_voeding[,-2]
X761_voeding <- read_excel("Patients_all_sources/761/761-voeding.xlsx", 
    col_types = c("date", "text", "text", 
        "text", "text", "text", "text", "text", 
        "text", "text", "text", "text", "text", 
        "text", "text", "text", "text", "text", 
        "text", "text", "text", "text", "text", 
        "text", "text", "text", "text", "text", 
        "text", "text", "text", "text", "text", 
        "text", "text"))
X761_voeding <- X761_voeding[!is.na(X761_voeding$...1), ]
X761_voeding <- X761_voeding[,-2]
X1001 <- read_delim("Patients_all_sources/1001/1001-voeding.csv", 
    delim = "\t", escape_double = FALSE, 
    trim_ws = TRUE)
```


Some of the data frames dont include patient IDs, so they are included manually
```{r}
X574_voeding$patient <- 574
X597_voeding$patient <- 597
X598_voeding$patient <- 598
X601_voeding$patient <- 601
X605_voeding$patient <- 605
X608_voeding$patient <- 608
X609_voeding$patient <- 609
X611_voeding$patient <- 611
X628_voeding$patient <- 628
X633_voeding$patient <- 633
X634_voeding$patient <- 634
X636_voeding$patient <- 636
X639_voeding$patient <- 639
X642_voeding$patient <- 642
X648_voeding$patient <- 648
X649_voeding$patient <- 649
X658_voeding$patient <- 658
X664_voeding$patient <- 664
X666_voeding$patient <- 666
X669_voeding$patient <- 669
X671_voeding$patient <- 671
X674_voeding$patient <- 674
X677_voeding$patient <- 677
X678_voeding$patient <- 678
X681_voeding$patient <- 681
X682_voeding$patient <- 682
X686_voeding$patient <- 686
X688_voeding$patient <- 688
X694_voeding$patient <- 694
X696_voeding$patient <- 696
X697_voeding$patient <- 697
X698_voeding$patient <- 698
X745_voeding$patient <- 745
X746_voeding$patient <- 746
X748_voeding$patient <- 748
X749_voeding$patient <- 749
X750_voeding$patient <- 750
X751_voeding$patient <- 751
X752_voeding$patient <- 752
X753_voeding$patient <- 753
X754_voeding$patient <- 754
X757_voeding$patient <- 757
X759_voeding$patient <- 759
X760_voeding$patient <- 760
X761_voeding$patient <- 761
```

# Process data frames
This is to bring the dfs in the same format. So each column is named accordingly and only columns of interest are selected

This is for the first part of patients.
```{r}
# The column names differ over the data frames so they need to be manually brought into the same format
extra_cob <- rbind(X597_voeding,X598_voeding,X601_voeding,X605_voeding,X608_voeding,X609_voeding,X611_voeding,X628_voeding,X634_voeding,X642_voeding,X648_voeding)
extra_cob <- extra_cob %>%
  rename(datetime=...1, carb=`Koolhydr (g)`,calories=`Energie (kcal)`,fat_in_g=`Vet (g)`) %>%
  select(patient,datetime,carb, calories, fat_in_g)

extra_cob2 <- rbind(X574_voeding,X745_voeding,X746_voeding,X748_voeding,X749_voeding,X750_voeding,X751_voeding,X752_voeding,X753_voeding,X754_voeding)
extra_cob2 <- extra_cob2 %>%
  rename(datetime=...1, carb=...10,calories=...7,fat_in_g=...8) %>%
  select(patient,datetime,carb, calories, fat_in_g)

extra_cob3 <- rbind(X633_voeding,X636_voeding,X639_voeding,X649_voeding,X658_voeding,X664_voeding,X666_voeding,X669_voeding,X671_voeding,X674_voeding,X677_voeding,X678_voeding,X681_voeding,X682_voeding,X686_voeding,X688_voeding,X694_voeding,X696_voeding,X697_voeding,X698_voeding,X757_voeding,X759_voeding,X760_voeding,X761_voeding)
extra_cob3 <- extra_cob3 %>%
  rename(datetime=...1, carb=...10,calories=...7,fat_in_g=...8) %>%
  select(patient,datetime,carb, calories, fat_in_g)


extra_cob <- rbind(extra_cob,extra_cob2,extra_cob3)
```

This is for the second part of patients, with very different data strucutre.
```{r}
# The date format is different between these two, therefore almost the same code is applied and brought in the same version
all_days_cob1 <- rbind(X606,X615,X616,X618,X630,X635,X650,X662,X667,X672,X676,X680,X683,X684,X687,X690,X691,X692,X695,X699,X702,X703,X708,X709,X712,X713,X716,X719,X729,X632)

# there are problems with this one variable, therefore these three lines need to be added
all_days_cob1$created_at <- 0
X665$created_at <- 0
all_days_cob1 <- rbind(all_days_cob1,X665)

all_days_cob2 <- rbind(X660,X656,X654,X647,X646,X644,X645,X643,X641,X640,X637,X638,X629,X621,X623,X624,X617,X607,
                       X612,X651,X1001)

all_days_cob1 <- all_days_cob1 %>%
  mutate(datetime = as_datetime(datetime, format="%d-%m-%Y %H:%M")) %>%
  rename(calories = "field_01001",
         fat_in_g = "field_01002",
         carb = "field_02002",
         patient = "patient_id") %>%
  select(patient,datetime,carb,calories,fat_in_g)

all_days_cob2 <- all_days_cob2 %>%
  rename(calories = "field_01001",
         fat_in_g = "field_01002",
         carb = "field_02002",
         patient = "patient_id") %>%
  select(patient,datetime,carb,calories,fat_in_g)
```

# Combine all datasets
Now we got all data in one df!
```{r}
all_days_cob <- rbind(all_days_cob1,all_days_cob2)
# combine all data frames
all_days_cob <- rbind(all_days_cob,extra_cob)
```

# Creating features based on single data set
Some formating is needed to extract all features accordingly
```{r}
all_days_cob <- all_days_cob %>%
  na.omit() %>%
  mutate(time = format(as.POSIXct(datetime), format = "%H:%M"),
         date = as.Date(datetime),
         time_num = as.numeric(hm(time)))

all_days_cob <- all_days_cob %>%
  mutate(mins_num = as.numeric(round(time_num/60)),
         Diff = 1350 - mins_num,
         Diff = replace(Diff, Diff < 0, 0),
         Diff = as.numeric(Diff),
         carb = as.numeric(carb),
         fat_in_g = as.numeric(fat_in_g),
         calories = as.numeric(calories))
```

## Apply COB formula 
Applying the COB formula as part of the feature extraction. This includes some pre set values accorrding to similar studies.,
```{r, warning=FALSE}
COB_fr <- function(c,x){c * 0.8 - as.numeric(integrate(function(t){(c*0.8*t*exp((-t)/60))/(60^2)}, lower =0, upper=x)[1])}
for(i in 1:nrow(all_days_cob)){
  all_days_cob$COB_new[i] <- COB_fr(all_days_cob$carb[i],all_days_cob$Diff[i])
}
all_days_cob <- all_days_cob %>%
  mutate(COB_new = round(COB_new,6))
```

Further features of interest get extracted.
```{r}
# extract more relevant features
food_pp_pd_1 <- all_days_cob %>%
  group_by(patient,date) %>%
  summarise(COB= sum(COB_new),
            Sum_C = sum(carb),
            Sum_F = sum(fat_in_g),
            Sum_Cal = sum(calories),
            Last_meal_time = min(Diff),
            Num_Meals=n_distinct(time))
```

# OPTIONAL - Data Summary
mall data summary about the food entry data. Also the data is saved for further analyses.
```{r}
number_of_days_pp <- food_pp_pd_1 %>%
  group_by(patient) %>%
  summarise(n= n())
sort(number_of_days_pp$n)
nrow(number_of_days_pp)
```

```{r}
#write.csv(food_pp_pd_1,"Data_processed/cob_all_patients.csv", row.names = FALSE)
```
