---
title: "Model_building_Full_data_Condition"
author: "Christoph Völtzke"
date: "2023"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Packages
```{r}
# Processing
library(readr) # read data
library(tidyverse) # data manipulation

# Methods
library(randomForest) # For RFE and Embedded
library(ranger) # RF with more hypers to tune
library(glmnet) # Lasso
library(xgboost) # Boosting
library(e1071) # SVM, most likely not used
library(kernlab) #SVM with more hypers and more sophisticated algorithms

# Feature Selection and Imbalance
library(caret) #  Hyper training
library(pROC) # AUC and ROC
library(ggforce) #needed for XGB
library(DMwR) # SMOTE in caret embedded, but need to be loaded
```

## Load Helper functions needed for analysis
```{r}
source("Functions/data_split.R")
source("Functions/confusion_matrix_function.R")
source("Functions/rf_pred_helper.R")
```

## Data set preparation
```{r}
# Load the data set with the feature set selected by the feature selection process
full_data <- read_csv("Data/Full_data/full_data_sel.csv")
full_data <- full_data %>% 
  mutate(Night_class_hypo_out = as.factor(Night_class_hypo_out))
```

## Data split train/test
**NOTE**
This is very important to consider. This script is run 3 seperate times with different seeds for the training and test data.
If you want to reproduce the exact same results you need to run the script with the following seeds:
1. Fold: Seed = 123
2. Fold: Seed = 41263
3. Fold: Seed = 2408

```{r}
full_data_split <- data_split(full_data,train_size= 0.75, seed = 123)
full_data_train <- full_data_split[[1]]
full_data_test <- full_data_split[[2]]

levels(full_data_train$Night_class_hypo_out) <- c("No_Hypo", "Hypo")
levels(full_data_test$Night_class_hypo_out) <- c("No_Hypo", "Hypo")
```
# Model tuning

## Control settings - For ALL ML algorithms
*NOTE* All control settings have a seed integrated ensuring that the results are the same if you want to reproduce them with the exact same settings. 
```{r}
# control settings are displayed for each model to ensure that each model building step is represented in a right way.
# Here it is controlled the search strategy (grid, random) and sampling methods (smote, up)
ctrl_out <- trainControl(method = "cv", 
                         number = 10,
                         classProbs = TRUE,
                         summaryFunction = twoClassSummary,
                         search = "grid",
                         allowParallel = TRUE)

ctrl_ins_smote <- trainControl(method = "cv", 
                               number = 10,
                               summaryFunction = twoClassSummary,
                               search = "grid",
                               classProbs = TRUE,
                               sampling = "smote",
                               allowParallel = TRUE)

ctrl_ins_up <- trainControl(method = "cv", 
                            number = 10,
                            classProbs = TRUE,
                            summaryFunction = twoClassSummary,
                            search = "grid",
                            sampling = "up",
                            allowParallel = TRUE)

ctrl_random <- trainControl(method = "cv",
                            number = 10,
                            classProbs = TRUE,
                            summaryFunction = twoClassSummary,
                            search = "random",
                            allowParallel = TRUE)

ctrl_random_ins_up <- trainControl(method = "cv", 
                                   number = 10,
                                   classProbs = TRUE,
                                   summaryFunction = twoClassSummary,
                                   search = "random",
                                   sampling = "up",
                                   allowParallel = TRUE)

ctrl_random_ins_smote <- trainControl(method = "cv", 
                                      number = 10,
                                      classProbs = TRUE,
                                      summaryFunction = twoClassSummary,
                                      search = "random",
                                      sampling = "smote",
                                      allowParallel = TRUE)
```

################################################################################
# RANDOM FOREST
################################################################################

## DEFAULT

```{r}
# Default tuning length of 10 is selected, data is scaled and centered
up_inside_t10 <- caret::train(Night_class_hypo_out ~ ., data = full_data_train,
                   method = "ranger",
                   metric = "ROC",
                   trControl = ctrl_ins_up,
                   verbose = FALSE,
                   preProc = c("center", "scale"),
                   tuneLength=10)

smote_inside_t10 <- caret::train(Night_class_hypo_out ~ ., data = full_data_train,
                   method = "ranger",
                   metric = "ROC",
                   trControl = ctrl_ins_smote,
                   verbose = FALSE,
                   preProc = c("center", "scale"),
                   tuneLength=10)

original_t10 <- caret::train(Night_class_hypo_out ~ ., data = full_data_train, 
                  method = "ranger",
                  metric = "ROC",
                  trControl = ctrl_out,
                  verbose = FALSE,
                  reProc = c("center", "scale"),
                  tuneLength=10)
```
## RANDOM
```{r}
# 20 random grids are selected
up_inside_ran <- caret::train(Night_class_hypo_out ~ ., data = full_data_train,
                   method = "ranger",
                   metric = "ROC",
                   trControl = ctrl_random_ins_up,
                   verbose = FALSE,
                   preProc = c("center", "scale"),
                  tuneLength=20)

smote_inside_ran <- caret::train(Night_class_hypo_out ~ ., data = full_data_train,
                   method = "ranger",
                   metric = "ROC",
                   trControl = ctrl_random_ins_smote,
                   verbose = FALSE,
                   preProc = c("center", "scale"),
                   tuneLength=20)

original_ran <- caret::train(Night_class_hypo_out ~ ., data = full_data_train, 
                  method = "ranger",
                  metric = "ROC",
                  trControl = ctrl_random,
                  verbose = FALSE,
                  reProc = c("center", "scale"),
                  tuneLength=20)
```

## Other Own Grid
```{r}
# A customized grid is used for all of the options based on the results of the two previous approaches and based on the literature
rangerGrid <-  expand.grid(mtry = c(2,5,12,18,25,30:36,41),
                           splitrule = c("extratrees","gini"),
                           min.node.size = seq(from = 1, to = 16, length.out = 5))

up_inside_own <- caret::train(Night_class_hypo_out ~ ., data = full_data_train,
                   method = "ranger",
                   metric = "ROC",
                   trControl = ctrl_ins_up,
                   verbose = FALSE,
                   preProc = c("center", "scale"),
                   tuneGrid= rangerGrid)

smote_inside_own <- caret::train(Night_class_hypo_out ~ ., data = full_data_train,
                   method = "ranger",
                   metric = "ROC",
                   trControl = ctrl_ins_smote,
                   verbose = FALSE,
                   preProc = c("center", "scale"),
                   tuneGrid= rangerGrid)

original_own <- caret::train(Night_class_hypo_out ~ ., data = full_data_train, 
                  method = "ranger",
                  metric = "ROC",
                  trControl = ctrl_out,
                  verbose = FALSE,
                  reProc = c("center", "scale"),
                  tuneGrid= rangerGrid)

```

## Predictions for Test set
```{r}
# a customized function is used which calculates all of the evaluation metrics needed and also gives the probablities in a single object
pred_original <- rf_pred(original_t10,threshold = TRUE)
pred_original_thres <- rf_pred(original_t10)

pred_smote_inside_t10 <- rf_pred(smote_inside_t10)
pred_up_inside_t10 <- rf_pred(up_inside_t10)
# Tune own
pred_up_inside_own <- rf_pred(up_inside_own)
pred_smote_inside_own <- rf_pred(smote_inside_own)
pred_original_own <- rf_pred(original_own)
# Tune random
pred_up_inside_ran <- rf_pred(up_inside_ran)
pred_smote_inside_ran <- rf_pred(smote_inside_ran)
pred_original_ran <- rf_pred(original_ran)
```

## probabilities results
Probabilities are saved to check for probabilities and also are used for later comparisons between models.
```{r}
probs <- cbind(pred_original$class_probs,pred_original_thres$class_probs,pred_smote_inside_t10$class_probs,pred_up_inside_t10$class_probs,pred_up_inside_own$class_probs,pred_smote_inside_own$class_probs,pred_original_own$class_probs,pred_up_inside_ran$class_probs,pred_smote_inside_ran$class_probs,pred_original_ran$class_probs)

probabilities_data <- cbind(full_data_test$Night_class_hypo_out,probs)
colnames(probabilities_data) <-  c("outcome","original","original_cost","smote_def","up_def",
           "up_own","smote_own","original_own","up_ran","smote_ran","original_ran")
probabilities_data <- as.data.frame(probabilities_data)
probabilities_data$outcome <- factor(probabilities_data$outcome)
levels(probabilities_data$outcome) <- c("No_Hypo", "Hypo")
probabilities_data_rf <- probabilities_data
```

## Saving the results 
The estimates are saved in a way that it is possible to differentiate between different model building decisions. 
```{r}
auc <- rbind(pred_original$auc,pred_original_thres$auc,pred_smote_inside_t10$auc,pred_up_inside_t10$auc,pred_up_inside_own$auc,pred_smote_inside_own$auc,pred_original_own$auc,pred_up_inside_ran$auc,pred_smote_inside_ran$auc,pred_original_ran$auc)

sens <- rbind(pred_original$metrics[[1]],pred_original_thres$metrics[[1]],pred_smote_inside_t10$metrics[[1]],pred_up_inside_t10$metrics[[1]],pred_up_inside_own$metrics[[1]],pred_smote_inside_own$metrics[[1]],pred_original_own$metrics[[1]],pred_up_inside_ran$metrics[[1]],pred_smote_inside_ran$metrics[[1]],pred_original_ran$metrics[[1]])

spec <- rbind(pred_original$metrics[[2]],pred_original_thres$metrics[[2]],pred_smote_inside_t10$metrics[[2]],pred_up_inside_t10$metrics[[2]],pred_up_inside_own$metrics[[2]],pred_smote_inside_own$metrics[[2]],pred_original_own$metrics[[2]],pred_up_inside_ran$metrics[[2]],pred_smote_inside_ran$metrics[[2]],pred_original_ran$metrics[[2]])

accuracy <- rbind(pred_original$metrics[[4]],pred_original_thres$metrics[[4]],pred_smote_inside_t10$metrics[[4]],pred_up_inside_t10$metrics[[4]],pred_up_inside_own$metrics[[4]],pred_smote_inside_own$metrics[[4]],pred_original_own$metrics[[4]],pred_up_inside_ran$metrics[[4]],pred_smote_inside_ran$metrics[[4]],pred_original_ran$metrics[[4]])

model <-  c("original","original_cost","smote_def","up_def",
           "up_own","smote_own","original_own","up_ran","smote_ran","original_ran")
metrics_rf <- cbind(model,auc,sens,spec,accuracy)
metrics_rf <- as.data.frame(metrics_rf)
colnames(metrics_rf) <- c("model","AUC","Sensitivity","Specificity","Accuracy")
metrics_rf <- metrics_rf %>%
  mutate(model = factor(model),
         AUC = as.numeric(AUC),
         Sensitivity = as.numeric(Sensitivity),
         Specificity = as.numeric(Specificity),
         Accuracy = as.numeric(Accuracy),
         ML = "RF",
         Condition = "Full_data") %>%
  mutate_if(is.numeric,round,digits=3)
```

*NOTE*
This procedure is repeated for each of the four ML algorithms:
1. Random Forest (as documented above)
2. Support Vector Machine
3. eXtreme Gradient Boosting
4. Lasso Logistic regression

################################################################################
# SVM
################################################################################

## DEFAULT

```{r}
svm_up_inside_t10 <- caret::train(Night_class_hypo_out ~ ., data = full_data_train,
                   method = "svmRadial",
                   metric = "ROC",
                   trControl = ctrl_ins_up,
                   verbose = FALSE,
                   preProc = c("center", "scale"),
                   tuneLength=10)

svm_smote_inside_t10 <- caret::train(Night_class_hypo_out ~ ., data = full_data_train,
                   method = "svmRadial",
                   metric = "ROC",
                   trControl = ctrl_ins_smote,
                   verbose = FALSE,
                   preProc = c("center", "scale"),
                   tuneLength=10)

svm_original_t10 <- caret::train(Night_class_hypo_out ~ ., data = full_data_train, 
                  method = "svmRadial",
                  metric = "ROC",
                  trControl = ctrl_out,
                  verbose = FALSE,
                  reProc = c("center", "scale"),
                  tuneLength=10)
```

## RANDOM
```{r}
svm_up_inside_ran <- caret::train(Night_class_hypo_out ~ ., data = full_data_train,
                   method = "svmRadial",
                   metric = "ROC",
                   trControl = ctrl_random_ins_up,
                   verbose = FALSE,
                   preProc = c("center", "scale"),
                  tuneLength=20)

svm_smote_inside_ran <- caret::train(Night_class_hypo_out ~ ., data = full_data_train,
                   method = "svmRadial",
                   metric = "ROC",
                   trControl = ctrl_random_ins_smote,
                   verbose = FALSE,
                   preProc = c("center", "scale"),
                   tuneLength=20)

svm_original_ran <- caret::train(Night_class_hypo_out ~ ., data = full_data_train, 
                  method = "svmRadial",
                  metric = "ROC",
                  trControl = ctrl_random,
                  verbose = FALSE,
                  reProc = c("center", "scale"),
                  tuneLength=20)
```

## Other Own Grid
```{r}
svm_Grid <-  expand.grid(sigma = c(seq(from = 0.001, to = 0.01, length.out = 8),seq(from = 0.011, to = 0.25, length.out = 6)),
                        C = c(seq(from = 0.1, to = 2, length.out = 12),seq(from = 3, to = 100, length.out = 12)))

svm_up_inside_own <- caret::train(Night_class_hypo_out ~ ., data = full_data_train,
                   method = "svmRadial",
                   metric = "ROC",
                   trControl = ctrl_ins_up,
                   verbose = FALSE,
                   preProc = c("center", "scale"),
                   tuneGrid= svm_Grid)

svm_smote_inside_own <- caret::train(Night_class_hypo_out ~ ., data = full_data_train,
                   method = "svmRadial",
                   metric = "ROC",
                   trControl = ctrl_ins_smote,
                   verbose = FALSE,
                   preProc = c("center", "scale"),
                   tuneGrid= svm_Grid)

svm_original_own <- caret::train(Night_class_hypo_out ~ ., data = full_data_train, 
                  method = "svmRadial",
                  metric = "ROC",
                  trControl = ctrl_out,
                  verbose = FALSE,
                  reProc = c("center", "scale"),
                  tuneGrid= svm_Grid)
```

## Predictions for Test set
```{r}
pred_svm_original <- rf_pred(svm_original_t10,threshold = TRUE)
pred_svm_original_thres <- rf_pred(svm_original_t10)

pred_svm_smote_inside_t10 <- rf_pred(svm_smote_inside_t10)
pred_svm_up_inside_t10 <- rf_pred(svm_up_inside_t10)
# Tune own
pred_svm_up_inside_own <- rf_pred(svm_up_inside_own)
pred_svm_smote_inside_own <- rf_pred(svm_smote_inside_own)
pred_svm_original_own <- rf_pred(svm_original_own)
# Tune random
pred_svm_up_inside_ran <- rf_pred(svm_up_inside_ran)
pred_svm_smote_inside_ran <- rf_pred(svm_smote_inside_ran)
pred_svm_original_ran <- rf_pred(svm_original_ran)
```

## probabilities
```{r}
probs <- cbind(pred_svm_original$class_probs,pred_svm_original_thres$class_probs,pred_svm_smote_inside_t10$class_probs,pred_svm_up_inside_t10$class_probs,pred_svm_up_inside_own$class_probs,pred_svm_smote_inside_own$class_probs,pred_svm_original_own$class_probs,pred_svm_up_inside_ran$class_probs,pred_svm_smote_inside_ran$class_probs,pred_svm_original_ran$class_probs)

probabilities_data <- cbind(full_data_test$Night_class_hypo_out,probs)
colnames(probabilities_data) <- c("outcome","original","original_cost","smote_def","up_def",
           "up_own","smote_own","original_own","up_ran","smote_ran","original_ran")
probabilities_data <- as.data.frame(probabilities_data)
probabilities_data$outcome <- factor(probabilities_data$outcome)
levels(probabilities_data$outcome) <- c("No_Hypo", "Hypo")
probabilities_data_svm <- probabilities_data
```

## Saving the results
```{r}
auc <- rbind(pred_svm_original$auc,pred_svm_original_thres$auc,pred_svm_smote_inside_t10$auc,pred_svm_up_inside_t10$auc,pred_svm_up_inside_own$auc,pred_svm_smote_inside_own$auc,pred_svm_original_own$auc,pred_svm_up_inside_ran$auc,pred_svm_smote_inside_ran$auc,pred_svm_original_ran$auc)

sens <- rbind(pred_svm_original$metrics[[1]],pred_svm_original_thres$metrics[[1]],pred_svm_smote_inside_t10$metrics[[1]],pred_svm_up_inside_t10$metrics[[1]],pred_svm_up_inside_own$metrics[[1]],pred_svm_smote_inside_own$metrics[[1]],pred_svm_original_own$metrics[[1]],pred_svm_up_inside_ran$metrics[[1]],pred_svm_smote_inside_ran$metrics[[1]],pred_svm_original_ran$metrics[[1]])

spec <- rbind(pred_svm_original$metrics[[2]],pred_svm_original_thres$metrics[[2]],pred_svm_smote_inside_t10$metrics[[2]],pred_svm_up_inside_t10$metrics[[2]],pred_svm_up_inside_own$metrics[[2]],pred_svm_smote_inside_own$metrics[[2]],pred_svm_original_own$metrics[[2]],pred_svm_up_inside_ran$metrics[[2]],pred_svm_smote_inside_ran$metrics[[2]],pred_svm_original_ran$metrics[[2]])

accuracy <- rbind(pred_svm_original$metrics[[4]],pred_svm_original_thres$metrics[[4]],pred_svm_smote_inside_t10$metrics[[4]],pred_svm_up_inside_t10$metrics[[4]],pred_svm_up_inside_own$metrics[[4]],pred_svm_smote_inside_own$metrics[[4]],pred_svm_original_own$metrics[[4]],pred_svm_up_inside_ran$metrics[[4]],pred_svm_smote_inside_ran$metrics[[4]],pred_svm_original_ran$metrics[[4]])

model <-  c("original","original_cost","smote_def","up_def",
           "up_own","smote_own","original_own","up_ran","smote_ran","original_ran")
metrics_svm <- cbind(model,auc,sens,spec,accuracy)
metrics_svm <- as.data.frame(metrics_svm)
colnames(metrics_svm) <- c("model","AUC","Sensitivity","Specificity","Accuracy")
metrics_svm <- metrics_svm %>%
  mutate(model = factor(model),
         AUC = as.numeric(AUC),
         Sensitivity = as.numeric(Sensitivity),
         Specificity = as.numeric(Specificity),
         Accuracy = as.numeric(Accuracy),
         ML = "SVM",
         Condition = "Full_data") %>%
  mutate_if(is.numeric,round,digits=3)
```

################################################################################
# XGB
################################################################################

## DEFAULT

```{r}
# Due to high computational time the default length is reduced to 5 compared to the other MLs
xgb_up_inside_t10 <- caret::train(Night_class_hypo_out ~ ., data = full_data_train,
                   method = "xgbTree",
                   metric = "ROC",
                   trControl = ctrl_ins_up,
                   verbose = FALSE,
                   preProc = c("center", "scale"),
                   tuneLength=5)

xgb_smote_inside_t10 <- caret::train(Night_class_hypo_out ~ ., data = full_data_train,
                   method = "xgbTree",
                   metric = "ROC",
                   trControl = ctrl_ins_smote,
                   verbose = FALSE,
                   preProc = c("center", "scale"),
                   tuneLength=5)

xgb_original_t10 <- caret::train(Night_class_hypo_out ~ ., data = full_data_train, 
                  method = "xgbTree",
                  metric = "ROC",
                  trControl = ctrl_out,
                  verbose = FALSE,
                  reProc = c("center", "scale"),
                  tuneLength=5)
```

## RANDOM
```{r}
# Due to high computational time the default length is reduced to 12 compared to the other MLs
xgb_up_inside_ran <- caret::train(Night_class_hypo_out ~ ., data = full_data_train,
                   method = "xgbTree",
                   metric = "ROC",
                   trControl = ctrl_random_ins_up,
                   verbose = FALSE,
                   preProc = c("center", "scale"),
                  tuneLength=12)

xgb_smote_inside_ran <- caret::train(Night_class_hypo_out ~ ., data = full_data_train,
                   method = "xgbTree",
                   metric = "ROC",
                   trControl = ctrl_random_ins_smote,
                   verbose = FALSE,
                   preProc = c("center", "scale"),
                   tuneLength=12)

xgb_original_ran <- caret::train(Night_class_hypo_out ~ ., data = full_data_train, 
                  method = "xgbTree",
                  metric = "ROC",
                  trControl = ctrl_random,
                  verbose = FALSE,
                  reProc = c("center", "scale"),
                  tuneLength=12)
```

## Other Own Grid
```{r}
xgb_Grid <-  expand.grid(eta = seq(from = 0.3, to = 0.8, length.out = 3),
                         max_depth = c(2,3,5),
                         min_child_weight = c(1,2),
                         subsample = seq(from = 0.4, to = 1, length.out = 3),
                         colsample_bytree = seq(from = 0.3, to = 0.8, length.out = 3),
                         nrounds = seq(from = 50, to = 500, length.out = 3),
                         gamma = seq(from = 0, to = 1.5, length.out = 2))

xgb_up_inside_own <- caret::train(Night_class_hypo_out ~ ., data = full_data_train,
                   method = "xgbTree",
                   metric = "ROC",
                   trControl = ctrl_ins_up,
                   verbose = FALSE,
                   preProc = c("center", "scale"),
                   tuneGrid= xgb_Grid)

xgb_smote_inside_own <- caret::train(Night_class_hypo_out ~ ., data = full_data_train,
                   method = "xgbTree",
                   metric = "ROC",
                   trControl = ctrl_ins_smote,
                   verbose = FALSE,
                   preProc = c("center", "scale"),
                   tuneGrid= xgb_Grid)

xgb_original_own <- caret::train(Night_class_hypo_out ~ ., data = full_data_train, 
                  method = "xgbTree",
                  metric = "ROC",
                  trControl = ctrl_out,
                  verbose = FALSE,
                  reProc = c("center", "scale"),
                  tuneGrid= xgb_Grid)
```

## Predictions for Test set
```{r}
pred_xgb_original <- rf_pred(xgb_original_t10,threshold = TRUE)
pred_xgb_original_thres <- rf_pred(xgb_original_t10)

pred_xgb_smote_inside_t10 <- rf_pred(xgb_smote_inside_t10)
pred_xgb_up_inside_t10 <- rf_pred(xgb_up_inside_t10)
# Tune own
pred_xgb_up_inside_own <- rf_pred(xgb_up_inside_own)
pred_xgb_smote_inside_own <- rf_pred(xgb_smote_inside_own)
pred_xgb_original_own <- rf_pred(xgb_original_own)
# Tune random
pred_xgb_up_inside_ran <- rf_pred(xgb_up_inside_ran)
pred_xgb_smote_inside_ran <- rf_pred(xgb_smote_inside_ran)
pred_xgb_original_ran <- rf_pred(xgb_original_ran)
pred_xgb_smote_inside_ran
```

## probabilities
```{r}
probs <- cbind(pred_xgb_original$class_probs,pred_xgb_original_thres$class_probs,pred_xgb_smote_inside_t10$class_probs,pred_xgb_up_inside_t10$class_probs,pred_xgb_up_inside_own$class_probs,pred_xgb_smote_inside_own$class_probs,pred_xgb_original_own$class_probs,pred_xgb_up_inside_ran$class_probs,pred_xgb_smote_inside_ran$class_probs,pred_xgb_original_ran$class_probs)

probabilities_data <- cbind(full_data_test$Night_class_hypo_out,probs)
colnames(probabilities_data) <-  c("outcome","original","original_cost","smote_def","up_def",
           "up_own","smote_own","original_own","up_ran","smote_ran","original_ran")
probabilities_data <- as.data.frame(probabilities_data)
probabilities_data$outcome <- factor(probabilities_data$outcome)
levels(probabilities_data$outcome) <- c("No_Hypo", "Hypo")
probabilities_data_xgb <- probabilities_data
```

## Saving the results
```{r}
auc <- rbind(pred_xgb_original$auc,pred_xgb_original_thres$auc,pred_xgb_smote_inside_t10$auc,pred_xgb_up_inside_t10$auc,pred_xgb_up_inside_own$auc,pred_xgb_smote_inside_own$auc,pred_xgb_original_own$auc,pred_xgb_up_inside_ran$auc,pred_xgb_smote_inside_ran$auc,pred_xgb_original_ran$auc)

sens <- rbind(pred_xgb_original$metrics[[1]],pred_xgb_original_thres$metrics[[1]],pred_xgb_smote_inside_t10$metrics[[1]],pred_xgb_up_inside_t10$metrics[[1]],pred_xgb_up_inside_own$metrics[[1]],pred_xgb_smote_inside_own$metrics[[1]],pred_xgb_original_own$metrics[[1]],pred_xgb_up_inside_ran$metrics[[1]],pred_xgb_smote_inside_ran$metrics[[1]],pred_xgb_original_ran$metrics[[1]])

spec <- rbind(pred_xgb_original$metrics[[2]],pred_xgb_original_thres$metrics[[2]],pred_xgb_smote_inside_t10$metrics[[2]],pred_xgb_up_inside_t10$metrics[[2]],pred_xgb_up_inside_own$metrics[[2]],pred_xgb_smote_inside_own$metrics[[2]],pred_xgb_original_own$metrics[[2]],pred_xgb_up_inside_ran$metrics[[2]],pred_xgb_smote_inside_ran$metrics[[2]],pred_xgb_original_ran$metrics[[2]])

accuracy <- rbind(pred_xgb_original$metrics[[4]],pred_xgb_original_thres$metrics[[4]],pred_xgb_smote_inside_t10$metrics[[4]],pred_xgb_up_inside_t10$metrics[[4]],pred_xgb_up_inside_own$metrics[[4]],pred_xgb_smote_inside_own$metrics[[4]],pred_xgb_original_own$metrics[[4]],pred_xgb_up_inside_ran$metrics[[4]],pred_xgb_smote_inside_ran$metrics[[4]],pred_xgb_original_ran$metrics[[4]])

model <-  c("original","original_cost","smote_def","up_def",
           "up_own","smote_own","original_own","up_ran","smote_ran","original_ran")
metrics_xgb <- cbind(model,auc,sens,spec,accuracy)
metrics_xgb <- as.data.frame(metrics_xgb)
colnames(metrics_xgb) <- c("model","AUC","Sensitivity","Specificity","Accuracy")
metrics_xgb <- metrics_xgb %>%
  mutate(model = factor(model),
         AUC = as.numeric(AUC),
         Sensitivity = as.numeric(Sensitivity),
         Specificity = as.numeric(Specificity),
         Accuracy = as.numeric(Accuracy),
         ML = "XGB",
         Condition = "Full_data") %>%
  mutate_if(is.numeric,round,digits=3)
```

################################################################################
# Lasso
################################################################################

## DEFAULT

```{r}
lasso_up_inside_t10 <- caret::train(Night_class_hypo_out ~ ., data = full_data_train,
                   method = "glmnet",
                   metric = "ROC",
                   trControl = ctrl_ins_up,
                   verbose = FALSE,
                   preProc = c("center", "scale"),
                   tuneLength=10)

lasso_smote_inside_t10 <- caret::train(Night_class_hypo_out ~ ., data = full_data_train,
                   method = "glmnet",
                   metric = "ROC",
                   trControl = ctrl_ins_smote,
                   verbose = FALSE,
                   preProc = c("center", "scale"),
                   tuneLength=10)

lasso_original_t10 <- caret::train(Night_class_hypo_out ~ ., data = full_data_train, 
                  method = "glmnet",
                  metric = "ROC",
                  trControl = ctrl_out,
                  verbose = FALSE,
                  reProc = c("center", "scale"),
                  tuneLength=10)
```

## RANDOM
```{r}
lasso_up_inside_ran <- caret::train(Night_class_hypo_out ~ ., data = full_data_train,
                   method = "glmnet",
                   metric = "ROC",
                   trControl = ctrl_random_ins_up,
                   verbose = FALSE,
                   preProc = c("center", "scale"),
                  tuneLength=20)

lasso_smote_inside_ran <- caret::train(Night_class_hypo_out ~ ., data = full_data_train,
                   method = "glmnet",
                   metric = "ROC",
                   trControl = ctrl_random_ins_smote,
                   verbose = FALSE,
                   preProc = c("center", "scale"),
                   tuneLength=20)

lasso_original_ran <- caret::train(Night_class_hypo_out ~ ., data = full_data_train, 
                  method = "glmnet",
                  metric = "ROC",
                  trControl = ctrl_random,
                  verbose = FALSE,
                  reProc = c("center", "scale"),
                  tuneLength=20)
```

## Other Own Grid
```{r}
lasso_Grid <-  expand.grid(alpha  = seq(from = 0.1, to = 1, length.out = 20),
                         lambda = seq(from = 0.00001, to = 0.1, length.out = 30))

lasso_up_inside_own <- caret::train(Night_class_hypo_out ~ ., data = full_data_train,
                   method = "glmnet",
                   metric = "ROC",
                   trControl = ctrl_ins_up,
                   verbose = FALSE,
                   preProc = c("center", "scale"),
                   tuneGrid= lasso_Grid)

lasso_smote_inside_own <- caret::train(Night_class_hypo_out ~ ., data = full_data_train,
                   method = "glmnet",
                   metric = "ROC",
                   trControl = ctrl_ins_smote,
                   verbose = FALSE,
                   preProc = c("center", "scale"),
                   tuneGrid= lasso_Grid)

lasso_original_own <- caret::train(Night_class_hypo_out ~ ., data = full_data_train, 
                  method = "glmnet",
                  metric = "ROC",
                  trControl = ctrl_out,
                  verbose = FALSE,
                  reProc = c("center", "scale"),
                  tuneGrid= lasso_Grid)
```

## Predictions for Test set
```{r}
pred_lasso_original <- rf_pred(lasso_original_t10,threshold = TRUE)
pred_lasso_original_thres <- rf_pred(lasso_original_t10)

pred_lasso_smote_inside_t10 <- rf_pred(lasso_smote_inside_t10)
pred_lasso_up_inside_t10 <- rf_pred(lasso_up_inside_t10)
# Tune own
pred_lasso_up_inside_own <- rf_pred(lasso_up_inside_own)
pred_lasso_smote_inside_own <- rf_pred(lasso_smote_inside_own)
pred_lasso_original_own <- rf_pred(lasso_original_own)
# Tune random
pred_lasso_up_inside_ran <- rf_pred(lasso_up_inside_ran)
pred_lasso_smote_inside_ran <- rf_pred(lasso_smote_inside_ran)
pred_lasso_original_ran <- rf_pred(lasso_original_ran)
```

## probabilities
```{r}
probs <- cbind(pred_lasso_original$class_probs,pred_lasso_original_thres$class_probs,pred_lasso_smote_inside_t10$class_probs,pred_lasso_up_inside_t10$class_probs,pred_lasso_up_inside_own$class_probs,pred_lasso_smote_inside_own$class_probs,pred_lasso_original_own$class_probs,pred_lasso_up_inside_ran$class_probs,pred_lasso_smote_inside_ran$class_probs,pred_lasso_original_ran$class_probs)

probabilities_data <- cbind(full_data_test$Night_class_hypo_out,probs)
colnames(probabilities_data) <-  c("outcome","original","original_cost","smote_def","up_def",
           "up_own","smote_own","original_own","up_ran","smote_ran","original_ran")
probabilities_data <- as.data.frame(probabilities_data)
probabilities_data$outcome <- factor(probabilities_data$outcome)
levels(probabilities_data$outcome) <- c("No_Hypo", "Hypo")
probabilities_data_lasso <- probabilities_data
```

## Saving the results
```{r}
auc <- rbind(pred_lasso_original$auc,pred_lasso_original_thres$auc,pred_lasso_smote_inside_t10$auc,pred_lasso_up_inside_t10$auc,pred_lasso_up_inside_own$auc,pred_lasso_smote_inside_own$auc,pred_lasso_original_own$auc,pred_lasso_up_inside_ran$auc,pred_lasso_smote_inside_ran$auc,pred_lasso_original_ran$auc)

sens <- rbind(pred_lasso_original$metrics[[1]],pred_lasso_original_thres$metrics[[1]],pred_lasso_smote_inside_t10$metrics[[1]],pred_lasso_up_inside_t10$metrics[[1]],pred_lasso_up_inside_own$metrics[[1]],pred_lasso_smote_inside_own$metrics[[1]],pred_lasso_original_own$metrics[[1]],pred_lasso_up_inside_ran$metrics[[1]],pred_lasso_smote_inside_ran$metrics[[1]],pred_lasso_original_ran$metrics[[1]])

spec <- rbind(pred_lasso_original$metrics[[2]],pred_lasso_original_thres$metrics[[2]],pred_lasso_smote_inside_t10$metrics[[2]],pred_lasso_up_inside_t10$metrics[[2]],pred_lasso_up_inside_own$metrics[[2]],pred_lasso_smote_inside_own$metrics[[2]],pred_lasso_original_own$metrics[[2]],pred_lasso_up_inside_ran$metrics[[2]],pred_lasso_smote_inside_ran$metrics[[2]],pred_lasso_original_ran$metrics[[2]])

accuracy <- rbind(pred_lasso_original$metrics[[4]],pred_lasso_original_thres$metrics[[4]],pred_lasso_smote_inside_t10$metrics[[4]],pred_lasso_up_inside_t10$metrics[[4]],pred_lasso_up_inside_own$metrics[[4]],pred_lasso_smote_inside_own$metrics[[4]],pred_lasso_original_own$metrics[[4]],pred_lasso_up_inside_ran$metrics[[4]],pred_lasso_smote_inside_ran$metrics[[4]],pred_lasso_original_ran$metrics[[4]])

model <-  c("original","original_cost","smote_def","up_def",
           "up_own","smote_own","original_own","up_ran","smote_ran","original_ran")
metrics_lasso <- cbind(model,auc,sens,spec,accuracy)
metrics_lasso <- as.data.frame(metrics_lasso)
colnames(metrics_lasso) <- c("model","AUC","Sensitivity","Specificity","Accuracy")
metrics_lasso <- metrics_lasso %>%
  mutate(model = factor(model),
         AUC = as.numeric(AUC),
         Sensitivity = as.numeric(Sensitivity),
         Specificity = as.numeric(Specificity),
         Accuracy = as.numeric(Accuracy),
         ML = "Lasso",
         Condition = "Full_data") %>%
  mutate_if(is.numeric,round,digits=3)
```

# COMBINE ALL RESULTS
All results are combined and saved in multiple data sets / lists.
```{r}
all_models_full_cgm <- rbind(metrics_rf,metrics_xgb,metrics_lasso,metrics_svm)
#write.csv(all_models_full_cgm,"Data/Model_results/all_models_cgm_full_123.csv", row.names = FALSE)
#probs_full_cgm <- list(rf= probabilities_data_rf, svm = probabilities_data_svm,xgb= probabilities_data_xgb, lasso =probabilities_data_lasso)
#saveRDS(probs_full_cgm, file = "Data/Model_results/Trained_models/probs_full_123.RData")
```


