---
title: "Final models and Tables/Figures"
author: "Christoph Völtzke"
date: "2023"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## packages
```{r}
library(readr) # read data
library(tidyverse) # data manipulation
library(RColorBrewer) # color palettes
library(xtable) # latex code for main results
library(yardstick) # ROC curves with multiple curves
library(stargazer) # latex code for descriptive stats
library(data.table) # data frame preparation for descriptive stats
```

# Information
- In this document the results of the data modeling are combined over the 3 folds and estimates are caluclated. 
- Then the results table of the report is created with final latex code in the end.
- Then the Figure for the ROC curves over the 3 folds for each ML and data condition is created. With the final being a plot. 
- Then the table for the descriptive data is included. Here the full patient data is used and not only the training or test data. 
- Last an optional section is included with some further visualizations to understand the data.
  - This includes:
  - Calibration curves for multiple models
  - Outcome frequency as a Figure
  - CGM continuous profiles as a Figure to see how it fluctuates over the monitored period
- A Session Info command is the last code chunk as this is the last needed script to be run for this study.

## Load Helper functions needed for analysis
```{r}
source("Functions/calibration_helper.R") # helper function to make calibration plots
```

## Full data
Load all results on evaluation metrics obtained by the model building scripts when run with different folds indicated by document name.
```{r}
# All produced data frames from the Model building docs
full <- read_csv("Data/Model_results/all_models_full_123.csv") # 1. fold
life <- read_csv("Data/Model_results/all_models_lifestyle_123.csv") # 1. fold

full_1 <- read_csv("Data/Model_results/all_models_full_41263.csv") # 2. fold
life_1 <- read_csv("Data/Model_results/all_models_lifestyle_41263.csv") # 2. fold

full_2 <- read_csv("Data/Model_results/all_models_full_2408.csv") # 3. fold
life_2 <- read_csv("Data/Model_results/all_models_lifestyle_2408.csv") # 3. fold
```

# Creating Estimates over folds
Get the mean and SD over the three folds for each of the evaluation metrics.
```{r}
all_full <- rbind(full,full_1,full_2)

all_full <- all_full %>%
  group_by(model,Condition,ML) %>%
  summarise(mean_AUC = round(mean(AUC),3),
            mean_SENS = round(mean(Sensitivity),3),
            mean_SPEC = round(mean(Specificity),3),
            sd_AUC = round(sd(AUC),3),
            sd_SENS = round(sd(Sensitivity),3),
            sd_SPEC = round(sd(Specificity),3))

all_life <- rbind(life,life_1,life_2)

all_life <- all_life %>%
  group_by(model,Condition,ML) %>%
  summarise(mean_AUC = round(mean(AUC),4),
            mean_SENS = round(mean(Sensitivity),4),
            mean_SPEC = round(mean(Specificity),4),
            sd_AUC = round(sd(AUC),4),
            sd_SENS = round(sd(Sensitivity),4),
            sd_SPEC = round(sd(Specificity),4))

all_full_cross <-  rbind(all_full,all_life)
```

# Table of Model Results
This is the pre-processing for the table with the best 32 models depicted in the report.
# Pre-Processing for Table
```{r}
data <- all_full_cross 

data <- data %>%
  extract(model,c("Resample", "grid"), "([[:alnum:]]+)_([[:alnum:]]+)",remove=FALSE) # make columns in a way that the best model performance across all ML, Sampling and Tuning Strategy, and data condition

data$Resample[is.na(data$Resample)] <- "original"
data$grid[is.na(data$grid)] <- "thres"

data <- data %>%
  mutate(Thres = ifelse(grid =="thres",TRUE,FALSE)) %>% # Always identify the no cost-sensitive learning models as these are always selected
  select(-model)

data <- data %>%
  group_by(Resample,ML,Condition) %>%
  mutate(Best = ifelse(mean_AUC == max(mean_AUC),TRUE,FALSE)) %>% # first filter based on best AUC
  filter(Best == TRUE | Thres == TRUE) 

data <- data %>%
  group_by(Resample,ML,Condition, Thres) %>%
  mutate(Best_Sp = ifelse(mean_SENS == max(mean_SENS),TRUE,FALSE)) %>% # next filter based on best SENS
  filter(Best_Sp == TRUE | Thres == TRUE)

data <- data %>%
  group_by(Resample,ML,Condition, Thres) %>%
  mutate(Best_Sens = ifelse(mean_SPEC == max(mean_SPEC),TRUE,FALSE)) %>% # last filter based on best SPEC
  filter(Best_Sens == TRUE | Thres == TRUE)
```

## Pre processing with only best 32 models
Models are ordered in the way that it is strucured across all MLs
```{r}
data <- data %>%
  ungroup()

# Make sure for each ML that the models are in the right order in which I want them to be depicted in the table
# This step is repeated for each of the 4 MLs

data_long_rf <- data %>% 
  filter(ML == "RF") %>%
  mutate(Order = case_when(Condition == "Full_data" & Resample == "original" & Thres == TRUE ~ 1,
                           Condition == "Full_data" & Resample == "original" & Thres == FALSE ~ 2,
                           Condition == "Full_data" & Resample == "smote" & Thres == FALSE ~ 3,
                           Condition == "Full_data" & Resample == "up" & Thres == FALSE ~ 4,
                           Condition == "Lifestyle" & Resample == "original" & Thres == TRUE ~ 5,
                           Condition == "Lifestyle" & Resample == "original" & Thres == FALSE ~ 6,
                           Condition == "Lifestyle" & Resample == "smote" & Thres == FALSE ~ 7,
                           Condition == "Lifestyle" & Resample == "up" & Thres == FALSE ~ 8)) %>%
  arrange(Order) %>% distinct(Order, .keep_all = TRUE) # If a model would produce the exact same estimates for multiple models only one is chosen.

colnames(data_long_rf) <- paste(colnames(data_long_rf),"RF",sep="_")

data_long_rf <- data_long_rf %>%
  select(mean_AUC_RF,mean_SENS_RF,mean_SPEC_RF,
         sd_AUC_RF,sd_SENS_RF,sd_SPEC_RF)

data_long_svm <- data %>%
  filter(ML == "SVM") %>%
  mutate(Order = case_when(Condition == "Full_data" & Resample == "original" & Thres == TRUE ~ 1,
                           Condition == "Full_data" & Resample == "original" & Thres == FALSE ~ 2,
                           Condition == "Full_data" & Resample == "smote" & Thres == FALSE ~ 3,
                           Condition == "Full_data" & Resample == "up" & Thres == FALSE ~ 4,
                           Condition == "Lifestyle" & Resample == "original" & Thres == TRUE ~ 5,
                           Condition == "Lifestyle" & Resample == "original" & Thres == FALSE ~ 6,
                           Condition == "Lifestyle" & Resample == "smote" & Thres == FALSE ~ 7,
                           Condition == "Lifestyle" & Resample == "up" & Thres == FALSE ~ 8)) %>%
  arrange(Order) %>% distinct(Order, .keep_all = TRUE)

colnames(data_long_svm) <- paste(colnames(data_long_svm),"SVM",sep="_")

data_long_svm <- data_long_svm %>%
  select(mean_AUC_SVM,mean_SENS_SVM,mean_SPEC_SVM,
         sd_AUC_SVM,sd_SENS_SVM,sd_SPEC_SVM)

data_long_xgb <- data %>%
  filter(ML == "XGB") %>%
  mutate(Order = case_when(Condition == "Full_data" & Resample == "original" & Thres == TRUE ~ 1,
                           Condition == "Full_data" & Resample == "original" & Thres == FALSE ~ 2,
                           Condition == "Full_data" & Resample == "smote" & Thres == FALSE ~ 3,
                           Condition == "Full_data" & Resample == "up" & Thres == FALSE ~ 4,
                           Condition == "Lifestyle" & Resample == "original" & Thres == TRUE ~ 5,
                           Condition == "Lifestyle" & Resample == "original" & Thres == FALSE ~ 6,
                           Condition == "Lifestyle" & Resample == "smote" & Thres == FALSE ~ 7,
                           Condition == "Lifestyle" & Resample == "up" & Thres == FALSE ~ 8)) %>%
  arrange(Order) %>% distinct(Order, .keep_all = TRUE)

colnames(data_long_xgb) <- paste(colnames(data_long_xgb),"XGB",sep="_")

data_long_xgb <- data_long_xgb %>%
  select(mean_AUC_XGB,mean_SENS_XGB,mean_SPEC_XGB,
         sd_AUC_XGB,sd_SENS_XGB,sd_SPEC_XGB)

data_long_lasso <- data %>%
  filter(ML == "Lasso") %>%
  mutate(Order = case_when(Condition == "Full_data" & Resample == "original" & Thres == TRUE ~ 1,
                           Condition == "Full_data" & Resample == "original" & Thres == FALSE ~ 2,
                           Condition == "Full_data" & Resample == "smote" & Thres == FALSE ~ 3,
                           Condition == "Full_data" & Resample == "up" & Thres == FALSE ~ 4,
                           Condition == "Lifestyle" & Resample == "original" & Thres == TRUE ~ 5,
                           Condition == "Lifestyle" & Resample == "original" & Thres == FALSE ~ 6,
                           Condition == "Lifestyle" & Resample == "smote" & Thres == FALSE ~ 7,
                           Condition == "Lifestyle" & Resample == "up" & Thres == FALSE ~ 8)) %>%
  arrange(Order) %>% distinct(Order, .keep_all = TRUE)
  

colnames(data_long_lasso) <- paste(colnames(data_long_lasso),"Lasso",sep="_")

data_long_lasso <- data_long_lasso %>%
  select(mean_AUC_Lasso,mean_SENS_Lasso,mean_SPEC_Lasso,
         sd_AUC_Lasso,sd_SENS_Lasso,sd_SPEC_Lasso)

all_table <- cbind(data_long_rf,data_long_svm,data_long_xgb,data_long_lasso) # The four MLs are combined and then transposed so I have it exactly in the format needed for my table
all_table <- t(all_table)
```

```{r}
# Crearing Latex code based on x_table package
tbl <- xtable(all_table)
tbl
```

------------------------------------------------------------------------------------------------------------------------

## ROC

# Load the probabilities for each patient in the test data set
```{r}
probabilities_full <- readRDS("Data/Model_results/Trained_models/probs_full_123.RData")
probabilities_full_1 <- readRDS("Data/Model_results/Trained_models/probs_full_41263.RData")
probabilities_full_2 <- readRDS("Data/Model_results/Trained_models/probs_full_2408.RData")
probabilities_life <- readRDS("Data/Model_results/Trained_models/probs_lifestyle_123.RData")
probabilities_life_1 <- readRDS("Data/Model_results/Trained_models/probs_lifestyle_41263.RData")
probabilities_life_2 <- readRDS("Data/Model_results/Trained_models/probs_lifestyle_2408.RData")
```

# Pre-Processing - Making it possible to have distinct MLs, Sampling and Tuning strategies, and data conditions
This step needs to be repeated for each of the three folds. The same code with different data sets is shown here.

## For 1. Fold
For each fold some further pre-processing is needed.
```{r}
probabilities_full$rf$ML <- "RF"
probabilities_full$svm$ML <- "SVM"
probabilities_full$xgb$ML <- "XGB"
probabilities_full$lasso$ML <- "Lasso"

probabilities_life$rf$ML <- "RF"
probabilities_life$svm$ML <- "SVM"
probabilities_life$xgb$ML <- "XGB"
probabilities_life$lasso$ML <- "Lasso"

-------------------------------------
  # Only for Full data condition
probs_full_new <- rbind(probabilities_full$rf,probabilities_full$svm,probabilities_full$xgb,probabilities_full$lasso)

probs_full_new_raw <- probs_full_new %>%
  pivot_longer(cols = c("original","original_cost","smote_def",
                        "up_def","up_own","smote_own","original_own","up_ran","smote_ran","original_ran"),
               names_to = "model", values_to = "Probs")

# Here the ROC curves are caluclated based on yardstick package
probs_full_new <- probs_full_new_raw %>%
group_by(model,ML) %>%
  roc_curve(outcome,Probs, event_level="second") # here the ROC curves are obtained.
probs_full_new$Condition <- "Full_data"

probs_full_new_auc <- probs_full_new_raw %>%
group_by(model,ML) %>%
  roc_auc(outcome,Probs, event_level="second") %>%
  rename("auc" = ".estimate") %>%
  subset( select = -c(.metric,.estimator))

probs_full_new <- left_join(probs_full_new,probs_full_new_auc, by= c("model","ML"))
--------------------------------------
  # THis needs to be repeated for Lifestyle Condition

probs_life_new <- rbind(probabilities_life$rf,probabilities_life$svm,probabilities_life$xgb,probabilities_life$lasso)

probs_life_new_raw <- probs_life_new %>%
  pivot_longer(cols = c("original","original_cost","smote_def",
                        "up_def","up_own","smote_own","original_own","up_ran","smote_ran","original_ran"),
               names_to = "model", values_to = "Probs")

probs_life_new <- probs_life_new_raw %>%
group_by(model,ML) %>%
  roc_curve(outcome,Probs, event_level="second")
probs_life_new$Condition <- "Lifestyle"

probs_life_new_auc <- probs_life_new_raw %>%
group_by(model,ML) %>%
  roc_auc(outcome,Probs, event_level="second") %>%
  rename("auc" = ".estimate") %>%
  subset( select = -c(.metric,.estimator))

probs_life_new <- left_join(probs_life_new,probs_life_new_auc, by= c("model","ML"))

probs_new <- rbind(probs_full_new,probs_life_new) 

probs_new$Fold <- "Fold 1"
```

## For 2. Fold
```{r}
probabilities_full_1$rf$ML <- "RF"
probabilities_full_1$svm$ML <- "SVM"
probabilities_full_1$xgb$ML <- "XGB"
probabilities_full_1$lasso$ML <- "Lasso"

probabilities_life_1$rf$ML <- "RF"
probabilities_life_1$svm$ML <- "SVM"
probabilities_life_1$xgb$ML <- "XGB"
probabilities_life_1$lasso$ML <- "Lasso"


probs_full_new_1 <- rbind(probabilities_full_1$rf,probabilities_full_1$svm,probabilities_full_1$xgb,probabilities_full_1$lasso)

probs_full_new_raw_1 <- probs_full_new_1 %>%
  pivot_longer(cols = c("original","original_cost","smote_def",
                        "up_def","up_own","smote_own","original_own","up_ran","smote_ran","original_ran"),
               names_to = "model", values_to = "Probs")

probs_full_new_1 <- probs_full_new_raw_1 %>%
group_by(model,ML) %>%
  roc_curve(outcome,Probs, event_level="second")
probs_full_new_1$Condition <- "Full_data"

probs_full_new_1_auc <- probs_full_new_raw_1 %>%
group_by(model,ML) %>%
  roc_auc(outcome,Probs, event_level="second") %>%
  rename("auc" = ".estimate") %>%
  subset( select = -c(.metric,.estimator))

probs_full_new_1 <- left_join(probs_full_new_1,probs_full_new_1_auc, by= c("model","ML"))


probs_life_new_1 <- rbind(probabilities_life_1$rf,probabilities_life_1$svm,probabilities_life_1$xgb,probabilities_life_1$lasso)

probs_life_new_raw_1 <- probs_life_new_1 %>%
  pivot_longer(cols = c("original","original_cost","smote_def",
                        "up_def","up_own","smote_own","original_own","up_ran","smote_ran","original_ran"),
               names_to = "model", values_to = "Probs")

probs_life_new_1 <- probs_life_new_raw_1 %>%
group_by(model,ML) %>%
  roc_curve(outcome,Probs, event_level="second")
probs_life_new_1$Condition <- "Lifestyle"

probs_life_new_1_auc <- probs_life_new_raw_1 %>%
group_by(model,ML) %>%
  roc_auc(outcome,Probs, event_level="second") %>%
  rename("auc" = ".estimate") %>%
  subset( select = -c(.metric,.estimator))

probs_life_new_1 <- left_join(probs_life_new_1,probs_life_new_1_auc, by= c("model","ML"))

probs_new_fold_1 <- rbind(probs_full_new_1,probs_life_new_1) 

probs_new_fold_1$Fold <- "Fold 2"
```

## For 3. Fold
```{r}
probabilities_full_2$rf$ML <- "RF"
probabilities_full_2$svm$ML <- "SVM"
probabilities_full_2$xgb$ML <- "XGB"
probabilities_full_2$lasso$ML <- "Lasso"

probabilities_life_2$rf$ML <- "RF"
probabilities_life_2$svm$ML <- "SVM"
probabilities_life_2$xgb$ML <- "XGB"
probabilities_life_2$lasso$ML <- "Lasso"


probs_full_new_2 <- rbind(probabilities_full_2$rf,probabilities_full_2$svm,probabilities_full_2$xgb,probabilities_full_2$lasso)

probs_full_new_raw_2 <- probs_full_new_2 %>%
  pivot_longer(cols = c("original","original_cost","smote_def",
                        "up_def","up_own","smote_own","original_own","up_ran","smote_ran","original_ran"),
               names_to = "model", values_to = "Probs")

probs_full_new_2 <- probs_full_new_raw_2 %>%
group_by(model,ML) %>%
  roc_curve(outcome,Probs, event_level="second")
probs_full_new_2$Condition <- "Full_data"

probs_full_new_2_auc <- probs_full_new_raw_2 %>%
group_by(model,ML) %>%
  roc_auc(outcome,Probs, event_level="second") %>%
  rename("auc" = ".estimate") %>%
  subset( select = -c(.metric,.estimator))

probs_full_new_2 <- left_join(probs_full_new_2,probs_full_new_2_auc, by= c("model","ML"))


probs_life_new_2 <- rbind(probabilities_life_2$rf,probabilities_life_2$svm,probabilities_life_2$xgb,probabilities_life_2$lasso)

probs_life_new_raw_2 <- probs_life_new_2 %>%
  pivot_longer(cols = c("original","original_cost","smote_def",
                        "up_def","up_own","smote_own","original_own","up_ran","smote_ran","original_ran"),
               names_to = "model", values_to = "Probs")

probs_life_new_2 <- probs_life_new_raw_2 %>%
group_by(model,ML) %>%
  roc_curve(outcome,Probs, event_level="second")
probs_life_new_2$Condition <- "Lifestyle"

probs_life_new_2_auc <- probs_life_new_raw_2 %>%
group_by(model,ML) %>%
  roc_auc(outcome,Probs, event_level="second") %>%
  rename("auc" = ".estimate") %>%
  subset( select = -c(.metric,.estimator))

probs_life_new_2 <- left_join(probs_life_new_2,probs_life_new_2_auc, by= c("model","ML"))

probs_new_fold_2 <- rbind(probs_full_new_2,probs_life_new_2) 

probs_new_fold_2$Fold <- "Fold 3"
```

## Combining all three folds
```{r}
probs_final <- rbind(probs_new,probs_new_fold_1,probs_new_fold_2)
```


## Last Pre-processing 
Here the means are calculated to have the best performing model based on all model building choices, corresponding to the best model selected for the tables.
```{r}
full$Fold <- "Fold 1"
full_1$Fold <- "Fold 2"
full_2$Fold <- "Fold 3"
life$Fold <- "Fold 1"
life_1$Fold <- "Fold 2"
life_2$Fold <- "Fold 3"
for_roc <- rbind(full,full_1,full_2,life,life_1,life_2)
for_roc <- for_roc %>%
  group_by(model,Condition,ML) %>%
  mutate(mean_AUC = round(mean(AUC),3),
         mean_SENS = round(mean(Sensitivity),3),
         mean_SPEC = round(mean(Specificity),3)) %>%
  ungroup()
```

## Final data set needed to visualize ROC curves
Again only the best performing Tuning and Sampling strategy is chosen to be depicted. However, this is depicted for each of the data folds to highlight the data variability in this data set. 
```{r}
probs_new_final <- left_join(probs_final,for_roc, by= c("model","ML","Condition","Fold")) # combine the roc curves data with the tables data

probs_new_final <- probs_new_final %>%
  mutate(Condition = recode(Condition, "Full_data" = "Full data", "Lifestyle" = "Lifestyle data")) %>% 
  group_by(ML,Condition,Fold) %>%
  mutate(Best = ifelse(mean_AUC == max(mean_AUC),TRUE,FALSE)) %>%  # first filter based on best AUC, same as Tables
  filter(Best == TRUE) 

probs_new_final <- probs_new_final %>%
  group_by(ML,Condition,Fold) %>%
  mutate(Best_Sp = ifelse(mean_SENS == max(mean_SENS),TRUE,FALSE)) %>%  # next filter based on best S
  filter(Best_Sp == TRUE)

probs_new_final <- probs_new_final %>%
  group_by(ML,Condition,Fold) %>%
  mutate(Best_Sens = ifelse(mean_SPEC == max(mean_SPEC),TRUE,FALSE)) %>%
  filter(Best_Sens == TRUE)
```

## Seperate data sets for Mean depiction
These extra dfs are containing information about the mean values which will be included in the plot.
```{r}
auc_values_full_mean <- probs_new_final %>%
  group_by(ML, Condition, Fold) %>%
  summarise(AUC = max(mean_AUC)) %>%
  filter(Condition == "Full data") %>% distinct(AUC, .keep_all = TRUE) 
  

auc_values_life_mean <- probs_new_final %>%
  group_by(ML, Condition, Fold) %>%
  summarise(AUC = max(mean_AUC)) %>%
  filter(Condition == "Lifestyle data") %>% distinct(AUC, .keep_all = TRUE)
```
## ROC plot across all folds
The code which produces exactly the code needed for the figure in the report.
```{r}
ROC_compare_fold <- probs_new_final%>%
  ggplot(aes(1 - specificity, sensitivity, fill = Fold, color=Condition)) +
  geom_abline(lty = 2, color = "gray", size = 1,alpha = 0.8) +
  geom_path(alpha = 0.6, size = 1.2) +
  coord_equal() +
  labs(x = "1 - Specificity", y = "Sensitivity") +
  facet_wrap(~ ML) +
    geom_text(data = auc_values_full_mean, aes(label = paste0("Mean AUC = ", AUC)), 
            x = 0.7, y = 0.15, show.legend = FALSE) +
  geom_text(data = auc_values_life_mean, aes(label = paste0("Mean AUC = ", AUC)), 
            x = 0.7, y = 0.05, show.legend = FALSE) +
  theme_bw(base_size = 12) +
  theme(legend.position = "top",
        panel.border = element_blank(),  # remove panel borders
        panel.grid.major = element_blank(),  # remove major grid lines
        panel.grid.minor = element_blank(),  # remove minor grid lines
        axis.line = element_line(),  # set axis lines to bold
        axis.text = element_text(),  # set axis text to bold
        axis.title = element_text(size = 14, face = "bold"),  # set axis title to bold
        plot.background = element_blank(),  # remove plot background
        panel.background = element_blank(),  # remove panel background
        legend.text = element_text(size = 12, face = "bold"),  # set legend text to bold
        legend.title = element_blank()  # remove legend title
  ) +
  scale_color_brewer(palette = "Dark2")
print(ROC_compare_fold)
```

------------------------------------------------------------------------------------------------------------------------
## Descirptives Table 
Estimates are obtained for all included patients on baseline stats.
```{r}
full_data <- read_csv("Data/Full_data/full_data.csv") # raw data set is loaded

# Preparation of dataset needed for descriptive stats
names <- c("patient","Age","Height","Weight","BMI","HbA1c","T2D_Dur")
descriptives <- full_data %>%
  select(patient,Age,Height,Weight,BMI,HbA1c,T2D_Dur) 
names(descriptives) <- c(names)

DT <- data.table(descriptives)
DT[, sapply(.SD, function(x) list(mean=round(mean(x), 2))), by=patient]
names(DT) <- c(names)
DT <- as.data.frame(DT)
```

# Proportions and counts for factor variables
For factors a different approach is used and values need to be included manually.
```{r}
table(full_data$Night_class_hypo_out)
round(table(full_data$Night_class_hypo_out)[1]/(table(full_data$Night_class_hypo_out)[1]+table(full_data$Night_class_hypo_out)[2]),3)
round(table(full_data$Night_class_hypo_out)[2]/(table(full_data$Night_class_hypo_out)[1]+table(full_data$Night_class_hypo_out)[2]),3)
table(full_data$Gender)
round(table(full_data$Gender)[1]/(table(full_data$Gender)[1]+table(full_data$Gender)[2]),3)
round(table(full_data$Gender)[2]/(table(full_data$Gender)[1]+table(full_data$Gender)[2]),3)
```
# Latex code for descriptives
```{r}
stargazer(DT, 
          type = 'latex', min.max=FALSE, mean.sd = TRUE, 
          nobs = FALSE, median = FALSE, iqr = FALSE,
          digits=1, align=T,
          title = "Summary Statistics")
```

------------------------------------------------------------------------------------------------------------------------

## Calibration plots - OPTIONAL
```{r}
calibration_plots(probabilities_full$rf)
calibration_plots(probabilities_full$svm)
calibration_plots(probabilities_full$xgb)
calibration_plots(probabilities_full$lasso)

calibration_plots(probabilities_life$rf)
calibration_plots(probabilities_life$svm)
calibration_plots(probabilities_life$xgb)
calibration_plots(probabilities_life$lasso)
```

## Outcome frequency and Distribution of days - OPTIONAL INFORMATION
```{r}
descrip <- full_data
number_of_days_pp <- descrip %>%
  group_by(patient) %>%
  summarise(n= n())
sort(number_of_days_pp$n) # distributions of days per patient
nrow(number_of_days_pp) # number of patients
nrow(full_data) # number of individual observations
```

```{r}
# Visualisation for distribution of outcome variable
ggplot(full_data %>%
      count(Night_class_hypo_out) %>% #Groups by team and role
       mutate(pct=n/sum(n)),       #Calculates % for each role
        aes(Night_class_hypo_out, n, fill=Night_class_hypo_out)) +
        geom_col(stat="identity", position="stack") +
  geom_text(aes(label=paste0(sprintf("%1.1f", pct*100),"%")),
            position=position_stack(vjust=0.5))
```


### CGM visualisation
Exemplary continous profiles of patients. Nocturnal Hypo-, and Hyperglyceamia are highlighted. On top it gets clear, where periods of glucose values are missing in the intended 14 day period
```{r}
all_patients_cgm <- read_csv("~/GitHub/Sweet_Dreams_Ahead_Machine_Learning_Models_for_Nocturnal_Hypoglycemia_Prediction_in_Type_2_Diabetes/Processing_and_Extraction/Data_processed/all_patients_cgm.csv")

all_patients_cgm %>%
  filter(patient == 761) %>%
  ggplot(aes(x=full_date, y=Historie_glucose, colour=Noc_variability)) +
  geom_line(aes(group =3)) +
  theme_minimal() +
  labs(title = "Glucose level of one patient over 14 days",
       x = "Time",
       y = "Glucose level in mmol/l",
       colour = "Nocturnal Hyperglycaemia")

all_patients_cgm %>%
  filter(patient == 601) %>%
  ggplot(aes(x=full_date, y=Historie_glucose, colour=Noc_variability)) +
  geom_line(aes(group =3)) +
  theme_minimal() +
  labs(title = "Glucose level of one patient over 14 days",
       x = "Time",
       y = "Glucose level in mmol/l",
       colour = "Nocturnal Hyperglycaemia")
```

## SESSION INFO
As this is the last code needed to perform the analysis here a session info command is run.
```{r}
sessionInfo()
```

