---
title: "Model_building_Lifestyle_condition"
author: "Christoph Völtzke"
date: "2023"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Packages
```{r}
# Processing
library(readr) # read data
library(tidyverse) # data manipulation

# Methods
library(ranger) # RF with more hypers to tune
library(glmnet) # Lasso
library(xgboost) # Boosting
library(e1071) # SVM, most likely not used
library(kernlab) #SVM with more hypers and more sophisticated algorithms

# Class Imbalance and Evaluation metrics
library(caret) # Hyper training
library(pROC) # AUC and ROC
library(ggforce) #needed for XGB 
library(DMwR) # SMOTE in caret embedded
```

# Information
- In this document all models for the Lifestyle condition are trained.
- First data is split with a SPECIFIC seed. NOTE: This document is run 3x times with different seed values.
- Then data is split to only perform any analyses on the training data, but not on the test data.
- 4 ML models are tested:
  - Random Forest
  - Support Vector Machines
  - eXtreme Gradient Boosting
  - Lasso Logistic Regression
  - For only this data  condition resulting in 40 different models.
- All estimates and probabilities are saved in dfs and just in later analyses

## Load Helper functions needed for analysis
```{r}
source("Functions/data_split.R")
source("Functions/confusion_matrix_function.R")
source("Functions/rf_pred_helper.R")
```

## Data set preparation
```{r}
# Load the data set with the feature set selected by the feature selection process
full_data_life_plus <- read_csv("Data/Full_data/full_data_life_plus_sel.csv")
full_data_life_plus <- full_data_life_plus %>% 
  mutate(Night_class_hypo_out = as.factor(Night_class_hypo_out))
```

## Data split train/test

**NOTE**

This is very important to consider. This script is run 3 separate times with different seeds for the training and test data.
If you want to reproduce the exact same results you need to run the script 3 TIMES with the following seeds:

1. Fold: Seed = 123
2. Fold: Seed = 41263
3. Fold: Seed = 2408

```{r}
# THIS IS THE EXAMPLARY SCRIPT WITH THE 1. FOLD
full_data_life_plus_split <- data_split(full_data_life_plus,train_size= 0.75, seed = 123) 
# with this code the results of the first fold will be reproduced.
full_data_life_plus_train <- full_data_life_plus_split[[1]]
full_data_life_plus_test <- full_data_life_plus_split[[2]]

levels(full_data_life_plus_train$Night_class_hypo_out) <- c("No_Hypo", "Hypo")
levels(full_data_life_plus_test$Night_class_hypo_out) <- c("No_Hypo", "Hypo")
```

# Model tuning

## Control settings - For ALL ML algorithms

*NOTE* 

All control settings have a seed integrated ensuring that the results are the same if you want to reproduce them with the exact same settings. 

ALSO: These control settings are used for each ML algorithm and are not newly defined.

```{r}
# control settings are displayed for each model to ensure that each model building step is represented in a right way.
# Here it is controlled the search strategy (grid, random) and sampling methods (smote, up)


# THE CODE IS ANNOTATED ONLY ONCE 
ctrl_out <- trainControl(method = "cv", # Cross-validation is performed
                         number = 10, # number of iterations in CV
                         classProbs = TRUE, # this allows to get probabilities for each person in training and later test set
                         summaryFunction = twoClassSummary, # this allows for the wanted evaluation metrics
                         search = "grid", # the grid strategy is specified. Here, it is grid search. Can be customized in train command
                         allowParallel = TRUE) # Allows to be run parallel - makes computation faster

ctrl_ins_smote <- trainControl(method = "cv", 
                               number = 10,
                               summaryFunction = twoClassSummary,
                               search = "grid",
                               classProbs = TRUE,
                               sampling = "smote", # smote included
                               allowParallel = TRUE)

ctrl_ins_up <- trainControl(method = "cv", 
                            number = 10,
                            classProbs = TRUE,
                            summaryFunction = twoClassSummary,
                            search = "grid",
                            sampling = "up", # up sampling included
                            allowParallel = TRUE)

ctrl_random <- trainControl(method = "cv",
                            number = 10,
                            classProbs = TRUE,
                            summaryFunction = twoClassSummary,
                            search = "random", # random tuning instead of default grid
                            allowParallel = TRUE)

ctrl_random_ins_up <- trainControl(method = "cv", 
                                   number = 10,
                                   classProbs = TRUE,
                                   summaryFunction = twoClassSummary,
                                   search = "random", # random tuning instead of default grid
                                   sampling = "up", # up sampling included
                                   allowParallel = TRUE)

ctrl_random_ins_smote <- trainControl(method = "cv", 
                                      number = 10,
                                      classProbs = TRUE,
                                      summaryFunction = twoClassSummary,
                                      search = "random", # random tuning instead of default grid
                                      sampling = "smote", # smote included
                                      allowParallel = TRUE)
```

################################################################################
# RANDOM FOREST
################################################################################

## DEFAULT

The code is annotated once here as it is repeated for each combination of Tuning strategy and Sampling procedure. Only the parameters tuneLength and trControl vary across the models.

```{r}
# Default tuning length of 10 is selected, data is scaled and centered


up_inside_t10 <- caret::train(Night_class_hypo_out ~ ., data = full_data_life_plus_train, # Outcome variable is predicted based on all features (.) in df, with a specific training data set
                   method = "ranger", # this is the package used for the calculation, Ranger has a commonly used RF approach with multiple hyperparameters to tune
                   metric = "ROC", # which metric is used
                   trControl = ctrl_ins_up, # specified above
                   verbose = FALSE, # indication about what to output
                   preProc = c("center", "scale"), # data is centered and scaled
                   tuneLength=10) # indicating the tuning strategy, Here the number of different tuning strategies is set to 10. Default is 3. Can also be customized, see below.

smote_inside_t10 <- caret::train(Night_class_hypo_out ~ ., data = full_data_life_plus_train,
                   method = "ranger",
                   metric = "ROC",
                   trControl = ctrl_ins_smote, # specified above
                   verbose = FALSE,
                   preProc = c("center", "scale"),
                   tuneLength=10)

original_t10 <- caret::train(Night_class_hypo_out ~ ., data = full_data_life_plus_train, 
                  method = "ranger",
                  metric = "ROC",
                  trControl = ctrl_out, # specified above
                  verbose = FALSE,
                  reProc = c("center", "scale"),
                  tuneLength=10)
```

## RANDOM
```{r}
# 20 random grids are selected
up_inside_ran <- caret::train(Night_class_hypo_out ~ ., data = full_data_life_plus_train,
                   method = "ranger",
                   metric = "ROC",
                   trControl = ctrl_random_ins_up,
                   verbose = FALSE,
                   preProc = c("center", "scale"),
                  tuneLength=20) # NEW TUNING LENGTH

smote_inside_ran <- caret::train(Night_class_hypo_out ~ ., data = full_data_life_plus_train,
                   method = "ranger",
                   metric = "ROC",
                   trControl = ctrl_random_ins_smote,
                   verbose = FALSE,
                   preProc = c("center", "scale"),
                   tuneLength=20)

original_ran <- caret::train(Night_class_hypo_out ~ ., data = full_data_life_plus_train, 
                  method = "ranger",
                  metric = "ROC",
                  trControl = ctrl_random,
                  verbose = FALSE,
                  reProc = c("center", "scale"),
                  tuneLength=20)
```

## Other Own Grid
```{r}
# A customized grid is used for all of the options based on the results of the two previous approaches and based on the literature

rangerGrid <-  expand.grid(mtry = c(2:19),
                           splitrule = c("extratrees","gini"),
                           min.node.size = seq(from = 1, to = 16, length.out = 7))

up_inside_own <- caret::train(Night_class_hypo_out ~ ., data = full_data_life_plus_train,
                   method = "ranger",
                   metric = "ROC",
                   trControl = ctrl_ins_up,
                   verbose = FALSE,
                   preProc = c("center", "scale"),
                   tuneGrid= rangerGrid) # CUSTOMIZED GRID IS USED

smote_inside_own <- caret::train(Night_class_hypo_out ~ ., data = full_data_life_plus_train,
                   method = "ranger",
                   metric = "ROC",
                   trControl = ctrl_ins_smote,
                   verbose = FALSE,
                   preProc = c("center", "scale"),
                   tuneGrid= rangerGrid) # CUSTOMIZED GRID IS USED

original_own <- caret::train(Night_class_hypo_out ~ ., data = full_data_life_plus_train, 
                  method = "ranger",
                  metric = "ROC",
                  trControl = ctrl_out,
                  verbose = FALSE,
                  reProc = c("center", "scale"),
                  tuneGrid= rangerGrid) # CUSTOMIZED GRID IS USED

```


## Predictions for Test set
```{r}
# a customized function is used which calculates all of the evaluation metrics needed and also gives the probabilities in a single object

# SEE source code of helper function for more information

# OVERALL 10 models are tested!
pred_original <- rf_pred(original_t10,threshold = TRUE, test = full_data_life_plus_test)
pred_original_thres <- rf_pred(original_t10, test = full_data_life_plus_test)

pred_smote_inside_t10 <- rf_pred(smote_inside_t10, test = full_data_life_plus_test)
pred_up_inside_t10 <- rf_pred(up_inside_t10, test = full_data_life_plus_test)
# Tune own
pred_up_inside_own <- rf_pred(up_inside_own, test = full_data_life_plus_test)
pred_smote_inside_own <- rf_pred(smote_inside_own, test = full_data_life_plus_test)
pred_original_own <- rf_pred(original_own, test = full_data_life_plus_test)
# Tune random
pred_up_inside_ran <- rf_pred(up_inside_ran, test = full_data_life_plus_test)
pred_smote_inside_ran <- rf_pred(smote_inside_ran, test = full_data_life_plus_test)
pred_original_ran <- rf_pred(original_ran, test = full_data_life_plus_test)
```

## probabilities results
Probabilities are saved to check for probabilities and also are used for later comparisons between models.

```{r}
probs <- cbind(pred_original$class_probs,pred_original_thres$class_probs,pred_smote_inside_t10$class_probs,pred_up_inside_t10$class_probs,pred_up_inside_own$class_probs,pred_smote_inside_own$class_probs,pred_original_own$class_probs,pred_up_inside_ran$class_probs,pred_smote_inside_ran$class_probs,pred_original_ran$class_probs) # Probabilities for each model, All bind by column for each patient in the test set

probabilities_data <- cbind(full_data_life_plus_test$Night_class_hypo_out,probs)
colnames(probabilities_data) <-  c("outcome","original","original_cost","smote_def","up_def",
           "up_own","smote_own","original_own","up_ran","smote_ran","original_ran") # naming the columns to have them in line for each ML and also to distinguish models

probabilities_data <- as.data.frame(probabilities_data)
probabilities_data$outcome <- factor(probabilities_data$outcome) # process outcome variable
levels(probabilities_data$outcome) <- c("No_Hypo", "Hypo")
probabilities_data_rf <- probabilities_data # save object for RF
```

## Saving the results 
The estimates are saved in a way that it is possible to differentiate between different model building decisions. 

```{r}
auc <- rbind(pred_original$auc,pred_original_thres$auc,pred_smote_inside_t10$auc,pred_up_inside_t10$auc,pred_up_inside_own$auc,pred_smote_inside_own$auc,pred_original_own$auc,pred_up_inside_ran$auc,pred_smote_inside_ran$auc,pred_original_ran$auc)
# ALL AUC VALUES ARE SAVED HERE IN ONE COLUMN 

sens <- rbind(pred_original$metrics[[1]],pred_original_thres$metrics[[1]],pred_smote_inside_t10$metrics[[1]],pred_up_inside_t10$metrics[[1]],pred_up_inside_own$metrics[[1]],pred_smote_inside_own$metrics[[1]],pred_original_own$metrics[[1]],pred_up_inside_ran$metrics[[1]],pred_smote_inside_ran$metrics[[1]],pred_original_ran$metrics[[1]])
# ALL SENSITIVITY VALUES ARE SAVED HERE IN ONE COLUMN 

spec <- rbind(pred_original$metrics[[2]],pred_original_thres$metrics[[2]],pred_smote_inside_t10$metrics[[2]],pred_up_inside_t10$metrics[[2]],pred_up_inside_own$metrics[[2]],pred_smote_inside_own$metrics[[2]],pred_original_own$metrics[[2]],pred_up_inside_ran$metrics[[2]],pred_smote_inside_ran$metrics[[2]],pred_original_ran$metrics[[2]])
# ALL SPECIFICITY VALUES ARE SAVED HERE IN ONE COLUMN 

accuracy <- rbind(pred_original$metrics[[4]],pred_original_thres$metrics[[4]],pred_smote_inside_t10$metrics[[4]],pred_up_inside_t10$metrics[[4]],pred_up_inside_own$metrics[[4]],pred_smote_inside_own$metrics[[4]],pred_original_own$metrics[[4]],pred_up_inside_ran$metrics[[4]],pred_smote_inside_ran$metrics[[4]],pred_original_ran$metrics[[4]])
# ALL ACCURACY VALUES ARE SAVED HERE IN ONE COLUMN - OPTIONAL OUTCOME VARIABLE

model <-  c("original","original_cost","smote_def","up_def",
           "up_own","smote_own","original_own","up_ran","smote_ran","original_ran") # Specifying each model building decision (tuning/sampling combination)
metrics_rf_life_plus <- cbind(model,auc,sens,spec,accuracy) # binding all metrics in one df

metrics_rf_life_plus <- as.data.frame(metrics_rf_life_plus)
colnames(metrics_rf_life_plus) <- c("model","AUC","Sensitivity","Specificity","Accuracy") # renaming columns to have it in line for each ML
metrics_rf_life_plus <- metrics_rf_life_plus %>% # last processing of evaluation metrics
  mutate(model = factor(model),
         AUC = as.numeric(AUC),
         Sensitivity = as.numeric(Sensitivity),
         Specificity = as.numeric(Specificity),
         Accuracy = as.numeric(Accuracy),
         ML = "RF", # Specifying the ML used
         Condition = "Lifestyle") %>% # Specifying the condition
  mutate_if(is.numeric,round,digits=3)

# OVERALL, for each ML it results in 10 independent models
```

*NOTE*

This procedure is repeated for each of the four ML algorithms:
1. Random Forest (as documented above)
2. Support Vector Machine # method = "svmRadial"
3. eXtreme Gradient Boosting # method = "xgbTree"
4. Lasso Logistic regression # method = "glmnet"

ONLY THE TUNING LENGTH AND THE CUSTOMIZED GRID IS CHANGED ACROSS THE MODELS. THEREFORE, NO ANNOTATION IS DONE FOR THESE MODELS. SEE ABOVE IF CODE IS UNCLEAR.


################################################################################
# SVM
################################################################################

## DEFAULT

```{r}
svm_up_inside_t10 <- caret::train(Night_class_hypo_out ~ ., data = full_data_life_plus_train,
                   method = "svmRadial", # NEW METHOD
                   metric = "ROC",
                   trControl = ctrl_ins_up,
                   verbose = FALSE,
                   preProc = c("center", "scale"),
                   tuneLength=10)

svm_smote_inside_t10 <- caret::train(Night_class_hypo_out ~ ., data = full_data_life_plus_train,
                   method = "svmRadial",
                   metric = "ROC",
                   trControl = ctrl_ins_smote,
                   verbose = FALSE,
                   preProc = c("center", "scale"),
                   tuneLength=10)

svm_original_t10 <- caret::train(Night_class_hypo_out ~ ., data = full_data_life_plus_train, 
                  method = "svmRadial",
                  metric = "ROC",
                  trControl = ctrl_out,
                  verbose = FALSE,
                  reProc = c("center", "scale"),
                  tuneLength=10)
```

## RANDOM
```{r}
svm_up_inside_ran <- caret::train(Night_class_hypo_out ~ ., data = full_data_life_plus_train,
                   method = "svmRadial",
                   metric = "ROC",
                   trControl = ctrl_random_ins_up,
                   verbose = FALSE,
                   preProc = c("center", "scale"),
                  tuneLength=20)

svm_smote_inside_ran <- caret::train(Night_class_hypo_out ~ ., data = full_data_life_plus_train,
                   method = "svmRadial",
                   metric = "ROC",
                   trControl = ctrl_random_ins_smote,
                   verbose = FALSE,
                   preProc = c("center", "scale"),
                   tuneLength=20)

svm_original_ran <- caret::train(Night_class_hypo_out ~ ., data = full_data_life_plus_train, 
                  method = "svmRadial",
                  metric = "ROC",
                  trControl = ctrl_random,
                  verbose = FALSE,
                  reProc = c("center", "scale"),
                  tuneLength=20)
```

## Other Own Grid
```{r}
svm_Grid <-  expand.grid(sigma = c(seq(from = 0.001, to = 0.01, length.out = 8),seq(from = 0.011, to = 0.25, length.out = 6)),
                        C = c(seq(from = 0.1, to = 2, length.out = 12),seq(from = 3, to = 100, length.out = 12)))

svm_up_inside_own <- caret::train(Night_class_hypo_out ~ ., data = full_data_life_plus_train,
                   method = "svmRadial",
                   metric = "ROC",
                   trControl = ctrl_ins_up,
                   verbose = FALSE,
                   preProc = c("center", "scale"),
                   tuneGrid= svm_Grid)

svm_smote_inside_own <- caret::train(Night_class_hypo_out ~ ., data = full_data_life_plus_train,
                   method = "svmRadial",
                   metric = "ROC",
                   trControl = ctrl_ins_smote,
                   verbose = FALSE,
                   preProc = c("center", "scale"),
                   tuneGrid= svm_Grid)

svm_original_own <- caret::train(Night_class_hypo_out ~ ., data = full_data_life_plus_train, 
                  method = "svmRadial",
                  metric = "ROC",
                  trControl = ctrl_out,
                  verbose = FALSE,
                  reProc = c("center", "scale"),
                  tuneGrid= svm_Grid)
```

## Predictions for Test set
```{r}
pred_svm_original <- rf_pred(svm_original_t10,threshold = TRUE, test = full_data_life_plus_test)
pred_svm_original_thres <- rf_pred(svm_original_t10, test = full_data_life_plus_test)

pred_svm_smote_inside_t10 <- rf_pred(svm_smote_inside_t10, test = full_data_life_plus_test)
pred_svm_up_inside_t10 <- rf_pred(svm_up_inside_t10, test = full_data_life_plus_test)
# Tune own
pred_svm_up_inside_own <- rf_pred(svm_up_inside_own, test = full_data_life_plus_test)
pred_svm_smote_inside_own <- rf_pred(svm_smote_inside_own, test = full_data_life_plus_test)
pred_svm_original_own <- rf_pred(svm_original_own, test = full_data_life_plus_test)
# Tune random
pred_svm_up_inside_ran <- rf_pred(svm_up_inside_ran, test = full_data_life_plus_test)
pred_svm_smote_inside_ran <- rf_pred(svm_smote_inside_ran, test = full_data_life_plus_test)
pred_svm_original_ran <- rf_pred(svm_original_ran, test = full_data_life_plus_test)
```

## probabilities
```{r}
probs <- cbind(pred_svm_original$class_probs,pred_svm_original_thres$class_probs,pred_svm_smote_inside_t10$class_probs,pred_svm_up_inside_t10$class_probs,pred_svm_up_inside_own$class_probs,pred_svm_smote_inside_own$class_probs,pred_svm_original_own$class_probs,pred_svm_up_inside_ran$class_probs,pred_svm_smote_inside_ran$class_probs,pred_svm_original_ran$class_probs)

probabilities_data <- cbind(full_data_life_plus_test$Night_class_hypo_out,probs)
colnames(probabilities_data) <-  c("outcome","original","original_cost","smote_def","up_def",
           "up_own","smote_own","original_own","up_ran","smote_ran","original_ran")
probabilities_data <- as.data.frame(probabilities_data)
probabilities_data$outcome <- factor(probabilities_data$outcome)
levels(probabilities_data$outcome) <- c("No_Hypo", "Hypo")
probabilities_data_svm <- probabilities_data
```

## Saving the results
```{r}
auc <- rbind(pred_svm_original$auc,pred_svm_original_thres$auc,pred_svm_smote_inside_t10$auc,pred_svm_up_inside_t10$auc,pred_svm_up_inside_own$auc,pred_svm_smote_inside_own$auc,pred_svm_original_own$auc,pred_svm_up_inside_ran$auc,pred_svm_smote_inside_ran$auc,pred_svm_original_ran$auc)

sens <- rbind(pred_svm_original$metrics[[1]],pred_svm_original_thres$metrics[[1]],pred_svm_smote_inside_t10$metrics[[1]],pred_svm_up_inside_t10$metrics[[1]],pred_svm_up_inside_own$metrics[[1]],pred_svm_smote_inside_own$metrics[[1]],pred_svm_original_own$metrics[[1]],pred_svm_up_inside_ran$metrics[[1]],pred_svm_smote_inside_ran$metrics[[1]],pred_svm_original_ran$metrics[[1]])

spec <- rbind(pred_svm_original$metrics[[2]],pred_svm_original_thres$metrics[[2]],pred_svm_smote_inside_t10$metrics[[2]],pred_svm_up_inside_t10$metrics[[2]],pred_svm_up_inside_own$metrics[[2]],pred_svm_smote_inside_own$metrics[[2]],pred_svm_original_own$metrics[[2]],pred_svm_up_inside_ran$metrics[[2]],pred_svm_smote_inside_ran$metrics[[2]],pred_svm_original_ran$metrics[[2]])

accuracy <- rbind(pred_svm_original$metrics[[4]],pred_svm_original_thres$metrics[[4]],pred_svm_smote_inside_t10$metrics[[4]],pred_svm_up_inside_t10$metrics[[4]],pred_svm_up_inside_own$metrics[[4]],pred_svm_smote_inside_own$metrics[[4]],pred_svm_original_own$metrics[[4]],pred_svm_up_inside_ran$metrics[[4]],pred_svm_smote_inside_ran$metrics[[4]],pred_svm_original_ran$metrics[[4]])

model <-  c("original","original_cost","smote_def","up_def",
           "up_own","smote_own","original_own","up_ran","smote_ran","original_ran")
metrics_svm_life_plus <- cbind(model,auc,sens,spec,accuracy)
metrics_svm_life_plus <- as.data.frame(metrics_svm_life_plus)
colnames(metrics_svm_life_plus) <- c("model","AUC","Sensitivity","Specificity","Accuracy")
metrics_svm_life_plus <- metrics_svm_life_plus %>%
  mutate(model = factor(model),
         AUC = as.numeric(AUC),
         Sensitivity = as.numeric(Sensitivity),
         Specificity = as.numeric(Specificity),
         Accuracy = as.numeric(Accuracy),
         ML = "SVM",
         Condition = "Lifestyle") %>%
  mutate_if(is.numeric,round,digits=3)
```

################################################################################
# XGB
################################################################################

## DEFAULT

```{r}
# Due to high computational time the default length is reduced to 5 compared to the other MLs
xgb_up_inside_t10 <- caret::train(Night_class_hypo_out ~ ., data = full_data_life_plus_train,
                   method = "xgbTree",
                   metric = "ROC",
                   trControl = ctrl_ins_up,
                   verbose = FALSE,
                   preProc = c("center", "scale"),
                   tuneLength=5)

xgb_smote_inside_t10 <- caret::train(Night_class_hypo_out ~ ., data = full_data_life_plus_train,
                   method = "xgbTree",
                   metric = "ROC",
                   trControl = ctrl_ins_smote,
                   verbose = FALSE,
                   preProc = c("center", "scale"),
                   tuneLength=5)

xgb_original_t10 <- caret::train(Night_class_hypo_out ~ ., data = full_data_life_plus_train, 
                  method = "xgbTree",
                  metric = "ROC",
                  trControl = ctrl_out,
                  verbose = FALSE,
                  reProc = c("center", "scale"),
                  tuneLength=5)
```

## RANDOM
```{r}
# Due to high computational time the default length is reduced to 12 compared to the other MLs
xgb_up_inside_ran <- caret::train(Night_class_hypo_out ~ ., data = full_data_life_plus_train,
                   method = "xgbTree",
                   metric = "ROC",
                   trControl = ctrl_random_ins_up,
                   verbose = FALSE,
                   preProc = c("center", "scale"),
                  tuneLength=12)

xgb_smote_inside_ran <- caret::train(Night_class_hypo_out ~ ., data = full_data_life_plus_train,
                   method = "xgbTree",
                   metric = "ROC",
                   trControl = ctrl_random_ins_smote,
                   verbose = FALSE,
                   preProc = c("center", "scale"),
                   tuneLength=12)

xgb_original_ran <- caret::train(Night_class_hypo_out ~ ., data = full_data_life_plus_train, 
                  method = "xgbTree",
                  metric = "ROC",
                  trControl = ctrl_random,
                  verbose = FALSE,
                  reProc = c("center", "scale"),
                  tuneLength=12)
```

## Other Own Grid
```{r}
xgb_Grid <-  expand.grid(eta = seq(from = 0.3, to = 0.8, length.out = 3),
                         max_depth = c(2,3,5),
                         min_child_weight = c(1,2),
                         subsample = seq(from = 0.4, to = 1, length.out = 3),
                         colsample_bytree = seq(from = 0.3, to = 0.8, length.out = 3),
                         nrounds = seq(from = 50, to = 500, length.out = 3),
                         gamma = seq(from = 0, to = 1.5, length.out = 2))

xgb_up_inside_own <- caret::train(Night_class_hypo_out ~ ., data = full_data_life_plus_train,
                   method = "xgbTree",
                   metric = "ROC",
                   trControl = ctrl_ins_up,
                   verbose = FALSE,
                   preProc = c("center", "scale"),
                   tuneGrid= xgb_Grid)

xgb_smote_inside_own <- caret::train(Night_class_hypo_out ~ ., data = full_data_life_plus_train,
                   method = "xgbTree",
                   metric = "ROC",
                   trControl = ctrl_ins_smote,
                   verbose = FALSE,
                   preProc = c("center", "scale"),
                   tuneGrid= xgb_Grid)

xgb_original_own <- caret::train(Night_class_hypo_out ~ ., data = full_data_life_plus_train, 
                  method = "xgbTree",
                  metric = "ROC",
                  trControl = ctrl_out,
                  verbose = FALSE,
                  reProc = c("center", "scale"),
                  tuneGrid= xgb_Grid)
```

## Predictions for Test set
```{r}
pred_xgb_original <- rf_pred(xgb_original_t10,threshold = TRUE, test = full_data_life_plus_test)
pred_xgb_original_thres <- rf_pred(xgb_original_t10, test = full_data_life_plus_test)

pred_xgb_smote_inside_t10 <- rf_pred(xgb_smote_inside_t10, test = full_data_life_plus_test)
pred_xgb_up_inside_t10 <- rf_pred(xgb_up_inside_t10, test = full_data_life_plus_test)
# Tune own
pred_xgb_up_inside_own <- rf_pred(xgb_up_inside_own, test = full_data_life_plus_test)
pred_xgb_smote_inside_own <- rf_pred(xgb_smote_inside_own, test = full_data_life_plus_test)
pred_xgb_original_own <- rf_pred(xgb_original_own, test = full_data_life_plus_test)
# Tune random
pred_xgb_up_inside_ran <- rf_pred(xgb_up_inside_ran, test = full_data_life_plus_test)
pred_xgb_smote_inside_ran <- rf_pred(xgb_smote_inside_ran, test = full_data_life_plus_test)
pred_xgb_original_ran <- rf_pred(xgb_original_ran, test = full_data_life_plus_test)
```

## probabilities
```{r}
probs <- cbind(pred_xgb_original$class_probs,pred_xgb_original_thres$class_probs,pred_xgb_smote_inside_t10$class_probs,pred_xgb_up_inside_t10$class_probs,pred_xgb_up_inside_own$class_probs,pred_xgb_smote_inside_own$class_probs,pred_xgb_original_own$class_probs,pred_xgb_up_inside_ran$class_probs,pred_xgb_smote_inside_ran$class_probs,pred_xgb_original_ran$class_probs)

probabilities_data <- cbind(full_data_life_plus_test$Night_class_hypo_out,probs)
colnames(probabilities_data) <-  c("outcome","original","original_cost","smote_def","up_def",
           "up_own","smote_own","original_own","up_ran","smote_ran","original_ran")
probabilities_data <- as.data.frame(probabilities_data)
probabilities_data$outcome <- factor(probabilities_data$outcome)
levels(probabilities_data$outcome) <- c("No_Hypo", "Hypo")
probabilities_data_xgb <- probabilities_data
```

## Saving the results
```{r}
auc <- rbind(pred_xgb_original$auc,pred_xgb_original_thres$auc,pred_xgb_smote_inside_t10$auc,pred_xgb_up_inside_t10$auc,pred_xgb_up_inside_own$auc,pred_xgb_smote_inside_own$auc,pred_xgb_original_own$auc,pred_xgb_up_inside_ran$auc,pred_xgb_smote_inside_ran$auc,pred_xgb_original_ran$auc)

sens <- rbind(pred_xgb_original$metrics[[1]],pred_xgb_original_thres$metrics[[1]],pred_xgb_smote_inside_t10$metrics[[1]],pred_xgb_up_inside_t10$metrics[[1]],pred_xgb_up_inside_own$metrics[[1]],pred_xgb_smote_inside_own$metrics[[1]],pred_xgb_original_own$metrics[[1]],pred_xgb_up_inside_ran$metrics[[1]],pred_xgb_smote_inside_ran$metrics[[1]],pred_xgb_original_ran$metrics[[1]])

spec <- rbind(pred_xgb_original$metrics[[2]],pred_xgb_original_thres$metrics[[2]],pred_xgb_smote_inside_t10$metrics[[2]],pred_xgb_up_inside_t10$metrics[[2]],pred_xgb_up_inside_own$metrics[[2]],pred_xgb_smote_inside_own$metrics[[2]],pred_xgb_original_own$metrics[[2]],pred_xgb_up_inside_ran$metrics[[2]],pred_xgb_smote_inside_ran$metrics[[2]],pred_xgb_original_ran$metrics[[2]])

accuracy <- rbind(pred_xgb_original$metrics[[4]],pred_xgb_original_thres$metrics[[4]],pred_xgb_smote_inside_t10$metrics[[4]],pred_xgb_up_inside_t10$metrics[[4]],pred_xgb_up_inside_own$metrics[[4]],pred_xgb_smote_inside_own$metrics[[4]],pred_xgb_original_own$metrics[[4]],pred_xgb_up_inside_ran$metrics[[4]],pred_xgb_smote_inside_ran$metrics[[4]],pred_xgb_original_ran$metrics[[4]])

model <-  c("original","original_cost","smote_def","up_def",
           "up_own","smote_own","original_own","up_ran","smote_ran","original_ran")
metrics_xgb_life_plus <- cbind(model,auc,sens,spec,accuracy)
metrics_xgb_life_plus <- as.data.frame(metrics_xgb_life_plus)
colnames(metrics_xgb_life_plus) <- c("model","AUC","Sensitivity","Specificity","Accuracy")
metrics_xgb_life_plus <- metrics_xgb_life_plus %>%
  mutate(model = factor(model),
         AUC = as.numeric(AUC),
         Sensitivity = as.numeric(Sensitivity),
         Specificity = as.numeric(Specificity),
         Accuracy = as.numeric(Accuracy),
         ML = "XGB",
         Condition = "Lifestyle") %>%
  mutate_if(is.numeric,round,digits=3)
```

################################################################################
# Lasso
################################################################################

## DEFAULT

```{r}
lasso_up_inside_t10 <- caret::train(Night_class_hypo_out ~ ., data = full_data_life_plus_train,
                   method = "glmnet",
                   metric = "ROC",
                   trControl = ctrl_ins_up,
                   verbose = FALSE,
                   preProc = c("center", "scale"),
                   tuneLength=10)

lasso_smote_inside_t10 <- caret::train(Night_class_hypo_out ~ ., data = full_data_life_plus_train,
                   method = "glmnet",
                   metric = "ROC",
                   trControl = ctrl_ins_smote,
                   verbose = FALSE,
                   preProc = c("center", "scale"),
                   tuneLength=10)

lasso_original_t10 <- caret::train(Night_class_hypo_out ~ ., data = full_data_life_plus_train, 
                  method = "glmnet",
                  metric = "ROC",
                  trControl = ctrl_out,
                  verbose = FALSE,
                  reProc = c("center", "scale"),
                  tuneLength=10)
```

## RANDOM
```{r}
lasso_up_inside_ran <- caret::train(Night_class_hypo_out ~ ., data = full_data_life_plus_train,
                   method = "glmnet",
                   metric = "ROC",
                   trControl = ctrl_random_ins_up,
                   verbose = FALSE,
                   preProc = c("center", "scale"),
                  tuneLength=20)

lasso_smote_inside_ran <- caret::train(Night_class_hypo_out ~ ., data = full_data_life_plus_train,
                   method = "glmnet",
                   metric = "ROC",
                   trControl = ctrl_random_ins_smote,
                   verbose = FALSE,
                   preProc = c("center", "scale"),
                   tuneLength=20)

lasso_original_ran <- caret::train(Night_class_hypo_out ~ ., data = full_data_life_plus_train, 
                  method = "glmnet",
                  metric = "ROC",
                  trControl = ctrl_random,
                  verbose = FALSE,
                  reProc = c("center", "scale"),
                  tuneLength=20)
```

## Other Own Grid
```{r}
lasso_Grid <-  expand.grid(alpha  = seq(from = 0.1, to = 1, length.out = 20),
                         lambda = seq(from = 0.00001, to = 0.1, length.out = 30))

lasso_up_inside_own <- caret::train(Night_class_hypo_out ~ ., data = full_data_life_plus_train,
                   method = "glmnet",
                   metric = "ROC",
                   trControl = ctrl_ins_up,
                   verbose = FALSE,
                   preProc = c("center", "scale"),
                   tuneGrid= lasso_Grid)

lasso_smote_inside_own <- caret::train(Night_class_hypo_out ~ ., data = full_data_life_plus_train,
                   method = "glmnet",
                   metric = "ROC",
                   trControl = ctrl_ins_smote,
                   verbose = FALSE,
                   preProc = c("center", "scale"),
                   tuneGrid= lasso_Grid)

lasso_original_own <- caret::train(Night_class_hypo_out ~ ., data = full_data_life_plus_train, 
                  method = "glmnet",
                  metric = "ROC",
                  trControl = ctrl_out,
                  verbose = FALSE,
                  reProc = c("center", "scale"),
                  tuneGrid= lasso_Grid)
```

## Predictions for Test set
```{r}
pred_lasso_original <- rf_pred(lasso_original_t10,threshold = TRUE, test = full_data_life_plus_test, boundary = .17)
pred_lasso_original_thres <- rf_pred(lasso_original_t10, test = full_data_life_plus_test)

pred_lasso_smote_inside_t10 <- rf_pred(lasso_smote_inside_t10, test = full_data_life_plus_test)
pred_lasso_up_inside_t10 <- rf_pred(lasso_up_inside_t10, test = full_data_life_plus_test)
# Tune own
pred_lasso_up_inside_own <- rf_pred(lasso_up_inside_own, test = full_data_life_plus_test)
pred_lasso_smote_inside_own <- rf_pred(lasso_smote_inside_own, test = full_data_life_plus_test)
pred_lasso_original_own <- rf_pred(lasso_original_own, test = full_data_life_plus_test)
# Tune random
pred_lasso_up_inside_ran <- rf_pred(lasso_up_inside_ran, test = full_data_life_plus_test)
pred_lasso_smote_inside_ran <- rf_pred(lasso_smote_inside_ran, test = full_data_life_plus_test)
pred_lasso_original_ran <- rf_pred(lasso_original_ran, test = full_data_life_plus_test)
```

## probabilities
```{r}
probs <- cbind(pred_lasso_original$class_probs,pred_lasso_original_thres$class_probs,pred_lasso_smote_inside_t10$class_probs,pred_lasso_up_inside_t10$class_probs,pred_lasso_up_inside_own$class_probs,pred_lasso_smote_inside_own$class_probs,pred_lasso_original_own$class_probs,pred_lasso_up_inside_ran$class_probs,pred_lasso_smote_inside_ran$class_probs,pred_lasso_original_ran$class_probs)

probabilities_data <- cbind(full_data_life_plus_test$Night_class_hypo_out,probs)
colnames(probabilities_data) <-  c("outcome","original","original_cost","smote_def","up_def",
           "up_own","smote_own","original_own","up_ran","smote_ran","original_ran")
probabilities_data <- as.data.frame(probabilities_data)
probabilities_data$outcome <- factor(probabilities_data$outcome)
levels(probabilities_data$outcome) <- c("No_Hypo", "Hypo")
probabilities_data_lasso <- probabilities_data
```

## Saving the results
```{r}
auc <- rbind(pred_lasso_original$auc,pred_lasso_original_thres$auc,pred_lasso_smote_inside_t10$auc,pred_lasso_up_inside_t10$auc,pred_lasso_up_inside_own$auc,pred_lasso_smote_inside_own$auc,pred_lasso_original_own$auc,pred_lasso_up_inside_ran$auc,pred_lasso_smote_inside_ran$auc,pred_lasso_original_ran$auc)

sens <- rbind(pred_lasso_original$metrics[[1]],pred_lasso_original_thres$metrics[[1]],pred_lasso_smote_inside_t10$metrics[[1]],pred_lasso_up_inside_t10$metrics[[1]],pred_lasso_up_inside_own$metrics[[1]],pred_lasso_smote_inside_own$metrics[[1]],pred_lasso_original_own$metrics[[1]],pred_lasso_up_inside_ran$metrics[[1]],pred_lasso_smote_inside_ran$metrics[[1]],pred_lasso_original_ran$metrics[[1]])

spec <- rbind(pred_lasso_original$metrics[[2]],pred_lasso_original_thres$metrics[[2]],pred_lasso_smote_inside_t10$metrics[[2]],pred_lasso_up_inside_t10$metrics[[2]],pred_lasso_up_inside_own$metrics[[2]],pred_lasso_smote_inside_own$metrics[[2]],pred_lasso_original_own$metrics[[2]],pred_lasso_up_inside_ran$metrics[[2]],pred_lasso_smote_inside_ran$metrics[[2]],pred_lasso_original_ran$metrics[[2]])

accuracy <- rbind(pred_lasso_original$metrics[[4]],pred_lasso_original_thres$metrics[[4]],pred_lasso_smote_inside_t10$metrics[[4]],pred_lasso_up_inside_t10$metrics[[4]],pred_lasso_up_inside_own$metrics[[4]],pred_lasso_smote_inside_own$metrics[[4]],pred_lasso_original_own$metrics[[4]],pred_lasso_up_inside_ran$metrics[[4]],pred_lasso_smote_inside_ran$metrics[[4]],pred_lasso_original_ran$metrics[[4]])

model <-  c("original","original_cost","smote_def","up_def",
           "up_own","smote_own","original_own","up_ran","smote_ran","original_ran")
metrics_lasso_life_plus <- cbind(model,auc,sens,spec,accuracy)
metrics_lasso_life_plus <- as.data.frame(metrics_lasso_life_plus)
colnames(metrics_lasso_life_plus) <- c("model","AUC","Sensitivity","Specificity","Accuracy")
metrics_lasso_life_plus <- metrics_lasso_life_plus %>%
  mutate(model = factor(model),
         AUC = as.numeric(AUC),
         Sensitivity = as.numeric(Sensitivity),
         Specificity = as.numeric(Specificity),
         Accuracy = as.numeric(Accuracy),
         ML = "Lasso",
         Condition = "Lifestyle") %>%
  mutate_if(is.numeric,round,digits=3)
```

# COMBINE ALL RESULTS
All results are combined and saved in multiple data sets / lists.
```{r}
all_models_lifestyle <- rbind(metrics_rf_life_plus,metrics_xgb_life_plus,metrics_lasso_life_plus,metrics_svm_life_plus)
write.csv(all_models_lifestyle,"Data/all_models_lifestyle_123.csv", row.names = FALSE)
#View(all_models_lifestyle)

probs_lifestyle_123 <- list(rf= probabilities_data_rf, svm = probabilities_data_svm,xgb= probabilities_data_xgb, lasso =probabilities_data_lasso)
saveRDS(probs_lifestyle_123, file = "Data/probs_lifestyle_123.RData")
```