---
title: "Combining data sets"
author: "Christoph Völtzke"
date: "2022"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Packages
```{r}
library(lubridate) # process dates
library(tidyverse) # process data
library(ggplot2) # to plot
library(readxl) # load raw data
library(haven) # for baseline stats
```

# Information
- In this document baseline patient data is processed and relevant features are extracted. Further new baseline stats are saved.
- Next all pre-processed data sets are loaded.
- Some last pre-processing of data from PA and Food is needed and afterwards all data sets are combined.
- Raw data from each patient needs to be processed in a way that all relevant features can get extracted.
- Several features are extracted and data is saved.

## Loading and processing baseline characteristics
```{r}
baseline_new <- read_sav("Patients_all_sources/new_baseline.sav")

baseline <- baseline_new %>%
  mutate(Diabetes_Length = 2023 - DMaanvang,
         BMI = Gewicht_poli1/((Lengte_poli1/100)^2)) %>%
  select(Subjectnr,DM_type,Geslacht,Leeftijd_poli1,Diabetes_Length,Leeftijd_aanvangDM2,Lengte_poli1,Gewicht_poli1,BMI,SerumHbA1c_1,insulin_bin,atcA10AE,dosA10AE,atcA10AB,dosA10AB,atcA10AD,dosA10AD,atcA10BB,dosA10BB,atcA10AC,dosA10AC) %>%
  rename(patient =Subjectnr) %>%
  mutate_all(~replace(., is.na(.), 0))
#write.csv(baseline, "Data_processed/baseline.csv")
```

## Loading all data sets
```{r, warning=FALSE}
baseline <- read_csv("Data_processed/baseline.csv")
all_patients_cgm <- read_csv("Data_processed/all_patients_cgm.csv")
steps_all_patients <- read_csv("Data_processed/steps_all_patients.csv")
cob_all_patients_new <- read_csv("Data_processed/cob_all_patients.csv")
```

## Combining the CGM data set with the AOB and the COB
First data needs to be combined by date to check wether the days for PA, Food and CGM fit together. If not the days are excluded.
```{r}
# new approach to work with all the patients
all_patients_cgm_cob <- left_join(all_patients_cgm, cob_all_patients_new,by=c("patient","date"))
all_patients_cgm_cob_steps <- left_join(all_patients_cgm_cob, steps_all_patients,by=c("patient","date"))
```

```{r}
# get the final estimates for lifestyle features (mean and sd is needed as otherwise there is no information about the periods.)
cob_steps_all_patients <- all_patients_cgm_cob_steps %>%
  group_by(patient,periods) %>%
  summarise(COB = mean(COB, na.rm=TRUE),
            Sum_carbs = mean(Sum_C, na.rm=TRUE),
            Sum_steps = mean(Sum_steps, na.rm=TRUE),
            AOB = mean(AOB, na.rm=TRUE),
            Sum_calories = mean(Sum_Cal, na.rm=TRUE),
            Sum_Fat = mean(Sum_F, na.rm=TRUE),
            Num_Meals = mean(Num_Meals, na.rm=TRUE),
            Last_meal = mean(Last_meal_time, na.rm=TRUE)) %>%
  ungroup()
```
```{r}
#wide format for cgm features, needed to have full information about features
cgm_all_patients <- read_csv("Data_processed/cgm_all_patients.csv")
cgm_cob_steps_all_patients <- left_join(cgm_all_patients, cob_steps_all_patients,by=c("patient","periods"))
```

## Full data sets
```{r}
full_data <- left_join(cgm_cob_steps_all_patients, baseline,by="patient")

full_data <- full_data %>%
   mutate(Night_class_hyper_30 = as.factor(Night_class_hyper_30),
         Night_class_hypo_out = as.factor(Night_class_hypo_out)) %>%
  select(-"...1")
```

## FINAL Data
One last patient is excluded as this one only had a single day left after combining all data sets.
```{r}
full_data <- full_data %>%
  filter(!(patient == 597 ))
```

## OPTIONAL - Data Summary
Small data summary of full data. Also the data is saved for further analyses.
```{r}
#check this with 1 obs per interval
number_of_days_pp <- full_data %>%
  group_by(patient) %>%
  summarise(n= n())
sort(number_of_days_pp$n)
nrow(number_of_days_pp)
```
It is saved within the preprocessing as well as in the analyses section.
```{r}
write.csv(full_data,"Data_processed/full_data.csv", row.names = FALSE)
```