---
title: "Physical activity_all_patients"
author: "Christoph Völtzke"
date: '2022'
output:
  html_document: default
  pdf_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
library(lubridate) # manipulate dates
library(tidyverse) # data processing
library(ggplot2) # plotting
library(readxl) # load xlsx files
```

# Information
- In this document the physical activity data is processed and features are extracted.
- All data is already in the same format and only needs to be combined in a single data set
- Two features are extracted and data is saved.

# Loading all data sets
All patients ordered by ID
```{r}
X574_steps <- read_excel("Patients_all_sources/574/574-steps.xlsx")
X597_steps <- read_excel("Patients_all_sources/597/597-steps.xlsx")
X598_steps <- read_excel("Patients_all_sources/598/598-steps.xlsx")
X601_steps <- read_excel("Patients_all_sources/601/601-steps.xlsx")
X605_steps <- read_excel("Patients_all_sources/605/605-steps.xlsx")
X606_steps <- read_excel("Patients_all_sources/606/606-steps.xlsx")
X607_steps <- read_excel("Patients_all_sources/607/607-steps.xlsx")
X608_steps <- read_excel("Patients_all_sources/608/608-steps.xlsx")
X609_steps <- read_excel("Patients_all_sources/609/609-steps.xlsx")
X611_steps <- read_excel("Patients_all_sources/611/611-steps.xlsx")
X612_steps <- read_excel("Patients_all_sources/612/612-steps.xlsx")
X615_steps <- read_excel("Patients_all_sources/615/615-steps.xlsx")
X616_steps <- read_excel("Patients_all_sources/616/616-steps.xlsx")
X617_steps <- read_excel("Patients_all_sources/617/617-steps.xlsx")
X618_steps <- read_excel("Patients_all_sources/618/618-steps.xlsx")
X621_steps <- read_excel("Patients_all_sources/621/621-steps.xlsx")
X623_steps <- read_excel("Patients_all_sources/623/623-steps.xlsx")
X624_steps <- read_excel("Patients_all_sources/624/624-steps.xlsx")
X628_steps <- read_excel("Patients_all_sources/628/628-steps.xlsx")
X629_steps <- read_excel("Patients_all_sources/629/629-steps.xlsx")
X630_steps <- read_excel("Patients_all_sources/630/630-steps.xlsx")
X632_steps <- read_excel("Patients_all_sources/632/632-steps.xlsx")
X633_steps <- read_excel("Patients_all_sources/633/633-steps.xlsx")
X634_steps <- read_excel("Patients_all_sources/634/634-steps.xlsx")
X635_steps <- read_excel("Patients_all_sources/635/635-steps.xlsx")
X636_steps <- read_excel("Patients_all_sources/636/636-steps.xlsx")
X637_steps <- read_excel("Patients_all_sources/637/637-steps.xlsx")
X638_steps <- read_excel("Patients_all_sources/638/638-steps.xlsx")
X639_steps <- read_excel("Patients_all_sources/639/639-steps.xlsx")
X640_steps <- read_excel("Patients_all_sources/640/640-steps.xlsx")
X641_steps <- read_excel("Patients_all_sources/641/641-steps.xlsx")
X642_steps <- read_excel("Patients_all_sources/642/642-steps.xlsx")
X643_steps <- read_excel("Patients_all_sources/643/643-steps.xlsx")
X644_steps <- read_excel("Patients_all_sources/644/644-steps.xlsx")
X645_steps <- read_excel("Patients_all_sources/645/645-steps.xlsx")
X646_steps <- read_excel("Patients_all_sources/646/646-steps.xlsx")
X647_steps <- read_excel("Patients_all_sources/647/647-steps.xlsx")
X648_steps <- read_excel("Patients_all_sources/648/648-steps.xlsx")
X649_steps <- read_excel("Patients_all_sources/649/649-steps.xlsx")
X650_steps <- read_excel("Patients_all_sources/650/650-steps.xlsx")
X651_steps <- read_excel("Patients_all_sources/651/651-steps.xlsx")
X654_steps <- read_excel("Patients_all_sources/654/654-steps.xlsx")
X656_steps <- read_excel("Patients_all_sources/656/656-steps.xlsx")
X658_steps <- read_excel("Patients_all_sources/658/658-steps.xlsx")
X660_steps <- read_excel("Patients_all_sources/660/660-steps.xlsx")
X661_steps <- read_excel("Patients_all_sources/661/661-steps.xlsx")
X662_steps <- read_excel("Patients_all_sources/662/662-steps.xlsx")
X664_steps <- read_excel("Patients_all_sources/664/664-steps.xlsx")
X665_steps <- read_excel("Patients_all_sources/665/665-steps.xlsx")
X666_steps <- read_excel("Patients_all_sources/666/666-steps.xlsx")
X667_steps <- read_excel("Patients_all_sources/667/667-steps.xlsx")
X669_steps <- read_excel("Patients_all_sources/669/669-steps.xlsx")
X671_steps <- read_excel("Patients_all_sources/671/671-steps.xlsx")
X672_steps <- read_excel("Patients_all_sources/672/672-steps.xlsx")
X674_steps <- read_excel("Patients_all_sources/674/674-steps.xlsx")
X676_steps <- read_excel("Patients_all_sources/676/676-steps.xlsx")
X677_steps <- read_excel("Patients_all_sources/677/677-steps.xlsx")
X678_steps <- read_excel("Patients_all_sources/678/678-steps.xlsx")
X680_steps <- read_excel("Patients_all_sources/680/680-steps.xlsx")
X681_steps <- read_excel("Patients_all_sources/681/681-steps.xlsx")
X682_steps <- read_excel("Patients_all_sources/682/682-steps.xlsx")
X683_steps <- read_excel("Patients_all_sources/683/683-steps.xlsx")
X684_steps <- read_excel("Patients_all_sources/684/684-steps.xlsx")
X686_steps <- read_excel("Patients_all_sources/686/686-steps.xlsx")
X687_steps <- read_excel("Patients_all_sources/687/687-steps.xlsx")
X688_steps <- read_excel("Patients_all_sources/688/688-steps.xlsx")
X690_steps <- read_excel("Patients_all_sources/690/690-steps.xlsx")
X691_steps <- read_excel("Patients_all_sources/691/691-steps.xlsx")
X692_steps <- read_excel("Patients_all_sources/692/692-steps.xlsx")
X694_steps <- read_excel("Patients_all_sources/694/694-steps.xlsx")
X695_steps <- read_excel("Patients_all_sources/695/695-steps.xlsx")
X696_steps <- read_excel("Patients_all_sources/696/696-steps.xlsx")
X697_steps <- read_excel("Patients_all_sources/697/697-steps.xlsx")
X698_steps <- read_excel("Patients_all_sources/698/698-steps.xlsx")
X699_steps <- read_excel("Patients_all_sources/699/699-steps.xlsx")
X702_steps <- read_excel("Patients_all_sources/702/702-steps.xlsx")
X703_steps <- read_excel("Patients_all_sources/703/703-steps.xlsx")
X708_steps <- read_excel("Patients_all_sources/708/708-steps.xlsx")
X709_steps <- read_excel("Patients_all_sources/709/709-steps.xlsx")
X712_steps <- read_excel("Patients_all_sources/712/712-steps.xlsx")
X713_steps <- read_excel("Patients_all_sources/713/713-steps.xlsx")
X716_steps <- read_excel("Patients_all_sources/716/716-steps.xlsx")
X719_steps <- read_excel("Patients_all_sources/719/719-steps.xlsx")
X729_steps <- read_excel("Patients_all_sources/729/729-steps.xlsx")
X745_steps <- read_excel("Patients_all_sources/745/745-steps.xlsx")
X746_steps <- read_excel("Patients_all_sources/746/746-steps.xlsx")
X748_steps <- read_excel("Patients_all_sources/748/748-steps.xlsx")
X749_steps <- read_excel("Patients_all_sources/749/749-steps.xlsx")
X750_steps <- read_excel("Patients_all_sources/750/750-steps.xlsx")
X751_steps <- read_excel("Patients_all_sources/751/751-steps.xlsx")
X752_steps <- read_excel("Patients_all_sources/752/752-steps.xlsx")
X753_steps <- read_excel("Patients_all_sources/753/753-steps.xlsx")
X754_steps <- read_excel("Patients_all_sources/754/754-steps.xlsx")
X756_steps <- read_excel("Patients_all_sources/756/756-steps.xlsx")
X757_steps <- read_excel("Patients_all_sources/757/757-steps.xlsx")
X759_steps <- read_excel("Patients_all_sources/759/759-steps.xlsx")
X760_steps <- read_excel("Patients_all_sources/760/760-steps.xlsx")
X761_steps <- read_excel("Patients_all_sources/761/761-steps.xlsx")
X1001_steps <- read_excel("Patients_all_sources/1001/1001-steps.xlsx")
```

```{r}
# adding the patient number to identify each patient
X574_steps$patient <- 574
X597_steps$patient <- 597
X598_steps$patient <- 598
X601_steps$patient <- 601
X605_steps$patient <- 605
X606_steps$patient <- 606
X607_steps$patient <- 607
X608_steps$patient <- 608
X609_steps$patient <- 609
X611_steps$patient <- 611
X612_steps$patient <- 612
X615_steps$patient <- 615
X616_steps$patient <- 616
X617_steps$patient <- 617
X618_steps$patient <- 618
X621_steps$patient <- 621
X623_steps$patient <- 623
X624_steps$patient <- 624
X628_steps$patient <- 628
X629_steps$patient <- 629
X630_steps$patient <- 630
X632_steps$patient <- 632
X633_steps$patient <- 633
X634_steps$patient <- 634
X635_steps$patient <- 635
X636_steps$patient <- 636
X637_steps$patient <- 637
X638_steps$patient <- 638
X639_steps$patient <- 639
X640_steps$patient <- 640
X641_steps$patient <- 641
X642_steps$patient <- 642
X643_steps$patient <- 643
X644_steps$patient <- 644
X645_steps$patient <- 645
X646_steps$patient <- 646
X647_steps$patient <- 647
X648_steps$patient <- 648
X649_steps$patient <- 649
X650_steps$patient <- 650
X651_steps$patient <- 651
X654_steps$patient <- 654
X656_steps$patient <- 656
X658_steps$patient <- 658
X660_steps$patient <- 660
X661_steps$patient <- 661
X662_steps$patient <- 662
X664_steps$patient <- 664
X665_steps$patient <- 665
X666_steps$patient <- 666
X667_steps$patient <- 667
X669_steps$patient <- 669
X671_steps$patient <- 671
X672_steps$patient <- 672
X674_steps$patient <- 674
X676_steps$patient <- 676
X677_steps$patient <- 677
X678_steps$patient <- 678
X680_steps$patient <- 680
X681_steps$patient <- 681
X682_steps$patient <- 682
X683_steps$patient <- 683
X684_steps$patient <- 684
X686_steps$patient <- 686
X687_steps$patient <- 687
X688_steps$patient <- 688
X690_steps$patient <- 690
X691_steps$patient <- 691
X692_steps$patient <- 692
X694_steps$patient <- 694
X695_steps$patient <- 695
X696_steps$patient <- 696
X697_steps$patient <- 697
X698_steps$patient <- 698
X699_steps$patient <- 699
X702_steps$patient <- 702
X703_steps$patient <- 703
X708_steps$patient <- 708
X709_steps$patient <- 709
X712_steps$patient <- 712
X713_steps$patient <- 713
X716_steps$patient <- 716
X719_steps$patient <- 719
X729_steps$patient <- 729
X745_steps$patient <- 745
X746_steps$patient <- 746
X748_steps$patient <- 748
X749_steps$patient <- 749
X750_steps$patient <- 750
X751_steps$patient <- 751
X752_steps$patient <- 752
X753_steps$patient <- 753
X754_steps$patient <- 754
X756_steps$patient <- 756
X757_steps$patient <- 757
X759_steps$patient <- 759
X760_steps$patient <- 760
X761_steps$patient <- 761
X1001_steps$patient <- 1001
```

All patients PA in one list to be less prone to errors
```{r}
steps_all <- list()
steps_all <- list(X574_steps,X597_steps,X598_steps,X605_steps,X606_steps,X607_steps,X609_steps,X611_steps,X612_steps,X615_steps,X616_steps,X617_steps,X618_steps,X621_steps,X623_steps,X624_steps,X628_steps,X629_steps,X630_steps,X632_steps,X634_steps,X635_steps,X637_steps,X638_steps,X640_steps,X641_steps,X642_steps,X643_steps,X644_steps,X645_steps,X646_steps,X647_steps,X648_steps,X650_steps,X654_steps,X656_steps,X660_steps,X1001_steps,X601_steps,X608_steps,X662_steps,X667_steps,X672_steps,X676_steps,X680_steps,X683_steps,X684_steps,X687_steps,X690_steps,X691_steps,X692_steps,X695_steps,X699_steps,X702_steps,X703_steps,X708_steps,X709_steps,X712_steps,X713_steps,X716_steps,X719_steps,X729_steps,X651_steps,X745_steps,X746_steps,X748_steps,X749_steps,X750_steps,X751_steps,X752_steps,X753_steps,X754_steps,X756_steps,X665_steps,X633_steps,X636_steps,X639_steps,X649_steps,X658_steps,X661_steps,X664_steps,X666_steps,X669_steps,X671_steps,X674_steps,X677_steps,X678_steps,X681_steps,X682_steps,X686_steps,X688_steps,X694_steps,X696_steps,X697_steps,X698_steps,X757_steps,X759_steps,X760_steps,X761_steps)
```

# Apply AOB formula
For each patient apply the AOB formula explained in the report with some preset values. 
And also extracting the full sum of steps as a feature.
Also Exlcusion criteria of less then 50 steps a day is applied here.
```{r}
# Extracting a feature for AOB
AOB_f <- function(st,t){st*exp(-0.0115*t)}

for(i in 1:length(steps_all)){
steps_all[[i]] <- steps_all[[i]] %>%
  pivot_longer(cols = starts_with("20"),names_to = "date", values_to = "Steps",values_drop_na = TRUE) %>%
  mutate(time = hms(time),
         min_num = as.numeric(time)/60,
         Diff = 1350 - min_num,
         date = ymd(date)) %>%
  group_by(patient,date) %>%
  mutate(Sum_steps = sum(Steps),
         AOB_f = AOB_f(Steps,Diff),
         AOB = sum(AOB_f)) %>%
  filter(Sum_steps > 50)%>% # exclusion criteria
  select(patient,date,Sum_steps,AOB)

steps_all[[i]] <- unique(steps_all[[i]])
  }
```


# All in one data set
```{r}
all_steps <- rbind(steps_all[[1]],steps_all[[2]],steps_all[[3]],steps_all[[4]],steps_all[[5]],steps_all[[6]],steps_all[[7]],steps_all[[8]],steps_all[[9]],steps_all[[10]],steps_all[[11]],steps_all[[12]],steps_all[[13]],steps_all[[14]],steps_all[[15]],steps_all[[16]],steps_all[[17]],steps_all[[18]],steps_all[[19]],steps_all[[20]],steps_all[[21]],steps_all[[22]],steps_all[[23]],steps_all[[24]],steps_all[[25]],steps_all[[26]],steps_all[[27]],steps_all[[28]],steps_all[[29]],steps_all[[30]],steps_all[[31]],steps_all[[32]],steps_all[[33]],steps_all[[34]],steps_all[[35]],steps_all[[36]],steps_all[[37]],steps_all[[38]],steps_all[[39]],steps_all[[40]],steps_all[[41]],steps_all[[42]],steps_all[[43]],steps_all[[44]],steps_all[[45]],steps_all[[46]],steps_all[[47]],steps_all[[48]],steps_all[[49]],steps_all[[50]],steps_all[[51]],steps_all[[52]],steps_all[[53]],steps_all[[54]],steps_all[[55]],steps_all[[56]],steps_all[[57]],steps_all[[58]],steps_all[[59]] ,steps_all[[60]],steps_all[[61]],steps_all[[62]],steps_all[[63]],steps_all[[64]],steps_all[[65]],steps_all[[66]],steps_all[[67]],steps_all[[68]],steps_all[[69]],steps_all[[70]],steps_all[[71]],steps_all[[72]],steps_all[[73]],steps_all[[74]],steps_all[[75]],steps_all[[76]],steps_all[[77]],steps_all[[78]],steps_all[[79]],steps_all[[80]],steps_all[[81]],steps_all[[82]],steps_all[[83]],steps_all[[84]],steps_all[[85]],steps_all[[86]],steps_all[[87]],steps_all[[88]],steps_all[[89]],steps_all[[90]],steps_all[[91]],steps_all[[92]],steps_all[[93]],steps_all[[94]],steps_all[[95]],steps_all[[96]],steps_all[[97]],steps_all[[97]],steps_all[[98]],steps_all[[99]])
```


## Optional - Data summary
Small data summary about the PA data. Also the data is saved for further analyses.
```{r}
nrow(all_steps)
number_of_days_pp <- all_steps %>%
  group_by(patient) %>%
  summarise(n= n())
sort(number_of_days_pp$n)
nrow(number_of_days_pp)
number_of_days_pp

summary(all_steps)
```

```{r}
#write.csv(all_steps,"Data_processed/steps_all_patients.csv", row.names = FALSE)
```
